---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fishcom

[![Build Status](https://travis-ci.org/alaindanet/fishcom.svg?branch=master)](https://travis-ci.org/alaindanet/fishcom)

The goal of fishcom is to get all the informations concerning the ECOSTAB postdoc
project in one place including reproducible code, notes, eventually data and
manuscripts.

## How to 

### Get the repository

You can clone the repository with [git](https://git-scm.com/) by pasting in your terminal:

```
git clone https://github.com/alaindanet/fishcom.git dir_name_to_be_created
```
OR

just download the repository: [alaindanet/fishcom](https://github.com/alaindanet/fishcom/archive/master.zip) 

### Open it in Rstudio 

If you have [Rstudio](https://www.rstudio.com/) installed on your computer, just open `fishcom.Rproj` with
Rstudio.

## Information

My notes are available in the introductory vignette `vignettes/intro.html`

## Structure of the project repository 

### Raw data

Raw datas are spreadsheets (xls, csv, etc...) shapefiles and others cartographic
data and reports (of the AFB, ONEMA, etc). The raw datas come together with `R`
scripts which describe cleaning procedures. The cleaning procedures end by
saving datasets used for data analysis. 

It is located in `data-raw`.

### Data for analysis

The clean datasets live in `data` directory and stored in `rda` compressed format.
Once the package is loaded, they can be call as easily as `load(objet_name)`.

```{r}
devtools::load_all()
data(metaweb_analysis)
names(metaweb_analysis)
```
The cleaned and filtered objects used for data analysis are named with the suffix `_analysis`.


### Analysis of data 

The analysis of data lives in the directory named `analysis`.

This folder contains scripts in which various metrics are computed for two
different aspects that have been more or less arbitrary separated.

#### Community data

The community data lives in the `community_analysis` and contains the following
data:

- species abondances
- species biomass
- species richness

The following metrics are summarised by station in `community_metrics`:

- mean and cv of species richness
- mean and cv of species biomass 
- temporal beta-diversity

#### Network data


The network data lives in the `network_analysis` and contains the following
metrics:

- connectance
- number of nodes
- modularity and modules 
- nestedness 
- trophic length

The following metrics are summarised by station:

- mean and cv of all the above indices
