---
title: "Build dataset from ASPE database"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Build dataset from ASPE database}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
default::default(unlist) <- list(use.names = FALSE)
mypath <- rprojroot::find_package_root_file
dest_dir <- mypath("data-raw", "fishing_op_build")

if (!dir.exists(dest_dir)) {
  dir.create(dest_dir)
}
```
```{r library}
library(tidyverse)
library(magrittr)
library(dbplyr)
library(lubridate)
library(ggplot2)
devtools::load_all()
theme_set(theme_alain())
```


This document groups all the questions and remarks that I have regarding the
ASPE database. Those questionings will be addressed to Thierry Point and Eddy
Cosson.  

The procedure to build my database is in `data-raw/01_clean_fish_op_data.R`.

```{r}
# Set up the connection with the database
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = "afb_fish", port = 5434)
```


# Fishing operation 

```{r fish operation dataset}
db_op <- tbl(con, in_schema("aspe", "operation"))
db_op %<>%
  rename_all(list(~ gsub("ope_", "", make.names(colnames(db_op)))))
```


## Fishing objectives 

In the fishing operation objectives, we can find the following:
```{r}
obj_id <- tbl(con, in_schema("aspe", "ref_objectif"))
obj_id
```

Here is the distribution of the objectives by year:

```{r}
obj_time <- tbl(con, in_schema("aspe", "operation_objectif")) %>%
  collect() %>%
  rename(id = opo_ope_id, obj_id = opo_obj_id) %>%
  left_join(., collect(db_op)) %>%
  left_join(., collect(obj_id) %>% select(obj_id, obj_libelle)) %>%
  mutate(year = year(date)) %>%
  select(obj_libelle, year) %>%
  group_by(year, obj_libelle) %>%
  summarise(n = n())
obj_time
```

Wahhh, a lot of objectives are NAs? Let's check:
```{r}
ggplot(obj_time, aes(x = year, y = n)) +
  geom_line(aes(color = obj_libelle))
```

I am not really sure of my choice. For intance, I keep the following objectives:

```{r}
obj_to_keep <- "RHP|DCE|RRP|RCS|CO|restauration|RNSORMCE|Étude"
obj_kept <- tbl(con, in_schema("aspe", "ref_objectif")) %>%
  collect() %>%
  filter(str_detect(obj_libelle, obj_to_keep))
obj_kept$obj_libelle
```

```{r}
# Keep the op id corresponding to the objectives:
objective_op_id <- tbl(con, in_schema("aspe", "operation_objectif")) %>%
  collect %>%
  filter(opo_obj_id %in% obj_kept$obj_id) %>%
  select(opo_ope_id) %>% unlist
```


## Levels of qualification 

There are different levels of qualification in the database.  
Those levels allow to filter and correct bugs (I guess). For example, if you enter the bad
units, introduce letters in numeric fields, etc... 

```{r}
qualif_lvl <- tbl(con, in_schema("aspe", "ref_niveau_qualification")) %>%
  collect() 
qualif_lvl
```
Here is the repartition of the qualification levels:

```{r}
qualif_time <- collect(db_op) %>%
  #rename(id = opo_ope_id, obj_id = opo_obj_id) %>%
  left_join(., qualif_lvl) %>%
  mutate(year = year(date)) %>%
  select(niq_libelle, year) %>%
  group_by(year, niq_libelle) %>%
  summarise(n = n())
ggplot(qualif_time, aes(x = year, y = n)) +
  geom_line(aes(color = niq_libelle)) +
  labs(color = "Qualification level",
  x = "Year", y = "# of fishing operations")
```

We keep everything because a huge part of the operations has an incorrect 
qualification level, which is strange.

```{r}
# we keep everything:
qualif_to_keep <- "[a-z]"#"Correct|Incertaine|Non renseignée"
qualif_kept <- qualif_lvl %>%
  collect() %>%
  filter(str_detect(niq_libelle, qualif_to_keep))
qualif_kept$niq_libelle
```

## Fishing protocol

There are seven fish protocols:

```{r}
protocols <- tbl(con, in_schema("aspe", "ref_protocole")) %>%
  collect() %>%
  select(-pro_acronyme, -pro_ordre_affichage)
protocols
```
Here their distribution:

```{r}
protocol_time <- collect(db_op) %>%
  #rename(id = opo_ope_id, obj_id = opo_obj_id) %>%
  left_join(., protocols) %>%
  mutate(year = year(date)) %>%
  select(pro_libelle, year) %>%
  group_by(year, pro_libelle) %>%
  summarise(n = n())
ggplot(protocol_time, aes(x = year, y = n)) +
  geom_line(aes(color = pro_libelle))

```

We keep the "complete" one which is the most homogeneous protocol and typical of
small rivers because the fishing is done by foot overall the river.

We also keep the "partial" protocols for the big rivers.

```{r}
protocol_to_keep <- "complète|partielle"
protocol_kept <- protocols %>%
  collect() %>%
  filter(str_detect(pro_libelle, protocol_to_keep))
protocol_replacement <- c(
"Pêche complète à un ou plusieurs passages" = "complete",
"Pêche partielle par points \\(grand milieu\\)" = "partial_by_point",
"Pêche partielle sur berge" = "partial_over_bank"
)
protocol_kept$pro_libelle %<>% str_replace_all(., protocol_replacement)
```

## Build the dataset

```{r}
# Selected ids 
col_to_keep <- c("id", "date", "pro_id", "pente_ligne_eau", "section_mouillee",
  "durete_totale", "temp_max_moyenne_eau", "temp_air_bassin_versant",
  "precipitation_bassin_versant", "amplitude_thermique_air_station",
  "temperature_air_station", "surface_calculee", "espece_ciblee", "niq_id",
  "eta_id", "commentaire")

op <- db_op %>%
  select(col_to_keep) %>%
  collect() %>%
  filter(niq_id %in% qualif_kept$niq_id) %>% # Select qualification
  filter(id %in% objective_op_id) %>% #operation objectives
  filter(espece_ciblee == FALSE) %>% # Do not keep those specific operations
  filter(pro_id %in% protocol_kept$pro_id) %>% #operation prospection methods 
  filter(date > lubridate::ymd("1995-01-01")) %>% # Because it is the time of protocol standardization
  arrange(date)

```

## Get names instead of id

```{r}
protocol_kept %<>%
  rename(protocol = pro_libelle) %>%
  select(pro_id, protocol)
op %<>%
  left_join(., protocol_kept) %>% select(-pro_id)

```

# Description of the fishing conditions

```{r}
# Collect débit, largeur, longueur, etc
# and them accordingly to fishing operation env and general
# HERE
op_desc <- tbl(con, in_schema("aspe", "operation_description_peche")) %>%
  filter(odp_ope_id %in% op$id) %>%
  collect()
colnames(op_desc)
desc_op_col <-c(
"odp_ope_id", "odp_mop_id", "odp_duree_peche",
"odp_surface_eq_radier_rapide_troncon",
"odp_observations_generales", "odp_longueur",
"odp_largeur_lame_eau", "odp_iso_id_aval", "odp_iso_id_amont",
"odp_largeur_rive_gauche", "odp_longueur_rive_gauche",
"odp_largeur_rive_droite", "odp_longueur_rive_droite",
"odp_temperature_instantanee", "odp_conductivite",
"odp_ted_id", "odp_tur_id", "odp_coh_id",
"odp_debit_moyen_journalier", "odp_debit_moyen_horaire"
)

op_desc %<>% select(desc_op_col)
# simplify naming:
op_desc %<>% rename_all(
  list(~ gsub("odp_", "", make.names(colnames(op_desc)))))
desc_col_replacement <- c(
 "mop_id"                  = "method_id"            ,
 "duree_peche"             = "time_fishing"      ,
 "iso_id_aval"             = "isolation_down_id"    ,
 "iso_id_amont"            = "isolation_up_id"      ,
 "largeur_lame_eau"        = "width_river"        ,
 "largeur_rive_gauche"     = "width_left_shore"   ,
 "longueur_rive_gauche"    = "length_left_shore"  ,
 "largeur_rive_droite"     = "width_right_shore"  ,
 "longueur_rive_droite"    = "length_right_shore" ,
 "longueur"                = "length_sourced"    ,
 "temperature_instantanee" = "instant_temperature",
 "conductivite"            = "conductivity"       ,
 "ted_id"                  = "flow_trend_id"         ,
 "tur_id"                  = "turbidity_id"          ,
 "coh_id"                  = "hydro_condition_id"    ,
 "debit_moyen_journalier"  = "avg_daily_flow"     ,
 "debit_moyen_horaire"     = "avg_hourly_flow",
 "observations_generales"  = "general_observations"
)
colnames(op_desc) <- str_replace_all(colnames(op_desc), desc_col_replacement)
```

## Replace ids by strings 

```{r}
ref_method <- tbl(con, in_schema("aspe", "ref_moyen_prospection")) %>%
  collect() %>%
  rename(
    "method_id" = "mop_id",
    "method" = "mop_libelle"
  ) %>%
  select(method_id, method)
# Translate in english:
method_replacement <- c(
  "A pied" = "by_foot",
  "En bateau" = "by_boat",
  "Mixte" = "mixed",
  "Non renseigné" = "unknown"
)
ref_method$method %<>% str_replace_all(., method_replacement)
```

```{r}
ref_turbidity <- tbl(con, in_schema("aspe", "ref_turbidite")) %>%
  collect() %>%
  rename(
    "turbidity_id" = "tur_id",
    "turbidity" = "tur_libelle"
  ) %>%
  select(turbidity_id, turbidity)
# Translate in english:
turbidity_replacement <- c(
  "Nulle"   = "null",
  "Faible"  = "weak",
  "Moyenne" = "medium",
  "Forte"   = "strong"
)
ref_turbidity$turbidity %<>% str_replace_all(., turbidity_replacement)
```

```{r}
ref_isolation <- tbl(con, in_schema("aspe", "ref_isolement")) %>%
  collect() %>%
  rename(
    "isolation_id" = "iso_id",
    "isolation" = "iso_libelle"
  ) %>%
  select(isolation_id, isolation)

# Translate in english:
isolation_replacement <- c(
 "Pas d’isolement"                   = "no",
 "Seuil partiellement franchissable" = "partly_crossable",
 "Obstacle infranchissable"          = "obstacle_uncrossable",
 "Filet"                             = "net",
 "Barrage électrique"                = "electric_dam",
 "Autres"                            = "others"
)
ref_isolation$isolation %<>% str_replace_all(., isolation_replacement)
ref_isolation_up <- ref_isolation %>%
  mutate(
    isolation_up_id = isolation_id,
    isolation_up = isolation
  ) %>%
  select(isolation_up_id, isolation_up)
ref_isolation_down <- ref_isolation %>%
  mutate(
    isolation_down_id = isolation_id,
    isolation_down = isolation
  ) %>%
  select(isolation_down_id, isolation_down)
```

```{r}
ref_hydro_condition <- tbl(con, in_schema("aspe", "ref_condition_hydrologique")) %>%
  collect() %>%
  rename(
    "hydro_condition_id" = "coh_id",
    "hydro_condition" = "coh_libelle"
  ) %>%
  select(hydro_condition_id, hydro_condition)
# Translate in english:
hydro_condition_replacement <- c(
 "Basses eaux"   = "low_water",
 "Eaux moyennes" = "medium_water",
 "Hautes eaux"   = "high_water"
)
ref_hydro_condition$hydro_condition %<>% str_replace_all(., hydro_condition_replacement)
```

```{r}
ref_flow_trend <- tbl(con, in_schema("aspe", "ref_tendance_debit")) %>%
  collect() %>%
  rename(
    "flow_trend_id" = "ted_id",
    "flow_trend" = "ted_libelle"
  ) %>%
  select(flow_trend_id, flow_trend)

# Translate in english:
flow_trend_replacement <- c(
 "Augmentation \\(en crue\\)" = "flooding",
 "Diminution \\(en décrue\\)" = "decline",
 "Stabilité"              = "stability",
 "Irrégularité"          = "irregularity"
)
ref_flow_trend$flow_trend %<>% str_replace_all(., flow_trend_replacement)
```

```{r}
op_desc %<>%
  left_join(., ref_flow_trend) %>%
  left_join(., ref_hydro_condition) %>%
  left_join(., ref_turbidity) %>%
  left_join(., ref_method) %>%
  left_join(., ref_isolation_up) %>%
  left_join(., ref_isolation_down) 

col_to_rm <- tidyselect::vars_select(names(op_desc), ends_with("id"))

op_desc %<>%
  select(- one_of(col_to_rm[col_to_rm != "ope_id"]))
save(op_desc, file = mypath("data-raw", "fishing_op_build", "op_desc.rda"))
```

# Environmental data of the fishing operation

```{r}
op_env <- tbl(con, in_schema("aspe", "operation_donnees_environnementales")) %>%
  filter(ode_ope_id %in% op$id) %>%
  collect()
colnames(op_env)
env_op_col <- c(
"ode_ope_id", "ode_lo3_id_secteur_debit_reserve",
"ode_lo3_id_secteur_soumis_ecluse", "ode_lo3_id_soutien_etiage",
"ode_observations_hydrologie", "ode_profondeur_moyenne_station",
"ode_observation_vegetation", "ode_observation_colmatage",
"ode_hab_id", "ode_haa_id",
"ode_omb_id", "ode_col_id",
"ode_gra_id_granulometrie_dominante", "ode_gra_id_granulometrie_accessoire",
"ode_observations_station", "ode_rep_id",
"ode_observations_repeuplement", "ode_lo3_id_station_canalisee",
"ode_lo3_id_station_naviguee", "ode_lo3_id_frequentation_sports_nautiques",
"ode_lo3_id_curage", "ode_faucardage",
"ode_lo4_id_deboisement_total", "ode_lo4_id_modification_morphologie",
"ode_lo4_id_extraction_granulats", "ode_observations_lits_rives"
)

op_env %<>% rename_all(
  list(~ gsub("ode_", "", make.names(colnames(op_env)))))
```

```{r}
ref_logique_3 <- tbl(con, in_schema("aspe", "ref_logique_3")) %>%
  collect()
logique_3_replacement <- c(
  "Renseignement inconnu" = "unknown",
  "Oui" = "yes",
  "Non" = "no"
)
ref_logique_3 %<>% 
  mutate(lo3_libelle = str_replace_all(lo3_libelle, logique_3_replacement))

replacement_lo3 <- ref_logique_3$lo3_libelle
names(replacement_lo3) <- ref_logique_3$lo3_id
```
```{r}
ref_logique_4 <- tbl(con, in_schema("aspe", "ref_logique_4")) %>%
  collect()
logique_4_replacement <- c(
  "Renseignement inconnu" = "unknown",
  "Oui \\(récent - depuis la dernière opération\\)" = "recent",
  "Oui \\(ancien\\)" = "ancient",
  "Non" = "no"                                
)
ref_logique_4 %<>% 
  mutate(lo4_libelle = str_replace_all(lo4_libelle, logique_4_replacement))

replacement_lo4 <- ref_logique_4$lo4_libelle
names(replacement_lo4) <- ref_logique_4$lo4_id
```

```{r}
ref_ombrage <- tbl(con, in_schema("aspe", "ref_ombrage")) %>%
  collect()
ombrage_replacement <- c(
  "Très Ombragé" = "very_shady",
  "Ombragé" = "shady",
  "Peu Ombragé" = "little_shade",
  "Éclairé" = "lit",
  "Très Eclairé" = "very_lit"
)
ref_ombrage %<>% 
  mutate(omb_libelle = str_replace_all(omb_libelle, ombrage_replacement))

replacement_ombrage <- ref_ombrage$omb_libelle 
names(replacement_ombrage) <- ref_ombrage$omb_id
```

```{r}
ref_colmatage <- tbl(con, in_schema("aspe", "ref_colmatage")) %>%
  collect()
colmatage_replacement <- c(
 "Pas de colmatage"     = "no",
 "Très léger colmatage" = "very_light",
 "Léger colmatage"      = "light",
 "Colmatage moyen"      = "medium",
 "Colmatage important"  = "important",
 "Colmatage complet"   = "full"
)
ref_colmatage %<>%
  mutate(col_libelle = str_replace_all(col_libelle, colmatage_replacement))
replacement_colmatage <- ref_colmatage$col_libelle
names(replacement_colmatage) <- ref_colmatage$col_id
```

```{r}
ref_repeuplement <- tbl(con, in_schema("aspe", "ref_repeuplement")) %>%
  collect()
repeuplement_replacement <- c(
 "Oui"            = "yes",
 "Non"            = "no",
 "Pas disponible" = "not_available"
)
ref_repeuplement %<>%
  mutate(rep_libelle = str_replace_all(rep_libelle, repeuplement_replacement))
replacement_repeuplement <- ref_repeuplement$rep_libelle
names(replacement_repeuplement) <- ref_repeuplement$rep_id
```

```{r}
op_env %<>%
  mutate_at(vars(contains("lo3")), list(~str_replace_all(., replacement_lo3))) %>%
  mutate_at(vars(contains("lo4")), list(~str_replace_all(., replacement_lo4))) %>%
  mutate(
    col_id = str_replace_all(col_id, replacement_colmatage),
    rep_id = str_replace_all(rep_id, replacement_repeuplement),
    omb_id = str_replace_all(omb_id, replacement_ombrage)
    )
replacement_env_op_col <- c(
  "lo3_id_secteur_debit_reserve"          = "instream_flow",
  "lo3_id_secteur_soumis_ecluse"          = "artificial_flow_variation",
  "lo3_id_soutien_etiage"                 = "replenishment_flow",
  "observations_hydrologie"               = "hydro_observations",
  "profondeur_moyenne_station"            = "avg_depth_station",
  "observation_vegetation"                = "vegetation_observations",
  "observation_colmatage"                 = "clogging_observations",
  "hab_id"                                = "habitat_id",
  "haa_id"                                = "eel_habitat_id",
  "omb_id"                                = "shade",
  "col_id"                                = "clogging",
  #"gra_id_granulometrie_dominante",
  #"gra_id_granulometrie_accessoire",
  "observations_station"                  = "station_observations",
  "rep_id"                                = "resettlement",
  "observations_repeuplement"             = "resettlement_observations",
  "lo3_id_station_canalisee"              = "chanelled_station",
  "lo3_id_station_naviguee"               = "sailed_station",
  "lo3_id_frequentation_sports_nautiques" = "nautical_sports",
  "lo3_id_curage"                         = "dredging",
  "faucardage"                            = "weed_cutting",
  "lo4_id_deboisement_total"              = "total_deforestation",
  "lo4_id_modification_morphologie"       = "artificial_morpho_modification",
  "lo4_id_extraction_granulats"           = "aggregates_extraction",
  "observations_lits_rives"               = "bank_bed_observations"
)

colnames(op_env) %<>% str_replace_all(., replacement_env_op_col)
save(op_env, file = mypath("data-raw", "fishing_op_build", "op_env.rda"))
```

```{r}
env_op_col <- c("id", "pente_ligne_eau", "section_mouillee",
  "durete_totale", "temp_max_moyenne_eau", "temp_air_bassin_versant",
  "precipitation_bassin_versant", "amplitude_thermique_air_station",
  "temperature_air_station", "commentaire")
op_env2 <- select(op, env_op_col)
# Convert columns in english
col_replacement <- c(
"pente_ligne_eau" = "slope",
"section_mouillee" = "width",
"durete_totale" = "water_hardness",
"temp_max_moyenne_eau" = "water_avg_30d_max_temp",
"temp_air_bassin_versant" = "air_avg_temp_basin",
"precipitation_bassin_versant" = "avg_rainfall_basin",
"amplitude_thermique_air_station" = "air_thermal_amplitude",
"temperature_air_station" = "air_avg_temp",
"commentaire" = "comment"
)
colnames(op_env2) %<>% str_replace_all(., col_replacement)
```

```{r}
op_env2 %>%
  filter(water_avg_30d_max_temp <= 0) %>%
  select(id, air_avg_temp, water_avg_30d_max_temp, air_thermal_amplitude)
# A lot of 0 in temp_max_moyenne_eau, looks very strange
# 9720 op over 26800: 36% des op 
# I guess that those data were not measured:
op_env2 %<>%
  mutate(water_avg_30d_max_temp = ifelse(water_avg_30d_max_temp <= 0, NA, water_avg_30d_max_temp)) %>%
  rename(opcod = id)

op_env %<>%
  rename(opcod = ope_id)

op_env %<>% left_join(op_env2, by = "opcod")

save(op_env, file = mypath("data-raw", "fishing_op_build", "op_env.rda"))
```

# Habitat

```{r}
op_hab <- tbl(con, in_schema("aspe", "habitat")) %>%
  filter(hab_id %in% op_env$habitat_id) %>%
  collect()
colnames(op_hab)
```

## Collect references 

```{r}
replace_abundance <- c(
  "Présence non caractérisée" = "NA",
  "Indéterminable" = "NA",
  "Nulle" = "null",
  "Faible" = "weak",
  "Moyenne" = "medium",
  "Importante" = "high",
  "Très importante" = "very_high")
ref_abun_saumon <- tbl(con, in_schema("aspe", "ref_type_abondance_saumon")) %>%
  collect() %>%
  select(tys_id, tys_libelle) %>%
  rename(abundance = tys_libelle) %>%
  mutate(abundance = str_replace_all(abundance, replace_abundance))
```

```{r}
ref_abun <- tbl(con, in_schema("aspe", "ref_type_abondance")) %>%
  collect() %>%
  select(tya_id, tya_libelle) %>%
  rename(abundance = tya_libelle) %>%
  mutate(abundance = str_replace_all(abundance, replace_abundance))
```

```{r}
replace_shade <- c(
  "Rivière ou ambiance couverte \\(>90% d'ombrage\\)" = "covered",
  "Rivière ou ambiance assez couverte \\(50-90% d'ombrage\\)" = "quite_covered",
  "Rivière ou ambiance assez dégagée \\(10-50% d'ombrage\\)" = "quite_clear",
  "Rivière ou ambiance dégagée" = "clear"
)
ref_shade <- tbl(con, in_schema("aspe", "ref_ombrage_riviere")) %>%
  collect() %>%
  select(omr_id, omr_libelle) %>%
  rename(shade = omr_libelle, hab_omr_id = omr_id) %>%
  mutate(shade = str_replace_all(shade, replace_shade))
```

```{r}
replace_sinuosite <- c(
  "Cours d'eau rectiligne" = "straight",
  "Cours d'eau sinueux" = "sinuous", 
  "Cours d'eau très sinueux" = "very_sinuous",
  "Cours d'eau méandriforme" = "meandering"
)
ref_sinuosite <- tbl(con, in_schema("aspe", "ref_sinuosite")) %>%
  collect() %>%
  select(sin_id, sin_libelle) %>%
  rename(sinuosite = sin_libelle, hab_sin_id = sin_id) %>%
  mutate(sinuosite = str_replace_all(sinuosite, replace_sinuosite))
```


```{r}
op_hab %<>%
  left_join(ref_shade, by = "hab_omr_id") %>%
  left_join(ref_sinuosite, by = "hab_sin_id") %>%
  left_join(
    rename(ref_abun, hab_tya_id_trous_fosses = tya_id, hole_pit = abundance),
    by = "hab_tya_id_trous_fosses") %>%
  left_join(
    rename(ref_abun, hab_tya_id_sous_berges = tya_id, under_bank = abundance),
    by = "hab_tya_id_sous_berges") %>%
  left_join(
    rename(ref_abun, hab_tya_id_abris_rocheux = tya_id, rock_shelter = abundance),
    by = "hab_tya_id_abris_rocheux") %>%
  left_join(
    rename(ref_abun, hab_tya_id_embacles_souches = tya_id, logjam_stumps = abundance),
    by = "hab_tya_id_embacles_souches") %>%
  left_join(
    rename(ref_abun, hab_tya_id_abri_vegetal_aquatique = tya_id, aqua_vg_shelter = abundance),
    by = "hab_tya_id_abri_vegetal_aquatique") %>%
  left_join(
    rename(ref_abun, hab_tya_id_vegetation_bordure = tya_id, edge_vg = abundance),
    by = "hab_tya_id_vegetation_bordure") %>%
  left_join(
    rename(ref_abun_saumon, hab_tys_id_vegetation_aquatique = tys_id, aqua_vg = abundance),
    by = "hab_tys_id_vegetation_aquatique") %>%
  select(
    -hab_omr_id,
    -hab_sin_id,
    -hab_tya_id_trous_fosses,
    -hab_tya_id_abris_rocheux,
    -hab_tya_id_sous_berges,
    -hab_tya_id_embacles_souches,
    -hab_tya_id_abri_vegetal_aquatique,
    -hab_tya_id_vegetation_bordure,
    -hab_tys_id_vegetation_aquatique
  )
```

## Add operation code 

```{r}
op_hab %<>%
  rename(habitat_id = hab_id) %>%
  left_join(select(op_env, opcod, habitat_id),
    by = "habitat_id") %>%
  select(-habitat_id) %>%
  select(opcod, everything())

mysave(op_hab, dir = mypath("data-raw"))
```

# Station

## Sampling point 

```{r}
sampling_point <- tbl(con, in_schema("aspe", "point_prelevement")) %>%
  filter(pop_id %in% op$pop_id) %>%
  collect()
sampling_point %<>% rename_all(
  list(~ gsub("pop_", "", make.names(colnames(sampling_point)))))
sampling_point_col <- c(
  "id", "sta_id", "code_sandre",
  "geometrie", "typ_id", "coordonnees_x", "coordonnees_y",
  "lieu_dit", "localisation_precise", "distance_mer",
  "distance_maree_dynamique", "nom_bassin", "fog_id",
  "ocs_id", "zoh_id", "cap_id", "largeur_lit_mineur",
  "unh_id", "distance_source", "altitude", "pente_ign_cours_eau",
  "surface_bassin_versant_amont", "temperature_moyenne_janvier",
  "temperature_moyenne_juillet") 
sampling_point %<>% select(sampling_point_col)
```

### NA station

```{r}
filter(sampling_point, is.na(sta_id) & is.na(code_sandre)) 
```


## Station

```{r}
station <- tbl(con, in_schema("aspe", "station")) %>%
  collect()
station %<>% rename_all(
  list(~ gsub("sta_", "", make.names(colnames(station)))))
replacement_station_col <- c( 
"code_sandre" = "sandre_code",
"com_code_insee" = "insee_town_code",
"point_km_aval" = "down_km_point",
"localisation_precise" = "precise_location",
"code_national_masse_eau"= "body_water_code",
"geometrie" = "postgis",
"coordonnees_x" = "x",
"coordonnees_y" = "y"
)
colnames(station) %<>% str_replace_all(., replacement_station_col)
```

### References projection type

```{r}
ref_type_proj <- tbl(con, in_schema("aspe", "ref_type_projection")) %>%
  collect()
ref_type_proj %<>%
  select(typ_id, typ_libelle) %>%
  rename(proj_type = typ_libelle)
```
```{r}
station %<>%
  left_join(., ref_type_proj) %>%
  select(-typ_id)
unique(station$proj_type)

```

### Region, departement and town 


```{r}
region <- tbl(con, in_schema("aspe", "region")) %>%
  collect() %>%
  rename(region = reg_libelle, dep_reg_code_insee = reg_code_insee) %>%
  select(-reg_ordre_affichage)
```


```{r}
dept <- tbl(con, in_schema("aspe", "departement")) %>%
  collect() %>%
  rename(com_dep_code_insee = dep_code_insee, department = dep_libelle) %>%
  left_join(region) %>%
  select(com_dep_code_insee, department, region)
```

```{r}
town <- tbl(con, in_schema("aspe", "commune")) %>%
  collect() %>%
  rename(town = com_libelle, insee_town_code = com_code_insee)

town %<>%  
  left_join(dept) %>%
  select(-com_dep_code_insee)
```

```{r}
station %<>%
  left_join(town) %>%
  select(- insee_town_code)
```


```{r}
hydro_type <- tbl(con, in_schema("aspe", "ref_entite_hydrographique")) %>%
  collect() %>%
  select(enh_id, enh_libelle) %>%
  rename(hydrographic_entity = enh_libelle)

station %<>%
  left_join(hydro_type) %>%
  select(-enh_id)
```


### NA station

Some `sampling_point` does not have a station id (`sta_id`), sandre code
(`code_sandre`). We cannot retrieve the station directly without one or the
other information.

```{r}
na_station <- filter(sampling_point,
  is.na(sta_id))
# But 6000 operations do not have station ids...
filter(sampling_point, is.na(sta_id) & is.na(code_sandre)) 
# 4000 have no sandre code and no station id
```

There are no stations where the stations have no id but a sandre code: 

```{r}
filter(sampling_point, is.na(sta_id) & !is.na(code_sandre)) 
```


### Projection

```{r}
library(sf)
unique(station$proj_type)
EPSG <- rgdal::make_EPSG()
EPSG[grep("RGF93 / Lambert-93", EPSG$note), 1:2]
EPSG[grep("RGFG95 / UTM zone 22", EPSG$note), 1:2]
EPSG[grep("RGR92 / UTM zone 40", EPSG$note), 1:2]
EPSG[grep("RRAF 1991 / UTM zone 20", EPSG$note), 1:2]
EPSG[grep("RGM04 / UTM zone 38", EPSG$note), 1:2]
```

```{r}
crs_correspondance <- c(
  "RGF93 / Lambert 93" = "2154",
  "RGFG95 / UTM 22" = "2972",
  "RGR92 / UTM 40" = "2975",
  "RRAF 91 \\(WGS84\\) / UTM 20" = "4559",
  "RGM04 / UTM 38" = "4471" 
)
station %<>%
  mutate(crs = str_replace_all(proj_type, crs_correspondance),
    crs = as.integer(crs))
station %<>%
  group_by(crs) %>%
  nest() %>%
  mutate(data = map2(data, crs,
      function (df, crs) {
	temp <- st_as_sf(df, crs = crs, coords = c("x", "y")) 
	st_transform(temp, crs = 4326)
      }
      ))

station <- do.call(rbind, station$data)
mapview::mapview(station)@map
```

Many station are outside metropolitan France. For the moment, we will suppress
them.

```{r}
load(mypath("data", "region_polygon.rda"))
plot(st_geometry(region_polygon))
plot(st_geometry(station["id"]), add = TRUE)

# Buffer in dec degree: 0.1° = 11km
region_buffer <- st_buffer(region_polygon, dist = .05)
station_in_metro <- st_within(station, region_buffer)
test <- purrr::map(station_in_metro, function(x) {
  if (length(x) == 0) { FALSE } else { TRUE }
    })
station_in_metro <- slice(station, which(test == TRUE)) 

plot(st_geometry(region_polygon))
plot(st_geometry(station), add = TRUE)
plot(st_geometry(station_in_metro), col = "red", add = TRUE)

station <- station_in_metro
save(station, file = mypath("data-raw", "fishing_op_build", "station.rda"))
```

## Add station id to fishing operation 

Let first take only the sampling points that have a station id

```{r}
sampling_point %<>%
  filter(sta_id %in% station$id)
```


```{r}
if (any(colnames(op) %in% "station")) {
  op %<>% select(-station)
}
station_id <- select(sampling_point, id, sta_id) %>%
  rename(pop_id = id, station = sta_id)
op %<>%
  left_join(., station_id)

op %<>% select(id, date, station, protocol, everything()) %>%
  rename(opcod = id, surface = surface_calculee)

```

### Filter op over station

Some op does not have identified stations. We have to filter them

```{r}
before_nrow <- nrow(op)
op %<>% filter(!is.na(station))
cat(round((before_nrow - nrow(op)) / before_nrow * 100),
  "% of the operations do not have identified stations.\n")
mysave(op, dir = mypath("data-raw", "fishing_op_build"), overwrite = TRUE)
```

# Exploration

Let's check the number of operation by year: 
```{r}
op_time <- op %>%
  mutate(year = year(date)) %>% 
  group_by(year) %>%
  summarise(n = n())
ggplot(op_time, aes(x = year, y = n)) +
  geom_line() +
  geom_point() +
  ylim(0, NA)
```

## Point prelevement 

```{r}
pre_ele <- tbl(con, in_schema("aspe", "prelevement_elementaire"))
pre_ele
```

```{r}
ref_pre_ele <- tbl(con, in_schema("aspe", "ref_type_prelevement_elementaire"))
ref_pre_ele %<>%
  rename(
    pre_tpe_id = tpe_id,
    type_prelevement = tpe_libelle) %>%
  select(-tpe_ordre_affichage)
```

We do not want to keep ambiance sampling:

```{r}
pre_ele <- left_join(pre_ele, ref_pre_ele) %>%
  select(-pre_tpe_id, -pre_duree) %>%
  filter(type_prelevement != "Ambiance")
```

### Passage

The number of passage:

```{r}
ref_pas <- tbl(con, in_schema("aspe", "passage")) %>%
  rename(pre_id = pas_id)
ref_pas
```

```{r}
# Join with pre_ele
pre_ele %<>% left_join(., ref_pas) %>%
  rename(passage_nb = pas_numero)
```

From Camille Rivière, operators are now doing fishing only once, so we keep only the
first passage of all the dataset: (I could check myself!)

```{r}
pre_ele %<>%
  filter(is.na(passage_nb)|passage_nb == 1)
```

### Point groups

```{r}
point_group <- tbl(con, in_schema("aspe", "groupe_points")) 
ref_point_group <- tbl(con, in_schema("aspe", "ref_type_groupe_points")) %>%
  rename(grp_tgp_id = tgp_id, point_type = tgp_libelle) %>%
  select(grp_tgp_id, point_type) %>%
  mutate(point_type = str_replace_all(point_type, "Points ", ""))
point_group %<>%
  left_join(., ref_point_group) %>%
  select(-grp_tgp_id) %>%
  select(grp_id, point_type, everything()) %>%
  rename_all(list(~ gsub("grp_nombre_points_", "nb_pt_", make.names(colnames(point_group)))))
point_group
```

I am not sure about what is the meaning of the points. I guess that that it is
the fishing protocol "partial by points". If I want to merge it with "partial
over bank", I have to select standard points in which 100 points were done in
bank.

```{r}
point_group %<>%
  filter(grp_tgp_id == "standards" & nb_pt_berge == 100)
```

### Filter elementary prelevement

We exclude all the prelevements that are not coming from standard point or that
are not in which all the points were not coming from the berge

```{r}
pre_ele %<>%
  filter(! (type_prelevement == "Groupe de points" & !(pre_id %in% collect(point_group)$grp_id)))
```

## Species 

```{r}
ref_espece <- tbl(con, in_schema("aspe", "ref_espece"))
```

```{r save species name}
species <- ref_espece %>%
  collect() %>%
  rename_all(list(~ gsub("esp_", "", make.names(colnames(ref_espece))))) %>%
  rename(
    code = code_alternatif,
    common_name = nom_commun,
    latin_name = nom_latin,
    max_size = taille_maximale) %>%
  select(code, common_name, latin_name, max_size)
mysave(species, dir = mypath("data"), overwrite = TRUE)
```


```{r}
ref_espece %<>%
  rename(lop_esp_id = esp_id, species = esp_code_alternatif) %>%
  select(lop_esp_id, species)
```
To join with lot

## Fish lot

```{r}
lot_poissons <- tbl(con, in_schema("aspe", "lot_poissons"))
lot_poissons

```

```{r}
ref_type_lot <- tbl(con, in_schema("aspe", "ref_type_lot"))
ref_type_lot %<>%
  rename(
    lop_tyl_id = tyl_id,
    type_lot = tyl_libelle) %>%
  select(-tyl_ordre_affichage)
```

```{r add species name}
lot_poissons <- left_join(lot_poissons, ref_type_lot) %>%
  left_join(., ref_espece) %>%
  select(- lop_tyl_id,- lop_esp_id) %>%
  select(lop_id, lop_pre_id, type_lot, species, everything()) 
lot_poissons
```



```{r, echo = FALSE, include = FALSE}
lot_testing <- purrr::map(collect(ref_type_lot)$type_lot, function (lot, data) {
  temp <- filter(data, type_lot == lot)
  sample_n(collect(temp), 1000)
    }, data = lot_poissons
  ) %>%
  do.call(rbind, .)

save(lot_testing, file = mypath("data-raw","fishing_op_build",
    "lot_testing.rda"))
```

### Individual measurements

```{r}
ind_measure <- tbl(con, in_schema("aspe", "mesure_individuelle"))
arrange(ind_measure, mei_lop_id)
ref_type_lot %<>%
  rename(
    lop_tyl_id = tyl_id,
    type_lot = tyl_libelle) %>%
  select(-tyl_ordre_affichage)
```

```{r echo = FALSE, include = FALSE}
ind_measure_testing <-
  filter(ind_measure, mei_lop_id %in% lot_testing$lop_id) %>%
  collect()
save(ind_measure_testing, file = mypath("data-raw","fishing_op_build",
    "ind_measure_testing.rda"))

filter(lot_poissons, type_lot == "N") %>%
  select(lop_id, lop_effectif) %>%
  collect() %>%
  slice(10)
filter(ind_measure, mei_lop_id == 3558592) %>% collect()
```

### Filter relevant lot and measurement

We select the lots that are in relevant elementary prevelement and in belonging
the operation that we select above.

```{r}
# All the relevant prelevement which are in the selected op:
pre_id_ok <- pre_ele %>%
  filter(pre_ope_id %in% op$id) %>%
  collect()
# filter: 
fish_lot <- lot_poissons %>%
  filter(lop_pre_id %in% pre_id_ok$pre_id) %>%
  collect()
save(fish_lot, file = mypath("data-raw","fishing_op_build", "fish_lot.rda"))
```

```{r add opcod to lot_poissons}
lot_opcod <- pre_id_ok %>%
  rename(lop_pre_id = pre_id, opcod = pre_ope_id) %>%
  select(lop_pre_id, opcod)

lot_id_opcod <- fish_lot %>%
  select(lop_id, lop_pre_id) %>%
  left_join(., lot_opcod) %>%
  select(lop_id, opcod)

mysave(lot_id_opcod, dir = mypath("data-raw","fishing_op_build"), overwrite =
  TRUE)
```

```{r select measurement}
# The measurement that are in the relevant lot:
lot_measure <- ind_measure %>%
  filter(mei_lop_id %in% fish_lot$lop_id) %>%
  collect()

save(lot_measure, file = mypath("data-raw","fishing_op_build", "lot_measure.rda"))
rm(fish_lot)
rm(lot_measure)
```

### Generate fish

All the fishes are measured in lot "N" and "I", but not in the other 
- lot S/L
- lot G
We have to build their size according to samples and assuming a normal
distribution.

It makes a very long time to run, so it is better to parallelize and to send to
cluster.
