---
title: "Review of Bonnafe code"
author: "Alain Danet"
date: "`r Sys.Date()`"
bibliography: references.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Review of Bonnafe code}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(knitr)
```

The objective of this vignette is to understand the code written by
@bonnafe_trophic_nodate.

## Overall structure

```{bash}
cd ../bonnafe_work
tree -d -L 2
```

## Data

### data_raw: Fishing operation dataset

Generation of the **cleaned** fishing operation data

- Script: `cleanData.r` 
- Data: `NEW_DATA.txt` 
- Output: `../bonnafe_work/data/raw_data/data_clean.txt`
  - **THE FILE**, really big
  - Variables:
```{r}
columns_meaning <- read_delim("../bonnafe_work/data/raw_data/Codes_colonne.txt",
  delim = ":", locale = locale("fr"), trim_ws = TRUE)
kable(columns_meaning)
```

Here are also the fish species:
```{r}
code_sp <- read_tsv("../bonnafe_work/data/raw_data/Code_sp.txt")
kable(code_sp)
```
- See the vignette `fish_op_explo.Rmd` for exploration of the data

### bib_data: Build the metaweb

Build the interaction matrices for F-F, F-R and R-R, merged in `AccMat_*.csv`

- Script: `../bonnafe_work/data/bib_data/AccMat_v0.r`
  - Could be easily factorize (I guess) 

#### Fish predation windows

```{r}
pred_win <- read_delim("../bonnafe_work/data/bib_data/F-F.csv", delim = ";",
  col_types = cols()) 
colnames(pred_win) <- str_replace_all(colnames(pred_win),
  c("par_" = "", "1" = "alpha", "2" = "beta"))
kable(pred_win)
```

Why $\beta$ and $\alpha$ are only partly filled ? Do some default parameters
values exist somewhere ? 

- Visualisation: `../bonnafe_work/data/bib_data/F-F.pdf`

#### Ontogenic Diet shift

- Fish:

```{r}
onto_diet_fish <- read_delim("../bonnafe_work/data/bib_data/ODSF.csv", delim = ";",
  col_types = cols())
kable(onto_diet_fish)
```

  - Variables: 
    - `stage`: ontogenic stage
    - `size` min and max: size range for a given life stage 
    - `light`
    - All the resources: from R1 to R7  
    - `fish`: piscivory
    -hypoth_ods`: different hypothesis to caracterise ODS:  
    - larvae hypoth: considering 1 stage for size $<$ 20mm
    - minimum size hypoth: considering stage 2 for size $\geq$ 20mm, i.e.
      considering that you need to be taller than 20mm to eat zoobenthos,
      same for stage 3 and eat fish
    - maximum size hypoth: maximum size to eat small prey as zooplankton and zoobenthos
    - genus hypoth: considering that ODS for this species is conserved at
      the genus level ?
    - age hypoth: to search ?
  
- Resources: `../bonnafe_work/data/bib_data/ODSR.csv`

```{r}
onto_diet_resources <- read_delim("../bonnafe_work/data/bib_data/ODSR.csv", delim = ";",
  col_types = cols())
kable(onto_diet_resources)
```

  - Variables: same as Fish diet data

```{r}
size_quantiles <- read_delim("../bonnafe_work/data/bib_data/size_quantiles.csv", delim = ";",
  col_types = cols())
kable(size_quantiles)
```

- Output: interaction matrices: `../bonnafe_work/data/bib_data/output/AccMat_*.csv`
  - file pattern: `AccMat_<criteria for class separation>_<number of classes>_<predation window (intraspe var or cst)>`
  - File used for the paper:  `AccMat_quant_9_PWvar_partOverlap.csv` **Not sure about the partOverlap but *I guess* it is necessary when you use midpoint of the size class**

- Two types of methods:
  1. With ontogenic stage: 1 class by ontogenic stage
  2. With size class (quantile or percentile methods): 1 class by nth quantile (depends on
     the number of class defined)
     - 15 ways to do it:
       - midpoint or range (with overlap or no overlap)?  
         - Overlap: when the biggest prey that can eat a predator is bigger
           than the smallest predator of the size class  
         - No overlap: The prey size class range is determine by the smallest
           predator: `minPredatorSize` L944-946 
       -predation window: constant or not (= same $\beta$ because $\alpha$ is
       always constant)
       - different numbers of size classes
- `piscivoryIndex` = {0,.5,1}; strength of the feeding interaction
- Determine Fish - Resources interaction:
  - If Ontogenic Feeding Stage min or max is in or around
    ]minPredatorSize,maxPredatorSize] predator size 
  - `fr_matrix`: L274

### network_data: Build local network and compute indices on them 

1. Extract local networks given:
  - Cumulated Trophic Network: `../bonnafe_work/data/bib_data/output/AccMat_*.csv` (See above)
  - Fishing data: `../bonnafe_work/data/raw_data/data_clean.txt`
  - Script: `../bonnafe_work/data/network_data/networks_v2.r`
    1. Assign each individual to a size class/species
    2. Do it for each fishing operation
    - Same as: `../bonnafe_work/data/network_data/networks_vBiomass.r`
  - Output: `../bonnafe_work/data/network_data/densityTable_*.csv`

2. Extract topology of local networks
  - Script: `../bonnafe_work/data/network_data/extractTNT.r`
    1. Compute degree, # of top and basal nodes: `n_w()`
    2. Trophic Level (TL) for each species: `getTL()`
  - Output: `../bonnafe_work/data/network_data/TNT_quant_*.txt`
3. Link TL & Biomass:
  - Script: `../bonnafe_work/data/network_data/getBTL.r`
  - Data: `densityTable_*.csv` and `TNT_*.txt` (see above for details)
  - Output: `../bonnafe_work/data/network_data/BTL_*.csv`

4. Network program: written in cpp
   - no idea about its role

### meta_data: join biomass, network indices and fishing operation datas

- What:
  - Get in the same file:
    - Biomass data: `../bonnafe_work/data/network_data/BTL_*.csv` 
    - Network topology indices: `../bonnafe_work/data/network_data/export_*.txt` 
    - Fishing operation data: `../bonnafe_work/data/raw_data/data_clean.txt`
- Script: `../bonnafe_work/data/meta_data/compileData_biomass.r`
- Output:
  `../bonnafe_work/data/meta_data/BiomassMetaData_quant_*.csv`

## Databases

- It contains databases used to build nodes and interaction links:
  - Aquaweb
  - Fishbase
  - Litterature 

I am not sure of how those database has been used. Apparently, there is one
folder for each species, containing a prey list. 


## Analysis

Contains analysis of the effect of temperature on the topology of the trophic
network on `TL`, `S`, `L.S.2`, `TLmax`, `Omni` and `BT_cor`.

- What:
  - Descriptive analysis
    - Correlation between variables
  - Statistical analysis
    - Mixed models
    - Model diagnostics
    - Plots

- Scripts:
  1. `../bonnafe_work/analysis/Temp_TNT/temperature_initiate.r` master script 
  2. To be continued...
     

- Data: `../bonnafe_work/data/meta_data/`
  - data for different trophic networks

# Notes 

## Predation window

The midpoint method retained by @bonnafe_trophic_nodate has one caveat is that
you can have a predator eating a prey bigger than it. @bonnafe_trophic_nodate
showed it in the code and tried to avoid those overlap with other methods than
the midpoint.

Why did they keep the midpoint instead of the others ?

# References
