---
title: "How to build the metaweb"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{How to build the metaweb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(magrittr)
devtools::load_all()
```

# Objectives

Here I describe how we are currently building metaweb and how it could be
improve.

# Preambule 

logic follow:

1. Setting the nodes:
  - Compute the size class
  - Determine resource nodes
  - Determine diet shift 
2. Set the interactions 
  1. Fish - Fish interactions
  - Theoretical prey size
  - Compute the piscivory index
  - Setting the links
  2. Fish - Resource interactions
  3. Resource - Resource interactions
3. Determine

Here the metaweb describes the presence and the absence of only feeding links between
(i) species, (ii) species-resources and (iii) resources-resources. It is called
a metaweb because it describes the theoretical feeding links between species that is
present in a given dataset regarless of the provenance of the species, i.e. if
they really cooccur or not.
The links
(i-ii) are based on size/weight relationship on the basis that your
size/weight^[I will use only size later for the sake of simplicity but it works
also for weight]
describes which/what you can eat and ontogenic diet shift.

The procedure described below is largely retake from the work of
@bonnafe_trophic_nodate.

- $C_i$: Number of class of the species $i$
- $c_j$: class $j$
- $n_i$: species $i$ 
- $N$: number of species
- $R$: number of resources 

# Set the nodes 

You can decide to set one node by species, it is the most simple. However,
species can have rather a large size range, and in keeping a low number of
nodes can make miss important features of the metaweb. In such a case, the
metaweb will not describe some important features like ontogenic diet shifts.
Choosing the number of nodes is like piking the magnification of the lens.

## Build size classes

The number of nodes by species corresponds to the number of classes $C$, the size
classes.

The classes can be determined by the method of the quantile (`?quantile()`) or percentile (`?seq()`).

```{r an example}
nb_class <- 5 
size <- seq(1, 100)

split_quant <- split_in_classes(size, class_method = "quantile", nb_class =
  nb_class)
split_percent <- split_in_classes(size, class_method = "percentile", nb_class =
  nb_class)
identical(split_quant, split_percent)
```
Quantile and percentile methods return the same output when data are uniformly
distributed. It is not the case when data are not, for example with normal
distribution.

```{r}
size <- rnorm(100, mean = 100, sd = 10)

split_quant <- split_in_classes(size, class_method = "quantile", nb_class =
  nb_class)
split_percent <- split_in_classes(size, class_method = "percentile", nb_class =
  nb_class)
identical(split_quant, split_percent)
```
Percentile method will build class of the same size equally distributed between
the minimum size `r min(size)` and the maximum size `r max(size)`. Quantile
method build classes containing the same number of observation. So, if $C = 2$,
the cutting point will be the median. In the case of the normal distribution,
quantile method created thiner classes (data are centered around the mean) and
wider classes at the extremes.

```{r}
method <- c("quantile", "percentile")
temp_obj <- list(split_quant, split_percent)
for (i in 1:2) {
  temp_obj[[ i ]] %<>% dplyr::mutate(method = method[i]) %>%
    gather(bound, values, lower, upper)
} 
temp2 <- dplyr::bind_rows(temp_obj[[1]], temp_obj[[2]])  %>%
  tidyr::spread(method, values)
knitr::kable(temp2)
```

When we have several species, the classes are computed with
`compute_classes()`.

Let me introduce the toy dataset that we will use. The pokemon are eating each
other (although it is not shown in the anime). The feeding interaction is 
determined by the size relationship (believe me!). So, we can build the
metaweb as other food web. The size values are arbitrary. 

```{r}
nb_class <- 4
pokemon_size <- tibble(
  species = rep(c("Pikachu", "Roucoups", "Dracofeu"), each = 10),
  size = c(seq(1,10), seq(11, 20), seq(101,110)))

size_classes <- compute_classes(pokemon_size, var = size, group_var = species, nb_class = nb_class,
  class_method = "percentile")

knitr::kable(size_classes)
```

We end up with species classification. Each class of each species ($c_{i,j}$)
will constitute a node. So here, with `r nb_class` classes and
`r nb_sp <- length(unique(pokemon_size$species)); nb_sp` species, we will have
`r nb_class*nb_sp` species nodes in the metaweb.

In @bonnafe_trophic_nodate they use the quantile methods.

We use **percentile method** because for us, it is justified that the size range
the most abundant get more weight and more precise feeding links resolution at
the metaweb scale because once the local networks will re-built, it does not
make sens that the resolution at which they will be solved depends on the
abundance distribution of the species at the regional scale. 
    
## Resource nodes

The resource nodes improve the biological reality of the metaweb. It differs
from the species nodes by the fact that we do not have information about neither
their size nor their abundance (in general). So, we do not generate class sizes
for those nodes. For the fish metaweb, the resource nodes are constituted of
non-fishes organisms such as, algae, phyto- & zoo-plankton, zoobenthos, ...
See `vignette("bonnafe_code_structure")` or `data(resource_diet_shift)`.

So, the resource nodes are defined by litterature and expert knowledge of the
system. Those nodes are really important for non-carnivorous fish species and
little fishes (regarless the species) for which the drawn feeding links will
come from only from the resource nodes.

For our toy metaweb, we know that Paras (crustacean) and Chetiflor (plant) are important resources for the little pokemons and vegetarian ones.  

```{r}
resource <- c("Chetiflor", "Paras")
```

# The links

## The diet 

### Fish diet


### Resource diet


```{r}
resource_shift <- tibble(
    species = c("Chetiflor", "Paras"),
    life_stage = c(0, 0),
    min = c(0, 0),
    max = c(0, 0),
    light = c(1, 0),
    Chetiflor = c(0, 1),
    Paras = c(0, 0),
    pisc = c(0, 0)
    )
knitr::kable()
```



## Hypotheses (reminder)

- determine piscivory is currently based on upper bound of the class
- Ontogenic diet class interval are closed ($[min;max]$), which is different from
  size class which is left open $]min;max]$: please unify
- Fish resource link is determined if the life stage is partly in or is
  including size class interval: [stage min size; stage max size] $\in$ [min
  class size; max class size] |  [stage min size; stage max size] $\supset$ [min
  class size; max class size]
- The `class_id = 1` is left open, meaning that the min size fishes will not
  belong to the size class. 

# References
