---
title: "How to build the metaweb"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{How to build the metaweb}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(magrittr)
devtools::load_all()
```

# Objectives

Here I describe how we are currently building metaweb and how it could be
improve.

# Preambule 

logic follow:

1. Setting the nodes:
  - Compute the size class
  - Determine resource nodes
  - Determine diet shift 
2. Set the interactions 
  1. Fish - Fish interactions
  - Theoretical prey size
  - Compute the piscivory index
  - Setting the links
  2. Fish - Resource interactions
  3. Resource - Resource interactions
3. Determine

Here the metaweb describes the presence and the absence of only feeding links between
(i) species, (ii) species-resources and (iii) resources-resources. It is called
a metaweb because it describes the theoretical feeding links between species that is
present in a given dataset regarless of the provenance of the species, i.e. if
they really cooccur or not.
The links
(i-ii) are based on size/weight relationship on the basis that your
size/weight^[I will use only size later for the sake of simplicity but it works
also for weight]
describes which/what you can eat and ontogenic diet shift.

The procedure described below is largely retake from the work of
@bonnafe_trophic_nodate.

- $C_i$: Number of class of the species $i$
- $c_j$: class $j$
- $n_i$: species $i$ 
- $N$: number of species
- $R$: number of resources 

# Set the nodes 

You can decide to set one node by species, it is the most simple. However,
species can have rather a large size range, and in keeping a low number of
nodes can make miss important features of the metaweb. In such a case, the
metaweb will not describe some important features like ontogenic diet shifts.
Choosing the number of nodes is like piking the magnification of the lens.

## Build size classes

The number of nodes by species corresponds to the number of classes $C$, the size
classes.

The classes can be determined by the method of the quantile (`?quantile()`) or percentile (`?seq()`).

```{r an example}
nb_class <- 5 
size <- seq(1, 100)

split_quant <- split_in_classes(size, class_method = "quantile", nb_class =
  nb_class)
split_percent <- split_in_classes(size, class_method = "percentile", nb_class =
  nb_class)
identical(split_quant, split_percent)
```
Quantile and percentile methods return the same output when data are uniformly
distributed. It is not the case when data are not, for example with normal
distribution.

```{r}
size <- rnorm(100, mean = 100, sd = 10)

split_quant <- split_in_classes(size, class_method = "quantile", nb_class =
  nb_class)
split_percent <- split_in_classes(size, class_method = "percentile", nb_class =
  nb_class)
identical(split_quant, split_percent)
```
Percentile method will build class of the same size equally distributed between
the minimum size `r min(size)` and the maximum size `r max(size)`. Quantile
method build classes containing the same number of observation. So, if $C = 2$,
the cutting point will be the median. In the case of the normal distribution,
quantile method created thiner classes (data are centered around the mean) and
wider classes at the extremes.

```{r}
method <- c("quantile", "percentile")
temp_obj <- list(split_quant, split_percent)
for (i in 1:2) {
  temp_obj[[ i ]] %<>% dplyr::mutate(method = method[i]) %>%
    gather(bound, values, lower, upper)
} 
temp2 <- dplyr::bind_rows(temp_obj[[1]], temp_obj[[2]])  %>%
  tidyr::spread(method, values)
knitr::kable(temp2)
```

When we have several species, the classes are computed with
`compute_classes()`.

Let me introduce the toy dataset that we will use. The pokemon are eating each
other (although it is not shown in the anime). The feeding interaction is 
determined by the size relationship (believe me!). So, we can build the
metaweb as other food web. The size values are arbitrary. 

```{r}
nb_class <- 4
pokemon_size <- tibble(
  species = rep(c("Pikachu", "Roucoups", "Dracofeu"), each = 10),
  size = c(seq(1,10), seq(11, 20), seq(101,110)))

size_classes <- compute_classes(pokemon_size, var = size, group_var = species, nb_class = nb_class,
  class_method = "percentile")

knitr::kable(size_classes)
```

We end up with species classification. Each class of each species ($c_{i,j}$)
will constitute a node. So here, with `r nb_class` classes and
`r nb_sp <- length(unique(pokemon_size$species)); nb_sp` species, we will have
`r nb_class*nb_sp` species nodes in the metaweb.

In @bonnafe_trophic_nodate they use the quantile methods.

We use **percentile method** because for us, it is justified that the size range
the most abundant get more weight and more precise feeding links resolution at
the metaweb scale because once the local networks will re-built, it does not
make sens that the resolution at which they will be solved depends on the
abundance distribution of the species at the regional scale. 
    
## Resource nodes

The resource nodes improve the biological reality of the metaweb. It differs
from the species nodes by the fact that we do not have information about neither
their size nor their abundance (in general). So, we do not generate class sizes
for those nodes. For the fish metaweb, the resource nodes are constituted of
non-fishes organisms such as, algae, phyto- & zoo-plankton, zoobenthos, ...
See `vignette("bonnafe_code_structure")` or `data(resource_diet_shift)`.

So, the resource nodes are defined by litterature and expert knowledge of the
system. Those nodes are really important for non-carnivorous fish species and
little fishes (regarless the species) for which the drawn feeding links will
come from only from the resource nodes.

For our toy metaweb, we know that Paras (crustacean) and Chetiflor (plant) are
important resources for the little pokemons and vegetarian ones.  

```{r}
resource <- c("Chetiflor", "Paras")
```

# Biological data

Before to move on the computation of the links, we will see how we can inform
our metaweb with some important biological details namely species and resource
diets, species carnivory (here i.e., eating other non-resource species) and
species theoretical prey sizes  

## The diet 

Many organisms change their diet along their life. The most caricatural exemple
can be found in insects, some have dramatic developmental shift (life stage
change) that are accompagnied by an equally important diet shift. 
 
We said earlier that the links were determined by the size relationship between
predators and preys. However, we can improve the biological realism of the
network by introducing size dependant diets, based on litterature, expert
knowledge and theoretical hypotheses^[For example, for fishes species, the
larvae hypothese states that a fish that has a size below 20cm will not
eat other things than protists].

So we will build here species and resource diet shift for the pokemon, based on
my (poor) expert knowledge.

### Species diet

The species diet is determined by known life stage which have lower and upper
bounds. It reads as follow (for the first line): *The Pikachu of stage 1 (< 3
) are eating only Chetiflor*.

```{r}
species_shift <- tibble(
  species = rep(c("Pikachu", "Roucoups", "Dracofeu"), each = 2),
  life_stage = rep(c(1, 2), times = 3),
  min = c(0, 3, 0, 13, 0, 103),
  max = c(3, Inf, 13, Inf, 103, Inf),
  Chetiflor = c(1, 0, 1, 1, 1, 0),
  Paras = c(0, 1, 0, 1, 1, 0),
  carn = c(0, 1, 0, 0, 0, 1)
    )
knitr::kable(species_shift)
```

### Resource diet

Same thing for the resource nodes.  However, we see that we do not set up life
stages for resource.  We can see that Chetiflor just feed on light and Paras on
Chetiflor. Please not that only the resource species will be include, so the
light will be not part of the network.

```{r}
resource_shift <- tibble(
  species = c("Chetiflor", "Paras"),
  life_stage = c(0, 0),
  min = c(0, 0),
  max = c(0, 0),
  light = c(1, 0),
  Chetiflor = c(0, 1),
  Paras = c(0, 0),
  carn = c(0, 0)
    )
knitr::kable(resource_shift)
```

## Carnivory

Now we have all the data that we needed to moving forward. For each species
class, we will determine if it is a carnivorous species. Right now, we implement only 
the "overlap" method. The given class is carnivorous if the size class overlap
the first carnivorous life stage.

```{r}
carn_classes <- compute_piscivory(
  size_class = size_classes,
  fish_diet_shift = species_shift,
  species = species,
  low_bound = min,
  upper_bound = max,
  fish = carn)
knitr::kable(carn_classes)
```

## Theoretical prey size 

Now that we know the diet of the species size classes, we can computed which
prey they can theoretically eat. Before to do this, we need to know the nature
of the relationship between the size of the predators and of its preys.
Among fish, numerous studies have shown that it exists a linear relationship
between the size of the predator and the size of a prey. The slope coefficient   
is different across species but if the data is not available, it is possible to
use generic parameters.
Two slope values are necessary to determine that is called the predation window. 

```{r}
## Let's determine the theoretical relationship for each species 
pred_prey_size <- tibble(
  species = c("Pikachu", "Roucoups", "Dracofeu"),
  lwr_slope = rep(.03, 3),
  upr_slope = rep(.45, 3)
) 
```

The predation window represents the relationship between the size predator and
the size of the prey. I show an example below.

```{r}
# Each species as column
spd_pkm <- group_by(pokemon_size, species) %>%
 mutate(id = row_number()) %>%
 spread(species, size)

## Get slopes
slopes <- filter(pred_prey_size, species == "Dracofeu") %>% 
  dplyr::select(lwr_slope, upr_slope) %>%
  unlist()

pred_win <- ggplot(spd_pkm, aes(x = Dracofeu, y = Roucoups)) +
  ylim(0, max(spd_pkm$Dracofeu)) +
  xlim(0, max(spd_pkm$Dracofeu)) +
  geom_blank() +
  geom_abline(intercept = 0, slope = slopes["lwr_slope"], color = "red") +
  geom_abline(intercept = 0, slope = slopes["upr_slope"], color = "red")

pred_win +
  labs(x = "Dracofeu size", y = "Prey size",
    title = "Predation window of Dracofeu")
```




# The links

The trophic links between species (species-species), species and resource
(species-resource), resource and resource (resource-resource) can be computed
following different rules. Here, I will present the "midpoint" and "overlap"
rules.

## species-species link

Before we have computed the carnivory and we have the theoretical prey size
range for each predator species (based on a linear relationship). We have to
choose a method to determine if there is or not a trophic link between a
predator and a prey size class.

There is two methods: *overlap* and *midpoint*. The *overlap* is the same than
the one for determining piscivory, an overlap between the classes. It means that
the minimal prey size for a predator would be each size contained in the
predation window of the predator. For a given predator size class, it
corresponds to ]`min(pred) * lwr_slope`; `max(pred) * upr_slope`]. According to
the *midpoint* method, the range of prey size that can be eaten by a predator
class is constrained by the mid of the predator size class. The range of prey
size is detemined as ]`mid(pred)* lwr_slope`; `mid(pred) * upr_slope`]. 

$$
x_{mid} = \frac{(x_{min} + x_{max})}{2}
$$

```{r}
## Let's compute the prey sizes for each predator
## with the midpoint method 
prey_size <- compute_prey_size(
  class_size = size_classes,
  pred_win = pred_prey_size,
  species = species,
  beta_min = lwr_slope,
  beta_max = upr_slope,
  pred_win_method = "midpoint")
knitr::kable(prey_size)
```

Now, that we have this table, we can determine the species-species links. A
species-species link is drawn if (i) the predator class is carnivorous and if
(ii) the correspondant prey class satisfies the characteristics of either the
*overlap* nor the *midpoint* method. 

If the *overlap* is used, the link is drawn if the range of a given prey class
overlap the prey range of the predator class. If the *midpoint* method is used,
the link is drawn if the mid of the given prey class fell in the prey range of
the predator class.  

- *overlap*: $L = 1 ssi ]N_{c, min};N_{c, max}] \in ]P_{c, min}*\beta_{min};P_{c, max}*\beta_{max}]$
- *midpoint* = $L = 1 ssi N_{c, mid} \in ]P_{c, mid}*\beta_{min};P_{c, mid}*\beta_{max}]$


```{r}
size_classes
## Draw an overlap
floor <- 0
draco_2 <- filter(size_classes, species == "Dracofeu", class_id == 2) %>%
  dplyr::select(lower, upper) %>% unlist
rou_2 <- filter(size_classes, species == "Roucoups", class_id == 3) %>%
  dplyr::select(lower, upper) %>% unlist
rou <- data.frame(x1 = floor, x2 = floor, y1 = rou_2["lower"], y2 = rou_2["upper"])
draco <- data.frame(x1 = draco_2["lower"], x2 = rou_2["upper"], y1 = floor, y2 = floor)

pred_range <- geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, colour = "segment"), colour = "blue", data = draco) 
prey_range <- geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, colour = "segment"), colour = "green", data = rou) 

## Theoretical prey size
coord_del_min <- with(draco, c(x2, x2, x2*slopes["lwr_slope"], x2*slopes["upr_slope"]))
coord_del_max <- with(draco, c(x1, x1, x1*slopes["lwr_slope"], x1*slopes["upr_slope"])) 
th_prey_coord <- rbind(coord_del_min, coord_del_max) %>% as.tibble
colnames(th_prey_coord) <- c("x1", "x2", "y1", "y2")
th_prey <- geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, colour = "segment"), colour = "blue", data = th_prey_coord)

pred_win + 
  pred_range +
  prey_range +
  th_prey 

```

## species-resource 

As there is no size for the resources, we assume that species class is
consumming the resource of the stage it belongs to.  As for species-species
trophic link, the species-resource link can be drawn either according to the
*overlap* nor the *midpoint* method. With the *overlap* method, a link is drawn
if there is an overlap between life stage boundaries and species size class.
With the *midpoint* method, there is a match where the mid of the species class
range  fell in life stage. A link is drawn between the given species class and
all the  resources of the given life stage.

- *overlap*: $L = 1 ssi ]L_{i, j, min};L_{i, j, max}] \in ]P_{c, min}; P_{c, max}] | ]L_{i, j, min};L_{i, j, max}] \supset ]P_{c, min}; P_{c, max}]$
- *midpoint* = $L = 1 ssi P_{c, mid} \in ]L_{i, j, min};L_{i, j, max}]$

## Other links

To complete the need, we still to define two more link types: resource-species
and resource-resource. Those types of link are straightforward to define.
Because we consider that resources cannot feed on species, there are not
resource-species links. The resource-resource links are defined in the resource
diet shift table, there are just to be reported.

# Midpoint or overlap

- f-r link: resource of several stage when *overlap* 

## Hypotheses (reminder)

- determine piscivory is currently based on upper bound of the class
- Explain downsize of each method: overlap, midpoint
- Ontogenic diet class interval are closed ($[min;max]$), which is different from
  size class which is left open $]min;max]$: please unify
- Fish resource link is determined if the life stage is partly in or is
  including size class interval: [stage min size; stage max size] $\in$ [min
  class size; max class size] |  [stage min size; stage max size] $\supset$ [min
  class size; max class size]
- The `class_id = 1` is left open, meaning that the min size fishes will not
  belong to the size class. 

# References
