---
title: "pressure_processing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pressure_processing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(magrittr)
mypath <- rprojroot::find_package_root_file
source(mypath("R", "misc.R"))
```

# Pressure data

- Contact data: Marie Sylvestre (FIRE, Paris) and Olivier Dezerald (ESE, Rennes)

The pressure data are coming from FIRE and [Naiaides](
http://www.naiades.eaufrance.fr/).

We have selected all the variables that have been used for the DCE (Directive
Cadre de l'Eau) which is a European policy. 

I am tented to use Naiaides more than FIRE data because I have choose FIRE
stations that were close to the fishing stations but looking at the raw data for
the nitrates in particular, Naiades data have a far more range.

- The scripts: `~/fishcom/data-raw/polluants/`
- The data: `~/fishcom/data-raw/polluants/naiades-data/`

There are several cleaning procedures for the data following Olivier's work
which include:
- Analyses should have date
- Analyses should have been performed on water 
- Qualification should be not "Incorrect"  

Some datas have values corresponding to the threshold of quantification and the
value can be high. Olivier was removing those datas if their values divided by
two were superior to the threshold good/moderate states.

For now I decide to not do this because I am not interested in quantifying
states but rather to explore variation in raw values. It could be a problem if
the methods vary a lot across labs and that this threshold of quantification
could lead to spurious trends. **To be discussed**

## Trends

The problem with temporal data is that they often have periodic trends. They are
often constraints by season in ecological data but it might not be the case for
some chemicals and their period could be different.
For exemple, temperature is highly seasonal but pesticides are applied at period
that correspond to each crop.

A method to detect the periodicity of temporal datas is the fourier
transformation. For each variable, we can detect the periodicity.
The periodicity can be used to compute a moving window averaging. The size of
the window correspond to the periodicity of the variable. The removal of
periodicity allows to see the trends.

- Two links to do that in R:
  - [Find periodicity](https://anomaly.io/detect-seasonality-using-fourier-transform-r/)
  - [Extract trends](https://anomaly.io/seasonal-trend-decomposition-in-r/)

We characterized the periodicity of each variable at the entire dataset (without
looking at the station).

```{r}
myload(fourier, dir = mypath("data-raw", "polluants"))
kable(filter(fourier, period_month < 14))
```

Most of the variables have a yearly period, we can detrend time series with
moving window of 12 months.

The moving window interpolation has been done in `03_moving_windows.R`
