---
title: "Stability and pressure"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Stability and pressure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(10, 10),
  echo = FALSE
)
library(tidyverse)
library(ggpmisc)
library(cowplot)
library(kableExtra)
library(magrittr)
library(igraph)
library(NetIndices)
library(tidygraph)
library(sf)
library(ggraph)
library(lubridate)
library(pander)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
#devtools::load_all()
theme_set(theme_alain())
```

```{r load dataset, include = FALSE}
#myload(yearly_press_interp_mv_avg, dir = mypath("data-raw", "polluants"))
myload(community_metrics, synchrony, temporal_press_polluants,
  press_metrics, temporal_community_metrics, op_analysis,
  dir = mypath("data"))

```

# Raw data

## All pollutants

```{r}
# Put units to present all the parameters
myload(polluant_units, dir = mypath("data-raw", "polluants", "naiades_data"))
kable(polluant_units)
```

## Press category

```{r}
myload(press_cat, dir = mypath("data-raw", "polluants"))
kable(press_cat)
```

## Press trough time

```{r}
ggplot(press_metrics, aes(y = press, x = year)) +
  stat_summary(fun.y = "mean", geom = "line") +
  stat_summary(geom="ribbon", fun.data=mean_cl_normal, colour=NA,alpha=0.1)+
  facet_wrap(~category, scales = "free_y")
```


## Between press correlation

```{r}
var_values <-  temporal_press_polluants %>%
  select(id, category, press) %>%
  spread(category, press) 

m <- cor(na.omit(select(var_values, -id)))

as.data.frame(round(m, 2)) %>%
  mutate_all(list(~cell_spec(., "html", color = ifelse(abs(.) > .65 & . != 1, "red",
	  "black")))) %>%
  mutate(variable = colnames(.)) %>%
  select(variable, everything()) %>%
  kable(format = "html", escape = F)
```

```{r}
library(ade4)
library(factoextra)

res.pca <- dudi.pca(na.omit(select(var_values, -id)),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)

eig_plot <- fviz_eig(res.pca)
```

```{r}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})
plot_grid(pca_plot[[1]], pca_plot[[2]], pca_plot[[3]], eig_plot)
```



I can delete some redondant variables 

```{r}
cat_to_rm <- c("nitrates", "phosphore", "mes", "disolved_oxygen",
  "matieres organiques", "ph", "flow", "industry", "pcb",
  "micropolluants organiques", "micropolluants mineraux", "hap")
temporal_press_polluants %<>%
  filter(!category %in% c(
      "matieres azotees", "other", "matieres phosphorees", "matieres
      organiques"))
```

```{r}
biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv)
biomass_com %<>%
  left_join(rename(temporal_press_polluants, station = id), by = "station")
biomass_com %<>% na.omit()

pca_press_data <- biomass_com %>%
  select(station, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press)
```

```{r, fig.dim = c(4, 4)}
res.pca <- dudi.pca(na.omit(select(pca_press_data, -station)),
  scannf = FALSE,   # Hide scree plot
  nf = 5            # Number of components kept in the results
)

fviz_eig(res.pca)
```

```{r, fig.dim = c(10, 7)}
pca_plot <- lapply(list(c(1,2), c(1, 3), c(1, 4), c(3, 2), c(4, 2), c(4, 3)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})
plot_grid(plotlist = pca_plot)
```

# Press and stability

```{r}
p1 <- ggplot(biomass_com, aes(x = press, y = log(biomass_stab))) +
  geom_point() +
  facet_wrap(~ category, scales = "free_x") +
  labs(x = "Scaled press", y = "Biomass stability")
p1
```


## Model


### Biomass stability

```{r}

mod_press_data <- biomass_com %>%
  select(station, biomass_stab, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press)

model <- lm(log10(biomass_stab) ~ .*richness_med,
  select(mod_press_data, -station))
pander(summary(model))
#par(mfrow = c(2,2))
#plot(model)
```
```{r}
#model$coefficients[["richness_med"]]
coeff <- broom::tidy(model) %>%
  mutate(
    ci5 = estimate - 1.96 * std.error,
    ci95 = estimate + 1.96 * std.error,
    est.10 = 10^estimate,
    ci5.10 = 10^ci5,
    ci95.10 = 10^ci95
  )

```


Biomass stability decreased with the increase of species richness and
temperature (). As species richness and temperature co-vary, it is not easy to
disentangle those two effects.
Does temperature increase species richness which in turn decreases biomass
stability? Does the effects of species richness are an artefact of temperature?

```{r}
formula <- y ~ x 
p1 <- ggplot(mod_press_data, aes(x = temperature, y = log(richness_med))) +
  geom_smooth(method = 'lm', formula = formula) +
  geom_point() +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  labs(x = "Temperature (°C)", y = "Species richness")
p1
```


```{r}
car::vif(model)
#kable(vif_mod)
model <- lm(log10(biomass_stab) ~ .,
  select(mod_press_data, -station, -richness_med))
pander(summary(model))
car::vif(model)
```

```{r}
cor(na.omit(select(mod_press_data, -station, -biomass_stab)), method = "spearman") %>%
  round(., 2)
```

### Structural Equation Modeling

```{r}
options(width = 120)

cat_to_rm <- c("mes", "disolved_oxygen",
  "matieres organiques", "ph", "flow", "industry", "pcb",
  "micropolluants organiques", "micropolluants mineraux", "hap")
library(piecewiseSEM)
dsem <- biomass_com %>%
  select(station, biomass_stab, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press) %>%
  na.omit()

model <- psem(
  lm(log(biomass_stab) ~ richness_med * (DBO + fungicides + herbicides + insecticides + temperature), dsem),
  lm(richness_med ~ temperature + DBO + fungicides + herbicides + insecticides, dsem),
  lm(DBO ~ nitrates * phosphore, dsem),
  richness_med %~~% temperature,
  nitrates %~~% phosphore
  )
summary(model, .progressBar = F)
#hist(biomass_com$richness_med, breaks = seq(0, 25))
model2 <- psem(
  lm(log(biomass_stab) ~ richness_med + DBO + fungicides + herbicides + insecticides + temperature, dsem),
  lm(richness_med ~ temperature, dsem)
  )
summary(model2, .progressBar = F)
```


#### Spatial model

```{r, eval = FALSE}
library(SSN)
myload(ssn, dir = mypath("data-raw", "fish_station_ssn"))
ssn@obspoints@SSNPoints[[1]]@point.data <- left_join(
  ssn@obspoints@SSNPoints[[1]]@point.data,
  mod_press_data
)

#ssn <- SSN::importSSN(mypath("data-raw", "fish_station_ssn", "fish_station.ssn"), o.write = TRUE)
## Compute the weight of each streams lines when they merged:
#ssn <- SSN::additive.function(ssn, "H2OArea",
  #"afv_area")
## create distance matrix between pred and obs:
#SSN::createDistMat(ssn, o.write = TRUE)
#mysave(ssn, dir = mypath("data-raw", "fish_station_ssn"), overwrite = TRUE)

#formula <-  as.formula(
  #paste0("biomass_stab"," ~ ", 
    #paste0(colnames(select(mod_press_data, -station)), sep = " + ")
    #(str_c(colnames(select(mod_press_data, -station)), " + ")
    #cat(colnames(select(mod_press_data, -station)), sep = " + ")
  #)
#)
spmod <- glmssn(
  biomass_stab ~ richness_med * (DBO + flow + industry +
    polluants +
    temperature), ssn, family = "Gaussian", CorModels =
       c("LinearSill.tailup", "Mariah.taildown", "Exponential.Euclid"),
       use.nugget = TRUE, use.anisotropy = FALSE, addfunccol = "afv_area", trialscol = NULL)
summary(spmod)

model <- lm(biomass_stab ~ .*richness_med,
  select(mod_press_data, -station, -`matieres organiques`)) 
pander(summary(model))
plot(model)
```


### Persistance of biomass composition

```{r}
options(width = 80)
p1 <- ggplot(biomass_com, aes(x = press, y = log10(1/(betadiv)))) +
  geom_point() +
  facet_wrap(~ category, scales = "free_x") +
  labs(x = "Scaled press", y = "Log 10 of 1 / beta-diversity")
p1
```

```{r}
mod_press_data <- biomass_com %>%
  select(station, betadiv, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press)

model <- lm(betadiv ~ .*richness_med,
  select(mod_press_data, -station)) 
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```

### Median diversity

```{r}
p1 <- ggplot(biomass_com, aes(x = press, y = log10(1/(betadiv)))) +
  geom_point() +
  facet_wrap(~ category, scales = "free_x") +
  labs(x = "Scaled press", y = "Log 10 of 1 / beta-diversity")
p1
```

```{r}
mod_press_data <- biomass_com %>%
  select(station, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press)

model <- lm(richness_med ~ .,
  select(mod_press_data, -station)) 
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```

## With CV of press

### Stability


```{r}
mod_press_data <- biomass_com %>%
  select(station, biomass_stab, richness_med, category, cv_press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, cv_press)

model <- lm(biomass_stab ~ .*richness_med,
  select(mod_press_data, -station)) 
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```

### Persistance of community composition

```{r}
mod_press_data <- biomass_com %>%
  select(station, betadiv, richness_med, category, cv_press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, cv_press)

model <- lm(betadiv ~ .*richness_med,
  select(mod_press_data, -station)) 
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```


### Model by hydrographic region

```{r}
myload(my_hydro_basin, dir = mypath("data-raw", "ssn_interpolation"))
myload(station_analysis, dir = mypath("data"))
station <- station_analysis %>%
  select(id) %>%
  st_transform(crs = 2154)

mask <- sf::st_intersects(station, my_hydro_basin)

station$basin <- purrr::map_chr(mask, function (x){
  if (length(x) == 0) {
    return(as.integer(NA))
  } else {
    return(my_hydro_basin[["basin_name"]][[x]])
  }
  })
```

#### Stability of biomass

```{r}
mod_by_basin <- biomass_com %>%
  select(station, biomass_stab, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press) %>%
  left_join(rename(station, station = id), by = "station") %>%
  select(-geometry, -station) %>%
  filter(!is.na(basin))

mod_by_basin %<>%
  group_by(basin) %>%
  nest()

model_basin <- function(df) {
  lm(biomass_stab ~ richness_med*., data = df)
}

mod_by_basin %<>%
  mutate(
    model = map(data, model_basin),
    coeff = map(model, broom::tidy)
  )

kable(unnest(mod_by_basin, coeff))
```

#### Persistance of the community

```{r}
mod_by_basin <- biomass_com %>%
  select(station, betadiv, richness_med, category, press) %>%
  filter(!category %in% cat_to_rm) %>%
  spread(category, press) %>%
  left_join(rename(station, station = id), by = "station") %>%
  select(-geometry, -station) %>%
  filter(!is.na(basin))

mod_by_basin %<>%
  group_by(basin) %>%
  nest()

model_basin <- function(df) {
  lm(betadiv ~ richness_med*., data = df)
}

mod_by_basin %<>%
  mutate(
    model = map(data, model_basin),
    coeff = map(model, broom::tidy)
  )

kable(unnest(mod_by_basin, coeff))
```

# Link between stability and network structure


```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
avg_network <- temporal_network_metrics %>%
  select_at(vars(matches("med|station")))

biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv)
stab_biomass_net_med <- left_join(avg_network, select(biomass_com, station,
    biomass_stab, richness_med), by = "station") %>%
  gather(metrics, values, colnames(select_at(., vars((matches("med")))))) %>%
  mutate(metrics = str_replace(metrics, "_med", "")) %>%
  filter(metrics != "nbnode")

ggplot(stab_biomass_net_med, aes(y = biomass_stab, x = values)) +
  facet_wrap(~ metrics, scale = "free_x")+
  geom_point()
```

```{r}
mod_press_data <- stab_biomass_net_med %>%
  spread(metrics, values)

model <- lm(log(biomass_stab) ~ .,
  select(mod_press_data, -station, -richness, -connectance)) 
pander(summary(model))
car::vif(model)
par(mfrow = c(2,2))
plot(model)
```



## With synchrony

### Synchrony

```{r}
mod_sync_net <- synchrony %>%
  left_join(mod_press_data)
model <- lm(synchrony ~ .,
  select(mod_sync_net, synchrony, connectance_corrected, max_troph_level,
     modularity, nestedness, richness))
car::vif(model)
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```

### CV_sp

```{r}
mod_sync_net <- synchrony %>%
  left_join(mod_press_data)
model <- lm(log10(cv_sp) ~ .,
  select(mod_sync_net, cv_sp, connectance_corrected, max_troph_level,
     modularity, nestedness, richness))
car::vif(model)
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```

# Distribution of biomass by trophic level

```{r}
biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv)
biomass_com %<>%
  left_join(rename(temporal_press_polluants, station = id), by = "station")
biomass_com %<>% na.omit()
myload(network_analysis, dir = mypath("data", "classes")) 
troph_bm <- network_analysis %>%
  unnest(composition) 

compute_troph_lvl_moment <- function(
  .data = NULL,
  group_var = opcod,
  weight = biomass,
  trait = troph_level) {
  group_var <- enquo(group_var)
  weight <- enquo(weight)
  trait <- enquo(trait)

  .data %>%
    group_by(!!group_var) %>%
    summarise(
      tot_weight = sum(!!weight),
      cwm = sum(!!weight / tot_weight * !!trait),
      cwv = sum(!!weight / tot_weight * (!!trait - cwm)^2),
      cwk = sum(!!weight / tot_weight * (!!trait - cwm)^4 / cwv^2),
      cws = sum(!!weight / tot_weight * (!!trait - cwm)^3 / cwv^(3/2))
    )
}
troph_lvl_moment <- compute_troph_lvl_moment(troph_bm)%>%
  left_join(select(op_analysis, station, opcod, date)) %>%
  filter(! cwv < 0.01)
ggplot(select(troph_lvl_moment, -opcod, -tot_weight, -date) %>% gather(moment, value, cwm:cws),
  aes(x = value)) +
  geom_histogram() +
  facet_wrap(~ moment, scales = "free_x")
```

## How vary distribution of trophic level through time

```{r}
time_moment <- select(troph_lvl_moment, -opcod, -tot_weight) %>%
  gather(moment, value, cwm:cws) %>%
  filter(station %in% sample(.data[["station"]], 10)) %>%
  mutate(station = as.character(station))

ggplot(time_moment,
  aes(x = date, y = value, color = station)) +
  geom_line() +
  geom_point() +
  facet_wrap(~ moment, scales = "free_y")

```

```{r}
biomass_moment <- troph_lvl_moment %>%
  gather(moment, value, cwm:cws) %>%
  filter(station %in% sample(.data[["station"]], 10)) %>%
  mutate(station = as.character(station))


ggplot(biomass_moment, aes(x = value, y = log10(tot_weight))) +
  facet_wrap(~ moment, scales = "free_x") +
  geom_point(aes(color = station))

```
```{r}
samp_opcod <- sample(troph_bm[["opcod"]], 12)
dist_troph_bm <- troph_bm %>% 
  left_join(select(op_analysis, station, opcod, date)) %>%
  filter(opcod %in% samp_opcod)

temp_moments <- troph_lvl_moment  %>%
  filter(opcod %in% samp_opcod) %>%
  select(opcod, cwm:cws) %>%
  mutate(troph_level = 3.5, biomass = 20) %>%
  mutate_at(vars(starts_with("cw")), ~round(., 2)) %>%
  mutate(label = paste("M = ", cwm, "\nV = ", cwv, "\nK = ", cwk , "\nS = ", cws))

ggplot(dist_troph_bm, aes(x = troph_level, weight = log10(biomass))) +
  geom_histogram() +
  facet_wrap(~opcod) +
  labs(x = "Trophic level", y = "Log10 of Biomass") +
  geom_text(data = temp_moments, aes(x = troph_level, y = biomass, label = label))
```


```{r}
stab_moment <- troph_lvl_moment %>%
  gather(moment, value, cwm:cws) %>%
  group_by(station, moment) %>%
  summarise(med = median(value), cv = sd(value) / mean(value)) %>%
  left_join(synchrony %>%
  select(station, cv_com, cv_sp, synchrony)) %>%
  gather(sync, value, cv_com, cv_sp, synchrony)

ggplot(stab_moment, aes(x = med, y = value)) +
  facet_grid(sync~moment, scales = "free_x") +
  geom_point() +
  labs(title = "Stability metrics versus the moment of biomass distribution by
    trophic level"
  )
```

```{r}
dist_troph_bm <- troph_bm %>% 
  left_join(select(op_analysis, station, opcod, date)) %>%
  filter(opcod %in% sample(.data[["opcod"]], 12))# %>%
  #group_by(opcod, troph_level) %>%
  #summarise(biomass = sum(biomass))

ggplot(dist_troph_bm, aes(x = troph_level, weight = log10(biomass))) +
  geom_histogram() +
  facet_wrap(~opcod)
```

### Coefficients of variation

```{r}
moment_model_biomass <- stab_moment %>%
  ungroup() %>%
  gather(metric, med_cv, med, cv) %>%
  unite(moment, metric, moment, metric,sep= "_") %>%
  spread(moment, med_cv) %>%
  spread(sync, value) %>%
  select(-station)

model <- lm(1/cv_com ~ .,
  select(moment_model_biomass, -matches("med"), -cv_sp, -synchrony))
pander(summary(model))
car::vif(model) #Too much colinearity

model <- lm(log10(1/cv_com) ~ .,
  select(moment_model_biomass, -matches("med"), -cv_sp, -synchrony))
car::vif(model) # ok
pander(summary(model))
par(mfrow = c(2,2))
plot(model)

```

### Median 

```{r}
model <- lm(log10(1/cv_com) ~ .,
  select(moment_model_biomass, -matches("cv_cw"), -med_cws, -synchrony, -cv_sp))
car::vif(model) # ok
pander(summary(model))
par(mfrow = c(2,2))
plot(model)
```


# Distribution of species richness by trophic level

```{r}

biomass_com <- temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv)
biomass_com %<>%
  left_join(rename(temporal_press_polluants, station = id), by = "station")
biomass_com %<>% na.omit()
myload(network_analysis, dir = mypath("data", "classes")) 
troph_bm <- network_analysis %>%
  unnest(composition)
troph_div <- troph_bm %>%
  mutate(species = str_sub(sp_class, 1, 3)) %>%
  group_by(opcod, troph_level) %>%
  summarise(
    richness = length(unique(species)),
    nb_node = length(unique(sp_class))
  )

troph_div_moment <- compute_troph_lvl_moment(troph_div, group_var = opcod,
  weight = richness, trait = troph_level) %>%
  left_join(select(op_analysis, station, opcod, date)) %>%
  filter(! cwv < 0.01)

```

```{r}
time_moment <- select(troph_div_moment, -opcod, -tot_weight) %>%
  gather(moment, value, cwm:cws) %>%
  filter(station %in% sample(.data[["station"]], 10)) %>%
  mutate(station = as.character(station))

ggplot(time_moment,
  aes(x = date, y = value, color = station)) +
  geom_line() +
  geom_point() +
  facet_wrap(~moment, scales = "free_y")

```

```{r}
biomass_moment <- troph_div_moment %>%
  gather(moment, value, cwm:cws) %>%
  filter(station %in% sample(.data[["station"]], 10)) %>%
  mutate(station = as.character(station))

ggplot(biomass_moment, aes(x = value, y = log10(tot_weight))) +
  facet_wrap(~ moment, scales = "free_x") +
  geom_point(aes(color = station))
```

```{r}
stab_moment <- troph_div_moment %>%
  gather(moment, value, cwm:cws) %>%
  group_by(station, moment) %>%
  summarise(med = median(value)) %>%
  left_join(temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv))

formula <- y ~ x 
ggplot(stab_moment, aes(x = med, y = biomass_stab)) +
  facet_wrap(~moment, scales = "free_x") +
  geom_smooth(method = 'lm', formula = formula) +
  stat_poly_eq(
    formula = formula,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_point()
```

```{r}
moment_model <- stab_moment %>%
  ungroup() %>%
  select(biomass_stab, moment, med) %>%
  spread(moment, med)
cor(moment_model)

```

```{r}
model <- lm(biomass_stab ~ ., moment_model)
pander(summary(model))
car::vif(model) #Too much colinearity

model <- lm(log10(biomass_stab) ~ cwk+cwv+cws, moment_model)
car::vif(model) # ok
pander(summary(model))
par(mfrow = c(2,2))
plot(model)

```

```{r}
troph_level_dist <- bind_rows(
  mutate(troph_lvl_moment,variable = "biomass"),
  mutate(troph_div_moment,variable = "richness")
  ) %>%
  gather(moment, value, cwm:cws) %>%
  select(opcod, station, variable, moment, value) %>%
  group_by(station, variable,moment) %>%
  summarise(med = median(value), cv = sd(value) / mean(value)) %>%
  left_join(temporal_community_metrics %>%
  select(station, biomass_stab, richness_med, betadiv))

# Transform to get the stat model data
mod_tot_troph_dist <- troph_level_dist %>%
  ungroup() %>%
  gather(metric, value, med, cv) %>%
  #filter(moment != "cwm") %>% # Causes to multi colinéarity
  unite(moment, variable, moment, metric,sep= "_") %>%
  spread(moment, value) %>%
  select(biomass_stab, biomass_cwk_cv:richness_cwv_med)

#cor(mod_tot_troph_dist)

#model <- lm(log10(biomass_stab) ~ ., select(mod_tot_troph_dist,
    #-biomass_cws_med, - richness_cwm_med, -biomass_cwv_med)) 
#car::vif(model)
#pander(model)
```


```{r}
res.pca <- dudi.pca(na.omit(select(mod_tot_troph_dist, -biomass_stab)),
  scannf = FALSE,   # Hide scree plot
  nf = 4            # Number of components kept in the results
)

fviz_eig(res.pca)
pca_plot <- lapply(list(c(1,2), c(1, 3), c(3, 2)), function (axes) {
  fviz_pca_var(res.pca,
    axes = axes,
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )
})
plot_grid(plotlist = pca_plot)
```


```{r}
samp_opcod <- sample(troph_bm[["opcod"]], 12)
dist_troph_div <- troph_div %>% 
  left_join(select(op_analysis, station, opcod, date)) %>%
  filter(opcod %in% samp_opcod)

temp_moments <- troph_div_moment  %>%
  filter(opcod %in% samp_opcod) %>%
  select(opcod, cwm:cws) %>%
  mutate(troph_level = 3.5, richness = 4) %>%
  mutate_at(vars(starts_with("cw")), ~round(., 2)) %>%
  mutate(label = paste("M = ", cwm, "\nV = ", cwv, "\nK = ", cwk , "\nS = ", cws))

ggplot(dist_troph_div, aes(x = troph_level, weight = richness)) +
  geom_histogram() +
  facet_wrap(~opcod) +
  labs(x = "Trophic level", y = "Log10 of Biomass") +
  geom_text(data = temp_moments, aes(x = troph_level, y = richness, label = label))
```

```{r}
myload(temporal_network_metrics, dir = mypath("data", "classes"))
network_metrics
diet <- temporal_network_metrics %>%
  unnest(data) %>%
  select(station, diet, rel_biomass_med)

press <- temporal_press_polluants %>%
  filter(!category %in% cat_to_rm, category != "NA") %>%
  select(id, category, press) %>%
  rename(station = id)

press_diet <- left_join(diet, press, by = "station")

ggplot(press_diet, aes(x = press, y = log10(rel_biomass_med))) +
  facet_grid(diet ~ category, scales = "free_x") +
  geom_point()
```



