---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library('lubridate')
library(magrittr)
library(sf)
mypath <- rprojroot::find_package_root_file
source(mypath("R", "misc.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "plot_methods.R"))
myload(quality_data, dir = mypath("data-raw"))
```
```{r}
######################
#  Nitrate Bretagne  #
######################

myload(station_analysis, region_polygon, dir = mypath("data"))

bretagne <- filter(region_polygon, nom == "Bretagne") 
lgs <- st_within(station_analysis, st_transform(bretagne, crs = 2154))
mask <- lengths(lgs) > 0
bre_station <- filter(station_analysis, mask)
bre_prediction <- filter(prediction, id %in% bre_station$id) %>%
  filter(var_code == "NO3")

avg_year <- bre_prediction %>% group_by(year) %>% summarise(no3 = mean(avg_data))
ggplot(avg_year, aes(x = year, y = no3)) +
  geom_line()
  
ggplot(prediction, aes(x = avg_data)) +
  geom_histogram() +
  facet_wrap(~year, scales = "free_x")
summary(prediction$avg_data)

which(prediction$avg_data > 100)
resume <- quality_data %>%
  group_by(var_code) %>%
  summarise(resume = list(summary(value))) %>%
resume %>%
  unnest(resume)
hist(quality_data[quality_data$var_code == "NO3", ]$value)
resume[resume$var_code %in% "NO3", ][["resume"]]
resume[resume$var_code %in% "NO2", ][["resume"]]
resume[resume$var_code %in% "PO4", ][["resume"]]
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
