---
title: Species richness destabilizes trophic communities in freshwater ecosystems
author: Alain Danet, Maud Mouchet, Elisa Thébault and Colin Fontaine
date: \today 
output:
  pdf_document:
    fig_caption: true
bibliography: references.bib
---

```{r, echo = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.dim = c(7, 7),
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = FALSE
)

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```


# Abstract

# Introduction 

Cf blutghen for CVsp as portfolio and statistical averaging of species.
Synchrony as insurance hypothesis facing environmental variations.

- Diversity - stability and diversity - biomass / productivity
  - well studied: both experimentally, empirically and theoretically
  - mecanisms:
    - stability: insurance (asynchrony),
    - diversity: overyielding (complementarity)
  - key papers: [@tilman_biodiversity_2006, @loreau_species_2008,
    @thibaut_understanding_2013, @may_will_1972]
  - BUT: less vertical diversity, trophic communities

- Vertical diversity and stability/biomass
  - well studied: theoretically and (experimentally, less)
  - mecanisms:
    - stability: top-down and bottom-up effect
    - biomass: top-down and bottom-up effects (pyramids of biomass)
  - key papers:[@barbier_pyramids_2019, @shanafelt_david_w._stability_nodate]
  - BUT: local stability, little systems 

- Environment can drive stability and biomass:
  - forcing: environmental forcing on communities 
  - can lead to misleading effect: @grace_integrative_2016

- Big scope assessment:
  - inconsistency between theoretical and empirical stability
    - theoretical: no cv_sp nor synchrony
  - No studies on stability-richness in empirical trophic communities
    - no effect of trophic structure

- Goal: Assess relation biomass/stability-diversity in empirical trophic communities
  - introduce effect of trophic structure and environment
  - merge gap between theoretical and empirical studies

- What we have done:
  - big empirical dataset
  - rebuilding empirical network
  - assess relationship between environment, community structure and stability

- Research questions:
  - What are the effects of the community structure on total biomass and stability ? 
    1. What are the effects of species richness on total biomass and stability ?
      - effect of species richness
      - effect of trophic group
    2. What are the effects of the community structure on total biomass and stability ?
      - What is the relative effect of the environment relative to the community
	structure ?
      - What is the effect of the community structure on the different
	parts of the stability + total biomass?
	- Effect of horizontal and vertical diversity

# Methods

## Fish data

- OFB
  - French long term protocol
  - standardized

- Electric fishing:
  - stuned fish
  - identification of the fishes
  - fish counted  
  - length of the fishes in mm by lot (4):
    - I: big fishes measured individually
    - S/L: fishes are grouped by species and by size 
      - 30 random fishes were measured in each lot
      - simulate the size of all the fishes of the lot:
	- normal distribution truncated at 95% (?)
	- mean and sd calculted from the sample of the lot 
    - G: little fishes are grouped by species
      - min and max size by lot 
      - simulate the size of all the fishes of the lot:
	- normal distribution truncated at 95% (?)
	- mean computed as ???  
	- se computed as ??? 
    - N:

- Protocols type:
  - complete
    - shallow river
  - partial:
    - deep and large river
    - partial over bank
    - partial by point
    - fusion of the two Protocols when "by point" all the point were done
      over bank

- Fishing operations and station
  - kept one protocol type by station
  - kept one sampling operation per year (of the season the most sampled in the
    time series)
  - remove operations which sampling effort (length of river sampled) superior to average
    plus or minus 30% of sd (by station)
  - kept station that had 10 or more samplings, i.e. followed 10 years or more


## Network building

- Diet data: 
  - 7? species over 57 had a piscivorous stage
  - 3? species had a strict piscivorous stage
  - ontogenic diet shift based on size

- 7 Resource nodes:
  - based on diet database
  - no information about their biomass

- Size class:
  - quantile: 9 size class per species

- Interaction:
  - Fish-resources and resources: based on diet data 
  - Fish-fish:
    1. diet data: is piscivorous?
    2. allometric relationship: predation range from .03 to .45 of body size

## Community

- Biomass:
  - infered by allometric law 
  - approximated by $B = 0.01 \times (l^3.03)$

```{r}
myload(nmds, habitat_pressure, dir = mypath("report"))
st_basin <- get_basin_station(sf_obj = FALSE)
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb)
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )

stab_div_troph <- com_data$tps_bm_troph %>%
  filter(troph_group != 1) %>%
  mutate(troph_group = as.factor(troph_group),
    log_rich = log10(richness_med),
    log_rich_tot = log10(richness_tot),
    log_bm = log10(biomass_med),
    log_stab = log10(biomass_stab)) %>%
  dplyr::select(station, troph_group, biomass_stab, richness_med, richness_tot, log_rich, log_rich_tot, log_stab, log_bm, biomass_med, richness_tot) %>%
  dplyr::left_join(st_basin, by = "station")
```

## Habitat and environment

- Collected during fishing operation:   
  - River size (width and depth)
  - Altitude and slope
  - distance to source
- Independant dataset from naiades: 
  - flow, temperature, DBO
    1. moving window average
    2. annual average 
    3. interpolation along rivers (OpenStars + SSN package)


```{r}
myload(
  hab_analysis,
  temporal_station_desc,
  temporal_press_polluants,
  geo_station,
  dir = mypath("data")
)
habitat_press <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)
```

```{r, fig.show = "hide"}
evt_var_mean <- c("flow_med", "temperature_med", "width_river_mean",
  "avg_depth_station_mean", "slope", "alt", "d_source", "strahler", "DBO_med")
evt_var_cv <- c("flow_cv", "temperature_cv", "width_river_cv",
  "avg_depth_station_cv", "DBO_cv")
pca_pressure <- habitat_press[, names(habitat_press) %in% c(evt_var_mean, evt_var_cv, "station")] %>%
  na.omit

pca_rotated <- compute_rotated_pca(
  .data = pca_pressure[, !names(pca_pressure) %in% "station"],
  naxis = 5 
)
```

## Statistical analysis

```{r get-data, cache = FALSE}
library(nlme)
library(piecewiseSEM)
```

### Relationship between stability and species richness

$$\begin{aligned}
\log_{10}S_i &= \beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}\\
S_i &= 10^{\beta_0 + \beta_R\log_{10}x_{Ri} + \epsilon_{ij}}\\
S_i &= 10^{\beta_0} \times 10^{\beta_R\log_{10}x_{Ri}} \times10^{\epsilon_{ij}}\\
S_i &= 10^{\beta_{0}} \times x_{Ri}10^{\beta_{R}} \times 10^{\epsilon_{ij}}
\end{aligned}$$

with $i$ being the station $i$.

```{r mod-div-total}
library(lme4)
ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
stab_div_mod <- lmer(
  data = sem_data,
  control = ctrl_lmer,
  formula = log_stab ~ log_rich_tot + (1 | basin)
)
stopifnot(!isSingular(stab_div_mod, tol = 1e-05))
stab_div_boot <- bootMer(stab_div_mod, mySumm2, nsim = 100)
stab_div_ci <- confint(stab_div_boot)
#stab_div_colin <- car::vif(stab_div_mod) not use if one response
stab_div_sum <- piecewiseSEM::rsquared(stab_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(stab_div_mod, terms = c("log_rich_tot"), type = "fe")
stab_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich_tot = x,
    basin = group
  )
stab_div_pred %<>%
  mutate(
    stab = 10^log_stab, # FALSE
    rich = 10^log_rich_tot,
    cl10 =  10^conf.low,
    ch10 =  10^conf.high
  )

#
bm_div_mod <- lmer(data = sem_data,
  formula = log_bm ~ log_rich_tot + (1 | basin)
)
bm_div_boot <- bootMer(bm_div_mod, mySumm2, nsim = 100)
bm_div_ci <- confint(bm_div_boot)
bm_div_sum <- piecewiseSEM::rsquared(bm_div_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred <- ggpredict(bm_div_mod, terms = c("log_rich_tot"), type = "fe")
#plot(pred, add.data = TRUE)
bm_div_pred <- pred %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    basin = group
  )

# get coeff
coef_div <- map(list(stab = stab_div_mod, bm = bm_div_mod), fixed.effects)
```

```{r mod-div-troph, fig.show = "hide"}
stab_troph_mod <- lmer(data = na.omit(stab_div_troph),
  formula = log_stab ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
  #control = ctrl
)
stab_troph_boot <- bootMer(stab_troph_mod, mySumm2, nsim = 100)
stab_troph_ci <- confint(stab_troph_boot)

stab_troph_colin <- car::vif(stab_troph_mod)
stab_troph_sum <- piecewiseSEM::rsquared(stab_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(stab_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_stab = predicted,
    log_rich_tot = x,
    troph_group = group
  )

# Productivity and troph group

bm_troph_mod <- lmer(data = na.omit(stab_div_troph),
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_bm ~ log_rich_tot + troph_group + log_rich_tot:troph_group + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
bm_troph_boot <- bootMer(bm_troph_mod, mySumm2, nsim = 100)
bm_troph_ci <- confint(bm_troph_boot)

bm_troph_sum <- piecewiseSEM::rsquared(bm_troph_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_troph_mod <- ggpredict(bm_troph_mod, terms = c("log_rich_tot", "troph_group"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
bm_troph_pred <- pred_troph_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

# get coeff
coef_troph <- map(list(stab = stab_troph_mod, bm = bm_troph_mod), fixed.effects)
```

### SEM

We computed Structural Equation Modeling (SEM) to unravel mechanisms underlying link
between environment, community structure and both biomass stability and total
biomass. Why SEM? 

SEM enables to reason in terms of causal relationship between components. We
aimed to understand the mechanisms behind the negative relationship biomass
stability and species richness and the positive relationship between total
biomass and species richness.

We built a metamodel to set up the nodes and the links between the different
compartment of the SEM. Basically, we tested the links between environmental
conditions, community structure and stability. Theory in ecology predicts that
community structure influences stability. In turn, environment influences
community structure but also directly stability.

#### Variables

To characterize environment, we retained five axis of PCA on habitat and
climatic variables which represent different types of forcing (constant and
variability). The two first axis (RC1 and RC2) were linked to the physical
structure and position of the river and the altitutinal gradient (+temperature).
The third axis (RC3) was linked to enrichment (Organic Biological Demand) and CV
of annual flow. The fourth and fifth (RC4 and RC5) axis were associated to
environmental variability, respectively to CV of width and depth of the river
and CV of enrichment.

The community structure was characterized by total species richness,
median average weighted trophic level and median connectance.
Total species richness was the number of unique fish species that were observed
at a given station over the whole sampling. Both median
connectance and average trophic level were just computed as the median over the
temporal period. For the details of the computation of the trophic networks,
see Network inference part.

The biomass stability was decomposed in synchrony and weighted average CV
components according to @thibaut_understanding_2013:

$$
CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
$$

with $CV_{com}$ being the Coefficient of Variation of the community,
$\overline{CV_{sp}}$ the average coefficient of variation of population
pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
community variance ($\sigma^2_{x_T}$) and the sum of population variance
($\sigma_{x_i}$) [@loreau_species_2008]:

$$
\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
$$


#### Causal relationships

---
# Environment to community attributes and stability  
---
We linked environmental variables both to community structure and stability
components. Rooted in assembly theory, environment filters species that can
establish in a community and thus affect community structure. (+ add specific
hypothesis about physical and climate). (1) We hypothesized that enrichment
(characterized by DBO) and mean annual temperature will increase species turnover
[@friedpetersen_drivers_2020]. (2) We hypothesized environmental forcing can also
decrease biomass stability directly without going by community structure. First,
instability of habitat and environmental factors may in turn drive biomass
instability [@hansen_climate_2013]. Secondly, average environmental conditions
such as enrichment can increase directly CV by increasing species biomass
fluctuations [@tabi_warming_2019]. Increasing temperature was also hypothesized
to decrease stability through starvation resulting from high metabolic activity
[@tabi_warming_2019].

---
# Species richness to community attributes 
---
To reveal the mechanisms behind the relationship between species richness and
biomass stability, causal links were set from species richness to other
community attributes. (5) We hypothesized also that species richness
decreased connectance following results from @thebault_stability_2010;
@winemiller_must_1989. But theoretically, some ecological networks can show the
inverse relationship [@winemiller_must_1989]. (6) We hypothesized also that species richness
will modulate average weighted trophic level because of food web assembly
processes. If *species richness increased and that new species are placed at
random in the network, we expected a positive relationship between average
trophic level and species richness because individuals of the higher trophic
level have a higher body mass [to think again]*. Finally, we set up causal
relationships from community attributes to stability components. 

---
#  Community attributes to stability
---
We hypothesized that (7) species richness decreased synchrony between species
[REF] and increased $\overline{CV_{sp}}$ [@tilman_biodiversity_2006] *to
complete*. (8a) We expected that average trophic level had a positive or
negative relationship with synchrony, bottom-up effects should result in
positive whereas top-down in negative relationship. We expected a (8b) negative
relationship between average trophic level and $\overline{CV_{sp}}$ if predators
stabilised population
fluctuations or if the increasing part of biomass in the predators decreased
$\overline{CV_{sp}}$ because of their higher body mass (if mean increase faster than
variance). (9a) Connectance was expected to decrease or increase $\overline{CV_{sp}}$
and (9b) synchrony because of top down effects or bottom up effects.


```{r}
# Compute SEMs
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

library(ggraph)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)
p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)

library(DiagrammeR)

p_format <- "png"
p_width <- 700
p_height <- 700

stab_sem_path <- mypath("manuscript", "bef_stability",
  paste0("stab_sem.", p_format))
bm_sem_path <- mypath("manuscript", "bef_stability",
  paste0("bm_sem.", p_format))

graph_stab_sem <- build_diag_from_sem(stab_sem_rich, p_val_thd = 0.05)
render_graph(graph_stab_sem)
export_graph(graph = graph_stab_sem, file_type = p_format,
  file_name = stab_sem_path,
  height = p_height - p_height*20/100,
  width = p_width
)
#source(mypath("R", "plot_methods.R")) 
graph_bm_sem <- build_diag_from_sem(bm_sem_rich, p_val_thd = 0.05)
render_graph(graph_bm_sem)
export_graph(graph = graph_bm_sem, file_type = p_format,
  file_name = bm_sem_path,
  #file_name = "stab_sem.svg",
  height = p_height,
  width = p_width 
)

library(magick)
library(rsvg)
img_stab_sem <- stab_sem_path %>%
  image_read()
p_stab_sem_rich <- ggdraw() +
  draw_image(img_stab_sem)
img_bm_sem <- bm_sem_path %>%
  image_read()
p_bm_sem_rich <- ggdraw() +
  draw_image(img_bm_sem)

```


```{r get-sem-coeff}
coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

coef_bm_sem <- coef(bm_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

```{r stab-network}
sem_data %>%
  select(sync, cv_sp, ct, t_lvl) %>%
  gather(network, metrics, ct, t_lvl) %>%
  gather(stab_comp, value, sync, cv_sp) %>%
  ggplot(aes(y = value, x = metrics)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(stab_comp ~ network, scales = "free_x")

stab_ct_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab ~ ct + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_ct_boot <- bootMer(stab_ct_mod, mySumm2, nsim = 100)
stab_ct_ci <- confint(stab_ct_boot)

stab_ct_sum <- piecewiseSEM::rsquared(stab_ct_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_stab_ct_mod <- ggpredict(stab_ct_mod, terms = c("ct"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_ct_pred <- pred_stab_ct_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

# get coeff
coef_stab_ct <- map(list(stab = stab_ct_mod), fixed.effects)


stab_tlvl_mod <- lmer(data = sem_data,
  #fixed = log_bm ~ log_rich_tot * troph_group,
  formula = log_stab ~ t_lvl + (1 | basin)
  #random = ~ 1 + log_rich_tot * troph_group | basin,
  #control = ctrl 
)
stab_tlvl_boot <- bootMer(stab_tlvl_mod, mySumm2, nsim = 100)
stab_tlvl_ci <- confint(stab_tlvl_boot)

stab_tlvl_sum <- piecewiseSEM::rsquared(stab_tlvl_mod, method = "nagelkerke") %>%
  mutate_at(vars(Conditional, Marginal), ~round(., 2))

pred_stab_tlvl_mod <- ggpredict(stab_tlvl_mod, terms = c("t_lvl"), type = "fe")
#plot(pred_troph_mod, add.data = TRUE)
stab_tlvl_pred <- pred_stab_tlvl_mod %>%
  as_tibble() %>%
  rename(
    log_bm = predicted,
    log_rich_tot = x,
    troph_group = group
  )

# get coeff
coef_stab_tlvl <- map(list(stab = stab_tlvl_mod), fixed.effects)
```


# Results

## Drivers of total biomass and stability

```{r sem-plot, fig.dim = c(10,10), fig.cap = "SEM"}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

plot_grid(p_stab_sem_rich, p_bm_sem_rich, labels = LETTERS[1:2], rel_widths = c(.55, .45))
```

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)
get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
  out <- ifelse(length(out) == 0, 0, out)
  round(out, 2)
}

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_rich_tot")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm", pred = "log_RC1")
```

```{r get-bm-tot-effect-env}
bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05)
# env on com 
env_on_t_lvl <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = bm_all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = bm_all_params,
  p_val_thl = 0.05)
```

```{r get-bm-tot-effect-rich}
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05)
```

---
# Total biomass
---

Species richness and the average trophic level were the main direct drivers of
total biomass ($r_\delta = `r rich_on_bm`$ and $r_\delta = `r tlvl_on_bm`$ resp.) whereas
connectance had no significant effect (Fig. \@ref(fig:sem-plot) C). The stream
size had a direct positive effect on total biomass ($r_\delta = `r RC1_on_bm`$) whereas
avg temperature, avg DBO, CV of river size and CV of DBO had no direct effects
on total biomass.

Species richness had also a indirect positive effect on total biomass through
average trophic level, species richness had a total positive effect of $`r rich_on_bm`$
on total biomass. The stream size had a total effect on total biomass as strong
as species richness ($r_\delta =`r env_on_bm["log_RC1"]`$), indirectly through average trophic level
and species richness. The avg temperature of the river had an indirect positive
effect on total biomass ($r_\delta = `r env_on_bm["log_RC2"]`$), through
average trophic level and species richness as well. Avg DBO, CV DBO and CV of
river size had no or weak indirect effect on total biomass
(resp. $r_\delta =`r env_on_bm["log_RC3"]`$, $r_\delta =`r env_on_bm["log_RC5"]`$, $r_\delta =`r env_on_bm["log_RC4"]`$).

```{r get-sem-single-effect}
stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)
get_clean_sem_coef <- function(sem = NULL, resp = NULL, pred = NULL) {
  out <- sem[sem$Response == resp & sem$Predictor == pred, ]$Std.Estimate
  out <- ifelse(length(out) == 0, 0, out)
  round(out, 2)
}

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
```

```{r get-sem-tot-effect-env}
all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab

env_on_stab <- get_env_on_stab(fit = all_params, p_val_thl = 0.05)
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
env_on_cv_sp <- get_env_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
# env on com 
env_on_t_lvl <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "t_lvl")
env_on_ct <- get_env_on_com(fit = all_params,
  p_val_thl = 0.05,
  com = "ct")
env_on_richness <- get_env_on_rich(fit = all_params,
  p_val_thl = 0.05)
```

```{r get-sem-tot-effect-rich}
rich_on_stab <- get_rich_on_stab(fit = all_params,
  p_val_thl = 0.05)
rich_on_sync <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp")
```


---
# Biomass stability
---

$\overline{CV_{sp}}$ ($r_\delta = `r cv_sp_on_stab`$) decreased biomass stability more than
synchrony ($r_\delta = `r sync_on_stab`$, Figure \@ref(fig:sem-plot)). Species richness had a strong
positive effect on $\overline{CV_{sp}}$ and a strong negative effect on synchrony
whereas average trophic level and connectance had no significant effects on either
$\overline{CV_{sp}}$ nor synchrony. The avg river size had a small positive direct
effect on synchrony ($r_\delta = `r RC1_on_sync`$). The other environmental variables had
no significant direct effects on either $\overline{CV_{sp}}$ nor synchrony.

Indirectly through synchrony and $\overline{CV_{sp}}$, species richness had a total negative
effect on biomass stability ($r_\delta = `r rich_on_stab`$). Avg river size and avg
temperature had also a total effect which was negative on biomass stability
(resp. $r_\delta = `r env_on_stab["log_RC1"]`$ and $r_\delta = `r env_on_stab["log_RC2"]`$),
going through richness (resp. $r_\delta = `r env_on_richness["log_RC1"]`$ and
$r_\delta = `r env_on_richness["log_RC2"]`$).

- Main outcome:
  - Biomass but stability increased with richness
  - Higher trophic group was more stable that lower one
    - Opposite relationship stability/richness
  - Stability was mainly driven by species richness


## Species richness increases total biomass but decreases biomass stability

```{r}
richness_lab <- "Total richness (Log 10)"
stab_lab <- "Biomass stability (Log 10)"
bm_lab <- "Total biomass (Log 10)"

stab_div_caption <- paste0("Relationship between biomass stability (log 10) (top panel) or total biomass (log 10) (bottom panel) versus total species richness.") 
```

```{r p-s-div, fig.cap = stab_div_caption}
lim_log_stab <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_stab")
lim_log_rich_tot <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_rich_tot")
# Plot left  

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = stab_lab) +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

# Right plot
p_stab_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot, y = log_stab, color = troph_group)) +
  geom_point() +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  geom_line(data = stab_troph_pred) +
  geom_ribbon(data = stab_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = .8, label = make_label_rsq(rsq = stab_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = stab_lab)

p_stab <- plot_grid(p_stab_div, p_stab_div_troph,
  ncol = 2, rel_widths = c(.4, .6),
  labels = c("A", "B") 
)
```


```{r p-p-div}
lim_log_bm <- get_min_max(list(sem_data, stab_div_troph), var_chr = "log_bm")

p_bm_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_bm))+
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = bm_lab) +
  geom_line(data = bm_div_pred) +
  geom_ribbon(data = bm_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = .8, y = 1.5, label = make_label_rsq(rsq = bm_div_sum),
    parse = TRUE)

p_bm_div_troph <- stab_div_troph %>%
  ggplot(aes(x = log_rich_tot, y = log_bm, color = troph_group)) +
  geom_point() +
  ylim(lim_log_bm) +
  xlim(lim_log_rich_tot) +
  ggplot2::scale_color_manual(
    labels = troph_group_labeller(),
    values = c("blue", "green", "red"),
    name = "Trophic group"
  ) +
  geom_line(data = bm_troph_pred) +
  geom_ribbon(data = bm_troph_pred,
    aes(ymin = conf.low, ymax = conf.high, color = NULL, group = troph_group),
    alpha = .2) +
  annotate("text", x = 0.8, y = 1.5, label = make_label_rsq(rsq = bm_troph_sum),
    parse = TRUE) +
  #scale_x_log10() + scale_y_log10() +
  labs(x = richness_lab, y = bm_lab)

p_bm <- plot_grid(p_bm_div, p_bm_div_troph, ncol = 2, rel_widths = c(.4, .6),
  labels = c("C", "D"))
```

```{r psbm, fig.dim = c(10,5)}
plot_grid(p_stab, p_bm, ncol = 1)

print_coef <- function (vec){
  round(abs(vec)*100)
}
print_ci <- function(.df){
  .df <- round(.df, 3)*100
  
  paste0("[", .df[["2.5 %"]],";",.df[["97.5 %"]] ,"]")
}
```

```{r print-coef-stab}
# Coefficients
s_co_i <- print_coef(coef_div$stab["(Intercept)"])
s_co_r <- print_coef(coef_div$stab["log_rich_tot"])
s_co_t <- print_coef(coef_troph$stab["troph_group3"])
s_co_r_t2 <- print_coef(coef_troph$stab["log_rich_tot"])
s_co_r_t3 <- print_coef(coef_troph$stab["log_rich_tot"]+coef_troph$stab["log_rich_tot:troph_group3"])

s_ci_r <- print_ci(stab_div_ci["beta.log_rich_tot",])
s_ci_t <- print_ci(stab_troph_ci["beta.troph_group3",])
s_ci_r_t2 <- print_ci(stab_troph_ci["beta.log_rich_tot",])
s_ci_r_t3 <- print_ci(coef_troph$stab["log_rich_tot"] + stab_troph_ci["beta.log_rich_tot:troph_group3",])
```

```{r print-coef-bm}
# Coefficients
b_co_i <- print_coef(coef_div$bm["(Intercept)"])
b_co_r <- print_coef(coef_div$bm["log_rich_tot"])
b_co_t <- print_coef(coef_troph$bm["troph_group3"])
b_co_r_t2 <- print_coef(coef_troph$bm["log_rich_tot"])
b_co_r_t3 <- print_coef(coef_troph$bm["log_rich_tot"]+coef_troph$bm["log_rich_tot:troph_group3"])

b_ci_r <- print_ci(bm_div_ci["beta.log_rich_tot",])
b_ci_t <- print_ci(bm_troph_ci["beta.troph_group3",])
b_ci_r_t2 <- print_ci(bm_troph_ci["beta.log_rich_tot",])
b_ci_r_t3 <- print_ci(coef_troph$bm["log_rich_tot"] + bm_troph_ci["beta.log_rich_tot:troph_group3",])
```

---
# Total biomass versus species richness
---
species richness increased total biomass (`r b_co_r`% `r b_ci_r` by 1% species richness increase). Total
biomass was `r b_co_t`% `r b_ci_t` higher in the high than in the low trophic
group. However, the increase of total biomass with the increase of species
richness was lower in the high than the low trophic group (`r b_co_r_t3`% `r
b_ci_r_t3` and `r b_co_r_t2`% `r b_ci_r_t2` respectively,  by 1% species
richness increase).

---
# Stability versus species richness
---

However, biomass stability decreased with species richness (`r s_co_r`% `r s_ci_r` by 1%
species richness increase). Biomass stability was overall `r s_co_t`% `r s_ci_t` higher for the high
than the low trophic group. But biomass stability decreased by `r s_co_r_t3`% by
1% increase in species richness in the high trophic group and increased by `r s_co_r_t2`% `r s_ci_r_t2`
in the low trophic group.

# Discussion

---
# Chapeau
---

For the first time, we assessed the determinants of total biomass and temporal
biomass stability in empirical trophic communities at such high temporal and
spatial scales. We showed that species richness increased total biomass but 
decreased biomass stability. In particular, species richness decreased
synchrony and increased species CV (\LaTeX). Surprisingly, the avg trophic
level and connectance had no effects on either synchrony nor species CV.
Finally, we showed that high trophic group was more stable than low trophic
group but that high trophic group was responsible for the negative
stability-diversity relationship.

---
# Negative relationship between stability and richness 
---

Surprisingly, we found a negative relationship biomass stability and species
richness whereas there was a positive one between total biomass and species
richness. Those relationships followed a power law, meaning that they represent
respectively accelerating and decelerating functions. Overall, it contrasts
with studies in grasslands [@tilman_biodiversity_2006, @zhang_scale_nodate],
mesocosms [@pennekamp_biodiversity_2018] or other animals
[@olivier_independent_nodate] where positive relationships are typically found
between biomass stability (computed as CV) and species richness. In streams as
well, @franssen_annual_2011 found that species richness increased biomass
stability. However other studies found a opposite relationship
[@yang_effects_2011] or a marginal one [@declerc_species_2006].


---
# Total biomass
---

We found that species richness increased total biomass as found in salt
marshes, forests [@wu_relationship_2014,@shuaifeng_positive_2018]. But opposite
relation has been found in richness in grasslands [@grace_integrative_2016],
notably because of light competition. Precedent researches in plant communities
showed that the total biomass was primary driven by environmental drivers. In
contrast, we found that the species richness was one of the main driver of the
total biomass, together with the stream size and increasing avg temperature
(with decreasing altitude). The big effect of species richness is 
partly explained by its effect on food web assembly and so, avg trophic level
(`r round(.2/0.54 * 100)` % of richness effect on total biomass). The direct
positive effect of species richness on total biomass might be due to resource use
complementarity [@cardinale_species_2002] [add more direct REF]. It was however
unexpected that connectance had no effect on total biomass, because we could
imagine that connectance could also improve resource use, but this might be
true only under the assumption that all species have the same assimilation
efficiency.

We found that contrary to stream size, the effect of altitude of the river and
its avg temperature on total biomass was only indirect through community
structure (avg trophic level and connectance). 

---
# Effect of environment on community structure
---

The total effect of river size on biomass stability was as negative as species
richness, indicating that big rivers had a high negative effect on stability (TO MOVE).
We found a mix of both expected and unexpected results on the effects on
environment on community structure. First, we expected that bigger and low
altitude streams had higher species richness because they might receive more
confluents streams and so more species through immigration.
Stream size increased both connectance and avg trophic level with the same
magnitude. An increase in mean trophic position of piscivorous species in
bigger rivers could explain this relation [@post_ecosystem_2000]. In our
network reconstruction, the fish-fish interactions are more resolved than
fish-resource interactions, which might explain positive effect of stream size
on connectance. @petchey_predicting_2010 predicted that temperature should
increase connectance but we did not find any relationship but temperature (and
low altitude) increased avg trophic level (**Bullshit**). 
CV of enrichment decreased both connectance and avg trophic level, while avg
enrichment (and CV of flow) increased both. The latter might by explained by
the fact that enrichment can benefit to top trophic level
[@hulot_functional_2000]. One explanation for the former is that enrichment
variation might destabilize top predators (REF or Bullshit again).

---
# Effect of synchrony and cv_sp  
---


Species richness decreased synchrony and increased $\overline{CV_{sp}}$. Species
richness can reduce synchrony through decrease of population size, thus raising
the role of demographic stochasticity [@loreau_species_2008] but also in the
case where species have different responses to environmental variation
[@loreau_species_2008]. While the effect of species richness on synchrony is
well understood, its effect on $\overline{CV_{sp}}$ is more complex. Indeed, studies reported positive [@tilman_biodiversity_2006, ], neutral  [@jiang_different_2009, @olivier_independent_nodate] or negative relationships [@franssen_annual_2011, @olivier_independent_nodate]. Positive relationship between

In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013].
However, it was unexpected that the average population $\overline{CV_{sp}}$ had
a stronger negative effect on biomass stability than synchrony
[@bluthgen_land_2016; @olivier_independent_nodate]. We can advance two
hypothesis that can raise this effect. First, the opportunity for diet
differentiation can be low in streams compare to other organisms. Bird species
are for example quite specialized in seed, flying or soil arthropods or mammals
which gives opportunities for independent dynamics. Plants also can achieve
independent dynamics either spatial segregation or niche differentiation. Because
fish species even piscivorous one are quite opportunistic in their foraging.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

---
# Effect of trophic level and connectance are richness effects:
---

Our path analysis revealed that, although species richness has a strong effect on
connectance and the average trophic level, network structure  itself had little
to no effect either on synchrony nor average population stability. This result
contradicts precedent theoretical studies on the relationship
between stability and network structure [@angelis_stability_1975,
@may_will_1972], although they considered different stability metrics (i.e.
local stability of equilibrium point). The reason might be that in our inferred
network, network structure is strongly constraints by assembly processes.
Indeed, connectance generally decreased with increasing species richness
[@winemiller_must_1989, @thebault_stability_2010], because a small fraction of
links are realized because of food diet constraints. In theoretical studies,
connectance can be tuned from 0 (no links) to 1 (all possible links are
present) [@angelis_stability_1975]. The link between the average trophic level
and species richness has been less studied. However, we can suppose that
because species richness increase total biomass, species richness also increase
both the biomass of prey available for piscivorous fishes and the biomass of
piscivorous species which in turn, increase the avg trophic level of the
community. In sum, the biomass stability of freshwater ecosystems can be
derived by species richness because, through trophic structure constraints,
species richness determine largely network structure.


---
# Trophic group
---

The total biomass of high and low trophic group trophic groups responded both
positively to species richness but not biomass stability. There is a
paradox where the high trophic group is overall more stable than the low but
species richness had a destabilizing effect on the former whereas a stabilizing
on the latter. @shanafelt_david_w._stability_nodate showed in a theoretical
study in trophic chains, the top trophic level is the more stable TOEXPLORE.
The comparison between our study and theoretical studies stays limited because
fishes in our system have a large diet and consume food item of several trophic
level while theoretical studies consider system in which one species of one
trophic level feeds only on the trophic level directly inferior
[@shanafelt_david_w._stability_nodate] ADD REF.


# Appendix

## PCA of environmental variables

```{r, fig.show = "hide"}
axis_pair <- list(c(1,2), c(1,3), c(2,3), c(1, 4), c(2, 4), c(3,4), c(4,5))
p_l_rot <- map(axis_pair, 
  function (axis)
    pca_rotated_plot <- plot_rotated_pca(
      pca_rotated = pca_rotated,
      axis = axis 
    )
)
```

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))


tot_var_expl_pca <- round(sum(pca_rotated$rotated$Vaccounted["Proportion Var", ]) * 100) 

pca_caption <- paste0(
  "Rotated axis of PCA on environmental variables. The five components
  explained,", tot_var_expl_pca, "% of the variance (",
  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
  "(A) Axis 1 was positively related to the river size, axis 2 was related to
  average temperature and negatively related to the river slope and altitude.
  (B) Axis 3 was negatively related to the CV of flow and average enrichment.
  Axis 4 was related to the CV of river size. Finally, axis 5 was related to the
  CV of enrichment.")
```


```{r pca-rotated, fig.cap = pca_caption}
to_plot <- c(1, 6, 7)
plot_grid(plotlist = map(p_l_rot[to_plot], ~.x$rotated),
  ncol = length(to_plot), labels = LETTERS[1:3])
```

## Model summary and diagnostics 

### Biomass and stability models

```{r tab-coeff-bm, fig.cap = "Coefficient"}
# Replacement rules for term
rp_est <- c(
  "(Intercept)" =     "intercept",
  "sd\\_\\(intercept\\)\\.basin" = "sd intercept basin",
  "log_rich" =     "Median richness (log base 10)",
  "troph_group3" =     "high trophic group",
  "log_rich:troph_group3" =     "Median richness (log10) : high trophic group",
  "sig01.basin" =     "sd intercept basin",
  "sd_Observation.Residual" =     "residuals",
  "sigma" = "residuals"
)
# Replacement rules for group
rp_group <- c(
  "fixed" = "Fixed",
  "basin" = "Random"
)

```

```{r}
coeff_troph <- map2_dfr(list(bm_troph_ci, stab_troph_ci), list(bm_troph_mod, stab_troph_mod),
  clean_summary_mod, term_rp = rp_est, group_rp = rp_group)

kable(coeff_troph) %>%
  pack_rows("Biomass", 1, 6) %>%
  pack_rows("Stab", 7, 12)
```



### SEM 

```{r tab-coeff-stab}

```


## Model residuals

### Biomass and stability models 

```{r}
mod_list <- list(bm_div_mod, bm_troph_mod, stab_div_mod, stab_troph_mod)
plot_res <- map(mod_list, ~ plot(.x))
plot_grid(plotlist = plot_res)
```

### SEM linear relationships


```{r hist-sem-data}
sem_data %>%
  select(prod, log_rich_tot, log_sync, log_stab, log_cv_sp, RC1, RC2, RC3, RC4,
    RC5, t_lvl, ct, log_bm) %>%
  gather(variable, value) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")

```



```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}
#compute_stab_sem_rich(.data = sem_data, get_sem =TRUE)

mod_stab_list <-
  list(
    nlme::lme(log_rich_tot ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
    #nlme::lme(piel ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(ct ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    #nlme::lme(beta_bin ~ log_RC1 + log_RC2 + log_RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_sync ~ log_rich_tot + ct + t_lvl + log_RC1 + log_RC2 + log_RC3 + RC4 + RC5,
      random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_cv_sp ~ log_rich_tot  + ct + t_lvl
      + RC1 + log_RC2 + log_RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data),
    lm(log_stab ~ log_cv_sp + log_sync, data = sem_data)
  )
names(mod_stab_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "synchrony", "cv_sp", "stability") 
colin_stab_sem <- map(mod_stab_list, car::vif)

tmp <- map(colin_stab_sem, enframe)
  
# colinearity table
colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
  unnest(vif) %>%
  spread(name, value)

kable(colin_stab_sem)
```

```{r}
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem)
```

```{r, eval = FALSE}
mod_tlvl <- nlme::lme(t_lvl ~ scale(RC1) + scale(RC2) + scale(RC3) + scale(RC4) + scale(RC5) + log_rich_tot, random = ~ 1 | basin, data = sem_data)
plot(mod_tlvl)
sem_data %>%
  ggplot(aes(x = log10(richness_tot), y = t_lvl)) +
  geom_point()+
  geom_smooth(method = "lm")
plot(x = log10(sem_data$RC1 + abs(min(sem_data$RC1))), y = sem_data$t_lvl)
sem_data %>%
  ggplot(aes(x = log10(RC1), y = t_lvl)) +
  geom_point()+
  geom_smooth(method = "lm")
plot(nlme::lme(t_lvl ~ I(log10(RC1 + abs(min(RC1)))) + log_rich_tot, random = ~ 1 | basin, data = sem_data))
nlme::lme(t_lvl ~ log_rich_tot, random = ~ 1 | basin, data = sem_data)
semd_test <- sem_data %>%
  mutate(RC1b = RC1 + abs(min(RC1)))
ricker.mixed.fit <- nls(
  t_lvl ~ (Vm*(RC1 + b) / (K + (RC1 + b)) + d),
 #fixed = Vm + K + b + d ~ 1,
 #random = Vm + K + b + d ~ 1|basin,
 start= c(Vm=1, K = 0.1, b = .5, d = 2.5),
 data = semd_test,
 control = lmeControl(maxIter = 1e8, msMaxIter = 1e8) 
)
summary(ricker.mixed.fit)
x <- seq(min(sem_data$RC1), max(sem_data$RC1), length.out = 100)
sem_data$test_pred <- predict(ricker.mixed.fit)

semd_test %>%
  ggplot(aes(x = RC1b, y = t_lvl)) +
  geom_point() +
  geom_line(aes(y = test_pred))
  geom_smooth(method = "lm")
cor(semd_test$piel, semd_test$t_lvl, method = c("spearman"))
```

```{r, eval = FALSE}
library(glmmTMB)
# Gaussian
mod_log_rich <- glmmTMB(
  log_rich_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = gaussian, data = sem_data)
summary(mod_log_rich)
plot(y = resid(mod_log_rich), x = fitted(mod_log_rich))

# Poisson 
mod_log_rich_poi <- glmmTMB(
  richness_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = poisson, data = sem_data)
summary(mod_log_rich_poi)
plot(y = resid(mod_log_rich_poi), x = fitted(mod_log_rich_poi))

# Truncate 
mod_log_rich_nbinom <- glmmTMB(
  richness_tot ~ log_RC1 + log_RC2 + log_RC3
  + RC4 + RC5 + (1 | basin), family = nbinom1, data = sem_data)
summary(mod_log_rich_nbinom)
plot(y = resid(mod_log_rich_nbinom), x = fitted(mod_log_rich_nbinom))
```

#### Total biomass

```{r}

mod_bm_list <-
  list(
    nlme::lme(log_rich_tot ~ RC1 + RC2 + RC3 + RC4 + RC5,  random = ~ 1 | basin, data = sem_data),
    #nlme::lme(piel ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(ct ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(t_lvl ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    #nlme::lme(beta_bin ~ RC1 + RC2 + RC3 + RC4 + RC5 + log_rich_tot, random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_bm ~ log_rich_tot + ct + t_lvl + RC1 + RC2 + RC3 + RC4 + RC5,
      random = ~ 1 | basin, data = sem_data)
  )
names(mod_bm_list) <- c("richness", "connectance", "weighted_mean_trophic_lvl", "total_biomass") 
colin_bm_sem <- map(mod_bm_list, car::vif)

tmp <- map(colin_bm_sem, enframe)
  
# colinearity table
colin_bm_sem <- tibble(vif = tmp, mod = names(mod_bm_list)) %>%
  unnest(vif) %>%
  spread(name, value)

kable(colin_bm_sem)
```


## Relationship at the absolute scale, i.e. not the logarythme scale 

```{r}
ggplot(sem_data, aes(x = richness_med, y = biomass_stab)) +
  geom_point()
test <- tibble(
  richness_med = seq(1,20, length.out = 100),
  biomass_stab =
    10^(fixef(stab_div_mod)[1])*richness_med^fixef(stab_div_mod)[2]
)  
```

```{r save-plot}

save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div.pdf",
  p_stab_div,
  base_height = 3,
  bg = "transparent",
  ncol = 1)

save_plot("~/Documents/thesis/talks/fishcom_fig/stab_div_troph.pdf",
  p_stab_div_troph + theme(legend.position = "bottom"),
  base_height = 3,
  bg = "transparent",
  ncol = 1)

```


# References
