---
title: Horizontal and vertical diversity drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, Elisa Thebault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

```{r, echo = FALSE, results = FALSE, message = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = FALSE 
)

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```

```{r, results = FALSE}
knitr::opts_chunk$set(
  results = TRUE 
)
```


# Abstract

# Introduction 

#### Biodiversity and ecosystem properties 


Current biodiversity losses and global changes affect ecosystems in complex and
unpredictable ways [@bellard_impacts_2012]. Since the seminal of paper of
@may_will_1972, the relationships between biodiversity and ecosystem properties
have received a lot of attention [@hector_plant_1999; @loreau_biodiversity_2001;
@hooper_effects_2005; @dunne_network_2006; @duffy_why_2009;
@isbell_forest_quantifying_2018]. Biodiversity largely determines both the
amount and the distribution of matter and energy fluxes within ecosystems, and
has hence a tremendous effect on ecosystem properties [@duffy_why_2009], such as
its total biomass [@hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016; @pennekamp_biodiversity_2018]], biomass production
[@tilman_productivity_1996; @cardinale_species_2002; @grace_integrative_2016]
and the biomass temporal stability [@thebault_trophic_2005;
@thebault_relationship_2006; @tilman_biodiversity_2006;
@olivier_independent_nodate].

#### Horizontal and vertical diversity are two ways to look at biodiversity  

Biodiversity can be quantified in numerous ways: either as the number of species
(i.e.  species richness) and in number of functional groups, which are usually
defined based on the trophic ecology of species, namely the way they acquire
food [@allan_stream_2007]. Those metrics can be organized into (i) "horizontal
diversity", which captures the overall diversity of components (i.e. species)
present in a community, and (ii) "vertical diversity" which captures diversity
of components across functional groups, such as the amount trophic categories,
often termed guilds or levels [@allan_stream_2007; @loreau_population_2010;
@zhao_horizontal_2019; @wang_biodiversity_2017]. Vertical diversity has been
primarily quantified as food chain length [@loreau_population_2010;
@zhao_horizontal_2019; @wang_biodiversity_2017] but it can also be characterized
by the food web structure [@wang_biodiversity_2017] such as connectance and
average trophic level. Horizontal and vertical diversity are, however, not
independent from each other. Connectance is known to covary negatively with
species richness [@winemiller_must_1989; @dunne_network_2006;
@thebault_stability_2010].

**Horizontal and vertical diversity are, however, not independent from each other
[@duffy_functional_2007; @zhao_horizontal_2019]. The add or removal of one
species (i.e. ) can have different effects depending on its vertical position in the
trophic chain [@duffy_functional_2007]. Hence, it is crucial to study their
interplay to improve our understanding of ecosystem dynamics.**

#### horizontal and vertical diversity increase total biomass by common and different mechanisms 

Horizontal diversity has been shown to promote higher biomass production in a
variety of ecosystems. Horizontal diversity, as species richness, has been
reported to increase primary productivity [@cardinale_species_2002,
@tilman_productivity_1996; @grace_integrative_2016]. Two mechanisms have been
proposed to rise this effect [@loreau_partitioning_2001]. The complementarity in
resource use, rising through niche differentiation and interspecific
facilitation, increase the total amount of resource used
[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
Positive select effect arise when species richness leads to an higher dominance
of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
As for total biomass, empirical studies have generally demonstrated positive
relationships with species richness in plant communities [@hector_plant_1999;
@tilman_biodiversity_2014; but see @grace_integrative_2016] and mesocosms
[@pennekamp_biodiversity_2018]. When adding the vertical diversity, e.g.
consumers species, @gamfelt_species_2005 and @thebault_relationship_2006 have found that total
biomass increased with increasing species diversity at two trophic levels.
But this positive relation seems to strongly depend on the niche differentiation of
the consumer species, i.e. their resource complementarity,
@thebault_relationship_2006. Hence, the total biomass-species richness
relationship seems to be supported by the same mechanisms within consumers and
within plants. (also duffy_ecosystem_2005)

The effect of the vertical diversity itself does not seem to affect total
biomass. But seek food chain length, connectance

You should connect average trophic level to biomass repartition (good when lots
of omnivory and no trophic chain)

- Effect of food web structure on total biomass are relatively absent

However, increasing consumer species richness
results in higher consumer biomass to the detriment of primary producer biomass
[@gamfelt_species_2005; @thebault_relationship_2006].

- Horizontal div at different trophic levels (v & h )
- Vertical div: 

The food web structure, vertical diversity, also modulates total biomass and
productivity [@thebault_food-web_2003; @thebault_trophic_2005;
@ogorman_multiple_2012; @dossena_warming_2012; @schneider_animal_2016;
@gamfelt_species_2005]. Both in theoretical and experimental study,

The addition of trophic levels, consumer usually
breaks the positive relationship between plant biomass and plant diversity as a
significant amount of biomass is transfered to consumers
[@thebault_food-web_2003].

It has been shown both in experiments
[@ogorman_multiple_2012; @dossena_warming_2012]
and theoretical models [@thebault_food-web_2003; @schneider_animal_2016;
@wang_biodiversity_2017].

Theoretical models @thebault_relationship_2006
have shown with a theoretical model that total biomass should increase with the
increase species diversity at two trophic level *+[]*. However, the joint effects of horizontal and vertical
diversity on total biomass has been rarely tested, especially in natural
communities. It is not clear whether horizontal and vertical diversity just
change the distribution of biomass across trophic level or it increases the
total amount of  biomass (*It misses a lot of references here*).

#### Horizontal and vertical diversity versus temporal stability

Horizontal and vertical diversity also affects the stability of ecosystem
properties. Experimental studies showed consistently that species richness
increase temporal stability of biomass in grasslands
[@tilman_biodiversity_2006], mesocosms [@pennekamp_biodiversity_2018]. While in
natural communities, same relation has been found for temporal biomass stability
in stream fish communities [@franssen_annual_2011] and temporal abundance
stability of birds and butterflies [@olivier_independent_nodate, but not bats].
Two mechanisms are involved into temporal stability of communities, (1)
synchrony and (2) species variability [@loreau_species_2008;
@thibaut_understanding_2013]. Synchrony measures the temporal covariation of
species. Very low synchrony indicates compensatory temporal variation between
species and so increased temporal stability. Species richness has been generally
found to decrease synchrony between species [@loreau_species_2008;
@thibaut_understanding_2013; @bluthgen_land_2016; @olivier_independent_nodate,
but @declerck_species_2006]. The average temporal variability of species is
measured as a average coefficient of variation of species, weighted by species
abundance/biomass. Higher species temporal variabiliy thus results in lower
temporal stability. Positive [@tilman_biodiversity_2006], neutral
[@jiang_different_2009; @olivier_independent_nodate] and negative
[@franssen_annual_2011; @olivier_independent_nodate] relationships between
species variability and species richness have been found. This different
patterns can be dependent on species mean variance relationships and on the
relationship between evenness and species richness
[@thibaut_understanding_2013].  Synchrony has been found to be the main driver
of temporal stability [@tilman_biodiversity_2006; @olivier_independent_nodate]
and responsible for the positive relationship between horizontal diversity and
temporal stability of biomass and abundance. (*Should I add more details about
the mecanisms?*)

Vertical diversity, represented by network structure, has been central to the
literature of diversity-stability debate and largely explored by theoretical
ecology [@may_will_1972; @angelis_stability_1975;
@stouffer_compartmentalization_2011; @thebault_stability_2010;
@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate]. Because species
interactions make species dynamics interdependant, they have a tremendous role
on stability notably through its effects on the propagation of perturbations.
However, it is important to note that theoretical ecology generally uses
stability definitions related to community equilibrium and its stability to
small independent perturbations [@may_will_1972; @angelis_stability_1975;
@barbier_pyramids_2019; @shanafelt_david_w._stability_nodate] or to the number
of secondary extinctions after species removal [@duffy_why_2009]. Those
stability metrics hardly relates to empirical temporal stability [@arnoldi_resilience_2016].
However, @thebault_trophic_2005 shows for a bi-trophic community
that asynchrony consistently increase temporal stability and a positive
relationship between temporal stability and species richness. However asynchrony
can also increase species variability through interspecific competition, which
amplifies species biomass fluctuations [@thebault_trophic_2005]. Furthermore
species interactions, considered as competition strength and niche breath of
consumers can results in negative or positive temporal stability-species
richness relationships
[@thebault_trophic_2005] depending on the food web configuration. Vertical
diversity, as network structure, can have strong effects on temporal stability.
However, there are few assesments of the effects of horizontal and diversity on
temporal stability in natural communities.

**Justify that horizontal and vertical diversity are linked**
Because horizontal & vertical diversity are not indedepent, they should be
analyzed jointly. For example, connectance generally covaries negatively with
species richness [@dunne_network_2006; @thebault_stability_2010; but see
@winemiller_must_1989]. This is also true for other metrics [@dunne_network_2006;
@delmas_analyzing_2018]. **TO DEVELOP, MOVE or RM**

#### Stream fish communities is a good model to study effects of horizontal & vertical diversity

Stream fish community constitutes a good model to study the joint effects of
horizontal & vertical diversity on total biomass and its temporal stability.
Despite that fish trophic interactions are difficult to assess in nature, a consequent
body of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Most of the biomass-diversity and stability-diversity
relationships have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types. Stream
ecosystems are characterized by the flowing water and depends for a large part
from the input of terrestrial ecosystems. Furthermore, the biotic activity in
stream ecosystems determines for a large part the water quality
[@cummins_structure_1974] and thus are crucial to maintain **human selfish
goals (can do better than that)**.

#### Environment plays a big role in structuring communities 

Environment also largely structure communities and is important to take in
account when considering natural communities. Environment directly affects
organism performance, and subsequently, abundance of species and in turn
determines total biomass [Add general ref; @grace_integrative_2016] and temporal
stability [@de_boeck_patterns_2017; @hansen_climate_2013; @bluthgen_land_2016;
@oliver_heterogeneous_2010; @friedpetersen_drivers_2020]. Hydrology of streams
constraints the composition of fish communities [REF toulouse à balle], and has
already been related to fish population temporal stability [@franssen_annual_2011].
However it is not clear which is the relative strength of direct and indirect
effects of environment on total biomass and its temporal stability (Figure
\@ref(fig:matmet) A).

#### Research questions 

The joint effects of horizontal & vertical diversity on total biomass and its
temporal stability remains yet poorly documented, especially in natural
communities. In this study, we questionned (1) whether the relationships between
horizontal diversity and total biomass/temporal stability are positive or
negative in aquatic ecosystems (Figure \@ref(fig:matmet) A). Then, as indicated
by theoretical studies, (2) what are the effects of vertical diversity on total
biomass and its temporal stability? Considering both direct & indirect effects,
(3) What is the magnitude of environmental effects on total biomass and its
temporal stability compare to horizontal and vertical diversity? (4) Which are
the pathways of the effects of environment, horizontal & vertical diversity on total
biomass and its temporal stability ? (4a) For environment, is it mainly (i)
direct, indirect (ii) through horizontal diversity, (iii) through horizontal &
vertical diversity or (iv) indirect through only vertical diversity? (4b) For
horizontal diversity, is it mainly (i) direct, or (ii) indirect through vertical
diversity?  Finally for temporal stability, (4c) how do environment, horizontal
& vertical diversity affect synchrony & species stability ?

#### SEM is a convenient approach to investigate direct and indirect path 

To reveal the direct and indirect effects of environment, horizontal & vertical
diversity on both total biomass and its temporal stability, we built and
analyzed Structural Equation Models (SEM). It is one promising way to go beyond
bivariate relationships and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. SEM makes possible to set
causal relationships between variables. This step can be critical, as the
estimated parameters can be determined by both the choice of the variables and
the links between them. Therefore, the set of variables and links should be
supported by theory and literature. We built a metamodel which present the set
of variables and the links between them (Figure \@ref(fig:matmet) A,
\@ref(fig:sem-plot) A & B). Basically, we tested the links between environmental
conditions, horizontal & vertical diversity and both total biomass and its
temporal stability (Figure \@ref(fig:matmet) A). We considered that environment
can directly affect horizontal and vertical diversity, as well as total biomass
and its temporal stability. Horizontal diversity, measured as species richness
directly affects vertical diversity, total biomass and its temporal stability.
Food web structure was shown to be constrained by species richness. In turn,
vertical diversity affects total biomass and its temporal stability (Figure
\@ref(fig:matmet) A).

We used an standardized monitoring of fish communities in french streams. 99
sites were followed more than 10 years on the 1995-2018 period. We inferred
(**XXX**) potential interaction networks, based on body size and food diet.
Horizontal diversity was quantified as species richness while vertical diversity
was as connectance and average trophic level. Environment was characterized by
the stream size, altitude, slope, and the temperature, flow and enrichment. Finally total
biomass was measured as median total biomass over the sampling period while its
temporal stability was quantified as the inverse of the CV.


- Q1:  horizontal diversity-biomass horizontal diversity-stability in aquatic systems
- Q2:  in aquatic systems
- Q2: Effect of horizontal and vertical diversity on total biomass and stablity
- Q3: Relative contribution of environment and community structure to biomass
  and stability 


# Methods

```{r}
matmet_cap <- paste0(
  "(A) Conceptual model of the hypothesized relationships between environment,
  species richness, network metrics and total biomass / biomass stability. ",
  "Solid and dashed arrows represent respectively direct and indirect effects.
  ",
  "The blue, green and blue/green dashed arrows being respectively indirect
  effects going through species richness, network metrics and through both
  species richness and network metrics.",
  "(B) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
  "Inner borders draw the limits of the hydrographic basins. ",
  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
  "(D) Subset over network variation through time."
)
```

```{r matmet, fig.cap = matmet_cap}
myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))

# Network inference
net_method_path <- mypath("manuscript/bef_stability/figs",
  "hypothesis.pdf")
metaweb_path <- mypath("manuscript/bef_stability/figs",
  "metaweb.png")
library(magick)

p_net_method <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read_pdf(net_method_path))
p_metaweb <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read(metaweb_path))

top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
  "AUTO")
bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
  rel_widths = c(1, 1), labels = c("C", "D"))

p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
  labels = c("", "C"))
save_plot(
  filename = mypath("manuscript/bef_stability/figs",
    "method_fig.pdf"),
  p_method, nrow = 2, ncol =2,
  base_width = 7/2.54,
  base_asp = 0.3
)
p_method
```


#### Protocol

Fish communities were monitored across streams of France on the period 1995-2018
by a French governmental agency (Office Français de la Biodiversité), using
electric fishing. Two different standardized protocols were used for little and
big streams (detailed in Supplementary methods). For streams shallower than (XX
m), the sampling takes place over the whole width of the streams and is done by
foot whereas in streams deeper than (XX m), the sampling is done over the bank
only and by foot or by boat. The sampling took place either in late spring and/or Autumn
and temperal series were checked to reduce sampling heterogeneity within
stations (detailed in Supplementary methods). Each station have been followed
ten years or more (i.e 10 sampling events or more). The temporal stability of
biomass, computed as inverse of the CV, can cover very different dynamics such
as decreasing, stable or increasing. However, the concept of community
variability referred to variability around an equilibrium, which is rarely
observed or difficult to characterize in natural communities. We finally kept
only the 99 stations (Figure \@ref(fig:matmet) B) which had no trends in
biomass (method detailed in Supplementary methods). However, the results
were robust to the relaxation of this hypothesis (Supplementary results).

##### Total biomass and its temporal stability 

To characterize communities variability, abundance or biomass are generally
used. When the body size and therefore body mass vary by several orders of
magnitude, one downside of abundance is that we mix individual that have
potentially really different meaning in terms of ecosystem properties such as
biomass. We therefore estimated the body mass of fish individuals according to
their body size. The body mass of individual fishes were then estimated with an
allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass in grams,
$l$ the body size in millimeters and $i$ the individual)
[@lleonart_removing_2000; @froese_cube_2006].

The species and community biomass were then computed for each sampling event.
As sampling effort, reported as the surface sampled during the sampling event,
varied across protocol type and sampling event, biomass was reported to the
surface sampled (in $m^{2}$). Community and species biomass were then expressed
in $gm^{-2}$.

Total biomass was characterized as the median total biomass over time. Temporal
biomass stability was defined as the inverse of biomass variability. Variability
was computed as Coefficient of Variation (CV) of the biomass ($CV_i = \sigma_i
\mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being respectively the standard
deviation and the temporal average of the biomass of the station $i$). Then, temporal
stability was equal to $CV^{-1} = \mu \sigma^{-1}$.

To characterize the mecanisms driving temporal stability, we decomposed
the community CV in synchrony and weighted average species CV
components according to @thibaut_understanding_2013:

$$
CV_{com} = \overline{CV_{sp}} \times \sqrt{\phi}
$$

with $CV_{com}$ being the Coefficient of Variation of the community,
$\overline{CV_{sp}}$ the average coefficient of variation of population
pondered by biomass. $\phi$ is the synchrony, which is the ratio the total
community variance ($\sigma^2_{x_T}$) and the sum of population variance
($\sigma_{x_i}$) [@loreau_species_2008].

$$
\overline{CV_{sp}} = \sum_i{\frac{B_i {CV}_i}{\sum_i{B_i}}}
$$

$$
\phi = \frac{\sigma^2_{x_T}}{\sum_i{\sigma_{x_i}}}
$$

## Hozizontal & vertical diversity

### Horizontal diversity

####  Species richness

Species richness was computed as the total species richness over time in a given
station. To normalize by sampling effort, we reported species richness to the
sum of surface sampled over the time period, it was expressed in number of
species by square meter.

### Vertical diversity

#### Trophic network inference 

```{r}
myload(metaweb_analysis, dir= mypath("data"))
meta <- metaweb_analysis
#metaweb_analysis$resource
#meta$metaweb[meta$resource, meta$resource]
```

Trophic interaction network was inferred from body size and ontogenic diet.
Body size is a reasonable approximation widely used to infer trophic
interactions [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
over lifespan. For example, alvins feed on plankton while adults may feed on
algae or fishes. Accordingly,  each fish species was divided in nine body size
classes. Each body size class constituting a trophic species. A high congruence
has been found at trophic species scale between inferred interactions and
measured trophic interactions, but not at the species
scale [@jennings_weak_2001]. We then inferred trophic interactions between the trophic species (Figure
\@ref(fig:matmet) C).  We determined network structure in two steps: (1) build a
metaweb describing the trophic interactions between all trophic
species (Figure \@ref(fig:matmet) C), then (2) determine network of a given
community by subtracting the metaweb according to the trophic species present in
a given community (Figure \@ref(fig:matmet) D). We added to each network seven
resource nodes present in food diet database: detritus, biofilm, phytoplankton,
zooplankton, macrophages, phytobenthos and zoobenthos (grey nodes in Figure
\@ref(fig:matmet) C & D). The trophic network inference procedure is detailed in
supplementary informations.

#### Trophic network structure

In each network, we computed two network metrics that have been commonly used to
characterize network structure. Connectance which describes the number of
interactions compared to the number of possible links, computed as ($C = L /
N^2$, L and N being
resp. the number of links and of trophic species plus resource nodes). We then
computed the average trophic level, the average trophic level was weighted by
the biomass of each trophic species (excluding resource nodes for which we had
no biomass) ($\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, $T_i$
and $B_i$ being resp. the trophic level and the biomass of the node $i$).

In resume, we infered binary trophic networks at the scale of trophic species
(i.e. body size classes by species) to take in account ontogenic diet shifts and
that fish-fish trophic interaction depends on body size ratio. On the other
side, the community metrics were defined at the species level, (i.e. species
richness, average species CV and synchrony).


```{r}
# Basin
st_basin <- get_basin_station(sf_obj = FALSE)

# Select fishing operation 
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

```

```{r, fig.show = "hide"}
myload(
  hab_analysis,
  temporal_station_desc,
  temporal_press_polluants,
  geo_station,
  dir = mypath("data")
)
habitat_press <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)

# Make PCA 
habitat_press %<>% na.omit()
mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
habitat_pressure <- 
  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
  as_tibble
ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
  geom_point()

ggplot(
  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
    names_to = "variable", values_to = "value"
  )
  , aes(x = value)) +
geom_histogram() +
facet_grid(cols = vars(variable))

```

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))
tot_var_expl_pca <- sum(prop_var_expl_pca) 
```

```{r, message = FALSE, results = FALSE}
# Com
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes"
)
# Compute sem dataset
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

```


## Environment

Habitat description, obtained from fish sampling data, describing the ecosystem
size namely the stream width, depth and position (altitude and
slope). Physico-chemical variables were obtained from
naiades web portal [http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/).
We chose flow and temperature to describe streams as flow
impose swimming constraints which filters fish species that can establish
[@rolls_scaling_2018; @tonkin_flow_2018; @gutierrez-canovas_contrasting_2013].
Water temperature is linked to physiological constraints namely thermal
tolerance and oxygen concentration tolerance [REF] since the level of water
saturation in oxygen is inversely linked to water temperature. We took 
Biochemical Oxygen Demand (BOD) for a proxy of enrichment in the ecosystem [REF].
BOD is also inversely linked to oxygen concentration in water and so, BOD is
also linked to physiological stress of fishes. As physico-chemical variables
were not recorded at the same place than fish communities, they were
interpolated with spatial stream networks [@isaak_applications_2014;
@hoef_ssn:_2014]. The interpolation procedure is detailed in supplementary
methods. 

For each fish station, environmental variables were matched with the year of
fish sampling (except for water temperature for which the record began in 2006).
Then, the average temperature, flow, BOD, river width and depth were computed as
well as coefficient of variation ($CV = \sigma \mu^{-1}$). As habitat and
environmental variables are often collinear, a principal component analysis (PCA)
was performed on the scaled variables. We kept in the analysis the two first
principal components based on eigen values distribution (Fig. SXX).
The PCA explained `r tot_var_expl_pca`%
of the variance. An varimax axis rotation was performed to maximize the representation
of the variables by the principal components (Fig. \@ref(fig:pca-rotated)).
Five principal components were used in the analysis, representing respectively
the (1) river size (river width & depth), (2) altitude, slope and decreasing
average temperature, (3) average enrichment (BOD) and CV of flow, (4) river size
CV (CV of river width and depth) and (5) CV of enrichment (CV of BOD). Further
informations about data transformation and filtering are detailed in
supplementary information.  

## Statistical analysis 

#### Summarise SEM statistical framework 

Structural Equation Modeling are able to assess multivariate relationships,
directs and indirects between variables.  The metamodel describes how variables
are interrelated (Figure \@ref(fig:matmet) A). We built separated structural
equation model for total biomass and its temporal variability (Figure
\@ref(fig:sem-plot) A & B). Structural equation modeling was set up according to the
hypothesis described in introduction and detailed in supplementary information.
Structural equation models were based on Gaussian linear models, some variables
were logged to fulfill model assumptions (see residual plots and data
transformation in supplementary
informations). To account for heterogeneity of hydrographic basin, we set it as random effect on the intercept. Moreover, statistical model were checked for the presence of
multicollinearity (Supplementary information). The slopes reported in the main
text are standardized in order to compare their magnitude ($r_\delta = \beta
\frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope, $\sigma_x$
and $\sigma_y$ being respectively the standard deviation of the predictive
variable $x$ and of the response variable $y$). In the main text, only the
slopes which had $P$ value inferior to $0.05$ were reported (but see Table SXX).

The structural equation models used for total biomass and its temporal stability
contains respectively 4 and 6 response variables, 35 and 26 direct paths.

#### Computation of indirect effects

The indirect effects of variables on total biomass and its temporal stability
was computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times r_{BC}$.
Only significant direct slopes were entered in the calculation of
indirect effects. Finally total effects were computed as the sum of direct and
indirect effects.


Environmental variables were interpolated with the `openStars` and `SSN`
packages. Linear models and SEMs were computed with respectively the `nlme` and
`piecewieseSEM` R packages. The code used for the analysis and the Rmarkdown
used to generate this document are accessible on github.

```{r get-data, cache = FALSE}
library(piecewiseSEM)
library(lme4)
library(nlme)

#ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

```{r}
# Compute SEMs
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

def_env_x_pos <- c(from = 0, to = 3)
asp <- 1.6

library(DiagrammeR)
meta_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "meta_stab_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE
)
p_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "stab_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2")
)

meta_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "meta_bm_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE
)
p_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "bm_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2")
)
```


```{r get-sem-coeff}
coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

coef_bm_sem <- coef(bm_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

# Results

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for (A) biomass stability and
  (B) total biomass. ",
  "Results of the Structural Equation Models for (C) the
  determinants of biomass stability and (D) total biomass. Red and green
  represent respectively negative and positive path coefficients. The path
  coefficients are standardized coeffients. For convenience, only significant
  paths (i.e, *P < 0.05*) are shown."

)
```


```{r sem-plot, fig.height = 7, fig.cap = sem_caption}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

plot_grid(
  meta_stab_sem_rich, meta_bm_sem_rich,
  p_stab_sem_rich, p_bm_sem_rich,
  labels = LETTERS[1:4], nrow = 2,
  rel_widths = c(1, 1)
)
```

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
```

```{r get-bm-tot-effect-env}
bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# rich on bm 
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")

tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```
```{r}
caption_indir_stab_sem <- paste0(
  "Indirect and total effect of variables on biomass stability from the
  structural equation model. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable, here
  biomass stability. Indirect effects are considered as one step from the target
  variable. For exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is -0.61. To compute indirect
  effect, only the significant direct effects were taken into account. ",
  "Network structure being the indirect effect that went through both avg trophic
  level and connectance and Species richness_Network structure being the
  indirect effect that went through (i) species richness and from (ii) species
  richness to network structure."
)

caption_indir_bm_sem <- paste0(
  "Indirect and total effect of variables on total biomass from the
  structural equation model. See the table 1 for details about computation and
  meaning." 
)
```

```{r}
stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab
env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
  type = "std")
rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
com_on_stab <- get_com_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")

tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```


```{r indir-stab}
kable(format_table(tmp_stab_indir_table),
  format = "latex",
  booktabs = T,
  label = paste0("indir-stab"),
  caption = caption_indir_stab_sem 
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

```{r indir-bm}
kable(format_table(tmp_bm_indir_table),
  format = "latex",
  booktabs = T,
  label = paste0("indir-bm"),
  caption = caption_indir_bm_sem
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

```{r get-sem-single-effect}
stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
```

```{r get-sem-tot-effect-env}
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on stab via network 
env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
```


Overall, the structural equation models explained a large part of the variation
of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
.45$, $.47$, $.49$ and $.38$) but not of average trophic level ($R^2 =
.18$, Figure \@ref(fig:sem-plot) C and D).

## Horizontal diversity increased total biomass but decreased its temporal stability 

```{r get-sem-tot-effect-rich}
rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

Species richness had a significant positive direct effect on total biomass
$r_\delta = `r rich_on_bm$direct`$ (Figure \@ref(fig:sem-plot) D, Table
\@ref(tab:indir-bm)). However, species richness had a total negative effect
on biomass stability ($r_\delta = `r rich_on_stab$total`$, Table
\@ref(tab:indir-stab)). Species richness had a positive effect on stability
through synchrony ($r_\delta = `r rich_on_stab$via_sync`$) but a negative  one
through $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
\@ref(tab:indir-stab)). Futhermore, species richness had a strong opposite
direct effect on $\overline{CV_{sp}}$ and synchrony, positive on
$\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$) and negative on synchrony
($r_\delta = `r rich_on_sync$direct`$).  Finally, it was surprising that the negative
effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).

## Vertical diversity increased total biomass and its temporal stability

Average trophic level had a positive effect on total biomass ($r_\delta
= `r tlvl_on_bm`$) but connectance had no significant effect (Figure
\@ref(fig:sem-plot) D). Average trophic level had a total positive effect on
temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$, Table
\@ref(tab:indir-stab)) by decreasing $\overline{CV_{sp}}$
($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) C). Again, connectance had no significant effect on
temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).

## Horizontal and vertical diversity had opposite and independant effect on total biomass and its temporal stability 

We described above that species richess had respectively a positive and a negative 
on total biomass and its temporal stability whereas average trophic level had a
positive effect on both (Table \@ref(tab:indir-bm) and \@ref(tab:indir-stab)).
The total effect of average trophic level on total biomass was of the same
magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and
$`r rich_on_bm$total`$, Table
\@ref(tab:indir-bm)). It was also true for temporal stability (resp.
$`r com_on_stab$total["t_lvl"]`$ and
$`r rich_on_stab$total`$, Table \@ref(tab:indir-stab)). Average trophic level was
dependent of species richness because species richness had a significant
negative effect on average trophic level ($r_\delta = `r rich_on_tlvl`$). 
Species richness had also a strong negative effect on connectance ($r_\delta =
`r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D).  But, in turn,
connectance had no significant effect on either total biomass nor
its temporal stability.

## Environment had an high effect on total biomass and its temporal stability 

The environmental variables had no significant direct effects on total biomass
(Table SXX), but indirect (Table \@ref(tab:indir-bm)). Average temperature and
altitude respectively increased and decreased total biomass ($r_\delta =
`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-bm)), mainly through
species richness ($r_\delta = `r env_on_bm$via_richness["log_RC2"]`$, Table
\@ref(tab:indir-bm)).  Average stream size had a positive effect on total
biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
equally through species richness and average trophic level 
($r_\delta = `r env_on_bm$via_richness["log_RC1"]`$ and
$`r env_on_bm$via_com["log_RC1"]`$ resp., Table \@ref(tab:indir-bm)). Average
temperature and altitude effects on total biomass were of the same magnitude
than the effects on species richness and average trophic level.

Average temperature and altitude had a negative and a positive effect on
temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-stab)) mainly
through a direct positive effect on $\overline{CV_{sp}}$
($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
Interesting, average temperature (and reverse of
altitude, *chiant cette variable composite*) had also a negative effect on
temporal stability through species richness but a positive one through average
trophic level (resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-stab)).
This was also true for average river size but effects were weak. Finally, the
effect of average temperature on temporal stability had a magnitude higher than
species richness and average trophic level (Table \@ref(tab:indir-stab)).
  
# Discussion

---
# Chapeau
---

#### Hat

With the aim to find out the determinants of total biomass and its temporal
stability in fish trophic communities, we analyzed a standardized dataset at
France scale going on from 1995 to 2018. We infer network structure with
together body size and food diet method and used SEM to disantangle direct and
indirect effects of environment, horizontal and vertical diversity on both total
biomass and biomass stability. We found that species richness and average
trophic level positively covariated with total biomass. However, species
richness negatively covariated with temporal stability whereas average trophic
level covariated positively. Futhermore, we found that the effect of species
richness and average trophic level on total biomass and its temporal stability
were independant. Finally, we found the magnitude of the effects of average
temperature and altitude was equal or superior to the effects of species
richness and average trophic level.

## Horizontal diversity increased total biomass but decreased its temporal stability 

We found that species richness increased total biomass as found in salt marshes,
forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
@li_relationship_2018]. The positive effect of species richness on total biomass
might be due to resource use complementarity [@cardinale_species_2002]. But
opposite relation has been found in richness in grasslands presumably because of
light competition [@grace_integrative_2016].  In accordance with theoretical
models, resource use complementarity [@loreau_biodiversity_1998;
@thebault_relationship_2006] might also be at work in fish trophic communities.

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with studies experimental studies in
grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
and even in natural communities [@olivier_independent_nodate] where positive
relationships are typically found between temporal stability and species
richness. In streams as well, @franssen_annual_2011 found that species richness
increased temporal stability. However other studies found a opposite relationship
in natural grassland [@yang_effects_2011] or a marginal one
[@declerck_species_2006] in natural forests. Further investigations are needed
to identify the mechanisms behind those contrasting patterns,

- add [@yang_effects_2011]

 Species richness decreased synchrony
and increased $\overline{CV_{sp}}$. Species richness can reduce synchrony
through decrease of population size, thus raising the role of demographic
stochasticity [@loreau_species_2008] but also in the case where species have
different responses to environmental variation [@loreau_species_2008]. While the
effect of species richness on synchrony is well understood, its effect on
$\overline{CV_{sp}}$ is more complex [see @thibaut_understanding_2013]. 

Suprisingly, we found that $\overline{CV_{sp}}$ had an negative effect twice
higher than synchrony on biomass stability.In turn,
we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013]. However, it was unexpected that the average
population $\overline{CV_{sp}}$ had a stronger negative effect on biomass
stability than synchrony [@bluthgen_land_2016; @olivier_independent_nodate]. We
can advance two hypothesis that can raise this effect. First, the opportunity
for diet differentiation can be low in streams compare to other organisms.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

- But @thebault_relationship_2006 with the same mecanisms on vertical and
  horizontal diversity

## Vertical diversity increased total biomass and its temporal stability

The average trophic level was positively linked to total biomass. This result is
straightforward. As feeding interactions were partly determined by body size and
that body mass increase with body size, it is expected that the more the average
biomass is located at higher trophic level, the more the total biomass increase.
In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance should translate in higher resource transfer
efficiency between prey and predators and so results in higher total biomass. A
reason for such an absence of an effect might be the absence of an interaction
strength knowledge/estimation. A consequence can be that connectance contains
few too informations. [ADD @thebault_relationship_2006].

Average trophic level had a positive effect on biomass stability by its negative
effect on CVsp (i.e. positive effect on average species stability). It means
that species at higher trophic level are more stable than the species at lower
trophic levels. @shanafelt_david_w._stability_nodate and @barbier_pyramids_2019
found the same pattern with pure trophic chain models. They have shown that
strong top-down control can generate the pattern that we observed but it is not
clear if this theoretical prediction holds when considering omnivorous species
(i.e not a pure food chain) and if other mechanisms can generate the same
pattern.  For example, species mean-variance relationship could also generate
this pattern. Moreover, the ontogenic nature of our networks can also be an
important mechanism at play.  Over its life span, a given fish will change of
diet and thus move upward in the trophic chain. The dynamic of a given species
composed of several trophic species can thus be a mix of the dynamics of several
trophic levels, plus the oscillatory dynamics of the cohorts
[@townsend_population_1989; @medvinsky_modelling_2015]. Then, there is a clear
need for a better understanding of how the dynamics of pure food chain models
would be affected by inclusion of omnivory and ontogeny.

We found that connectance had no effect on temporal stability. This result
contradicts precedent theoretical studies on the relationship between stability
and network structure [@angelis_stability_1975; @may_will_1972;
@thebault_stability_2010], although they considered different stability metrics
(i.e. local stability of equilibrium point). Once again, it is possible that
that connectance from our networks contains too few information.
Furthermore, a crucial missing ingredient to go further is the interaction
strength. Indeed, @may_will_1972 has theoretically demonstrated the
fondamental interplay between connectance, species richness and average
interaction strength (*Add ref and develop a bit*).


## Horizontal and vertical diversity had common, opposite and dependant effects on total biomass and its temporal stability 

We found that species richness had a positive and a negative effect on
respectively total biomass and its temporal stability whereas average trophic
level had a positive effect on both. It confirms that more investigation is needed to
understand the mechanisms leading to common and opposite effects of
horizontal and vertical diversity. @thibaut_understanding_2013 have
theoretically shown that a highly positive relationship between species variance
and mean together with a positive relationship between mean species abundance
(i.e. dominance) and species richness should drive to a negative temporal
stability - species richness relationship. @thebault_relationship_2006 have
also shown in a bi-trophic foodweb that a positive temporal stability-species
richness appears in case of a plant species is highly dominant through low
comsumption by consumers but in the same time highly variable because of low
competitive ability. Then, common mecanisms might be at play for both horizontal
and vertical diversity while having same or opposite effects on total biomass
and its temporal stability.

We found that connectance covaries negatively with species richness
[@winemiller_must_1989; @dunne_network_2006; @thebault_stability_2010],
connectance had itself no effects on both total biomass and its temporal
stability. On the other side, we found species richness was negatively related
to average trophic level and average trophic level covariated positively with
total biomass and its temporal stability. Hence, horizontal diversity had a
direct positive and negative effect respectively on total biomass and its
stability but a negative and positive effect through vertical diversity. It
indicates the importance to consider both horizontal, vertical diversity and
their dependance.

## Environment had an high effect on total biomass and its temporal stability 

- add [@yang_effects_2011]

Precedent researches in plant communities showed that the total biomass was
primary driven by environmental drivers [@grace_integrative_2016]. We did not
find direct but indirect effects of environmental drivers on total biomass. The
average temperature (& inverse altitude) was positively linked to total biomass
mainly through species richness while the average stream size had a positive
link equally through species richness and average trophic level. It is not
straightforward to explain why the effect average temperature and altitude was
going through horizontal diversity and why average stream size is going through
both horizontal and vertical diversity.  (*Add more biological interpretations
about total effect? Until now, what I have in mind is a bit bullshit and those
explanations are not the heart of the paper.  What do you think?*).  Overall it
indicates that environment affects primarily community structure and then
affects total biomass. Furthermore, one can notice that average temperature had
a positive effect on total of the same magnitude than horizontal & vertical
diversity. It underlines that environment should not be ignored in natural
communities studies and that its effects can be mainly indirect and in this
case, path analysis should more relevant than bivariate relationships
[@grace_causal_2014; @grace_integrative_2016]. 

Average temperature (& inverse of altitude) had a negative effect on temporal
stability, mainly by an direct positive CVsp. Two mecanisms might explain this
pattern: (i) temperature is negatively linked to concentration of dissolved
oxygen and so might be linked to respiration stress, (ii) temperature might lead
be to higher metabolic activity and so higher variability [@taby_warming_2019].
Interestingly, average temperature (& inverse of altitude) had also a negative
effect on temporal stability through species richness but a positive one through
average trophic level. Then, the effect of temperature on temporal stability
might be more complex than previously thought and call for further
investigations. Furthermore, average temperature and altitude had a stronger
effect on temporal stability than horizontal and vertical diversity. Considering
big effects of temperature on both total biomass and its temporal stability
might suggest the crucial role of climate change on stream ecosystems. (*Not
convinced: may be to discuss together*)

# Conclusion and perspectives 

We aimed to assess the effect of horizontal & vertical diversity on empirical
trophic communities. While theoretical ecology has focused on the effects of
network structure on stability, empirical ecology has focused on species richess
and ingnored network structure. Furthermore, both fields have largely used
different stability metrics. We showed that horizontal and vertical diversity
can have independent and sometimes opposite effects on total biomass and its
temporal stability. It opens a promising way for the understanding on how
species interactions, of different types, can affect both synchrony and CVsp in
different ecosystems. The reconstruction of ecological networks based on trait
can be a first approach to document such relationships, however it will not
compensate for close evaluation of measured interaction strength. We also
believe that SEM methods are particularly helpful to assess complex relationship
between environment, community structure and ecosystem properties in empirical
data which necessitate to move from simple bivariate relationships
[@grace_integrative_2016]. We believe that the integration of network structure
and species interaction in general will improve our understanding of the
mechanisms which determines ecosystem properties. (*c'est pas top mais à
discuter*)


```{r}
save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
```

# References
