---
title: Species richness and network structure jointly drive total biomass and its temporal stability in fish communities
author: Alain Danet, Maud Mouchet, (Willem Bonnaffe ici?), Elisa Thebault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
---

```{r, echo = FALSE, results = FALSE, message = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = FALSE 
)

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```

```{r, results = FALSE}
knitr::opts_chunk$set(
  results = TRUE 
)
```

- Author affiliation:
  - Alain Danet:
  - Maud Mouchet:
  - Willem Bonnaffe:
  - Elisa Thebault: 
  - Colin Fontaine:

- Author contributions: AD, CF, MM and ET designed the study. WB designed the
  network inference method and collected the food diet data. AD performed the
  data analysis and wrote the first draft of the manuscript. All authors
  contributed substantially to revisions.  

- Data accessibility statement: the ONEMA database is available upon request to 
  eddy.cosson@afbiodiversite.fr and thierry.point@afbiodiversite.fr. The code
  used for the analysis and to generate the manuscript is available on github:
  (alaindanet/fishcom.git)

- Article type: Letters

- Number of words:
  - Abstract: 194
  - Main text: XXXX 

- Number of references: XXX
- Number of figures: 2
- Number of tables: 2
- Number of text boxes: 0 

- Coresponding author:
  - Alain Danet
  - UMR 7204 CESCO, BP 61; 45, rue Buffon, 75005 Paris, France
  - alain.danet@mnhn.fr 
  - +331XXXXXXXX

# Abstract

The effect of species richness and network structure on ecosystem properties has
been central to ecology. It has been at the basis of the predictions of the
effect species richness and  network structure on total biomass, productivity
and stability. However, empirical data are lacking on the link between network
structure and ecosystem properties. We used a dataset of standardized fish
sampling in French stream running from 1995 to
2018. We inferred trophic interactions thanks to recorded body size and diet
literature. We then investigate the direct and indirect effects of stream
size and temperature, species richness and network structure on total biomass and
its temporal stability. We found that species richness and network structure had
a positive relationship with total biomass while they had respectively a
negative and positive effect on temporal stability. We also found that
species richness and network structure are not independent and that environment
had an tremendous effect on total biomass and its temporal stability notably
through its effect on species richness and network structure. We conclude that our
study highlights that the effects of species richness and network structure should be 
assessed conjointly and that it opens exciting perspectives on how environment,
species richness and network structure can jointly determine total biomass in natural
communities.

(210/150 words)

# Introduction 

#### Biodiversity and ecosystem properties 

Current biodiversity losses and global changes has the potential to affect
ecosystems in complex ways [@bellard_impacts_2012]. Biodiversity has a
tremendous effect on ecosystem properties because it largely determines both the
amount and the distribution of matter and energy fluxes
within ecosystems [@duffy_why_2009]. Biodiversity thus affects biomass
production [@tilman_productivity_1996; @cardinale_species_2002;
@grace_integrative_2016], biomass repartition [@thebault_relationship_2006] and
biomass stability [@thebault_trophic_2005; @thebault_relationship_2006;
@tilman_biodiversity_2006]. The relationship between biodiversity and
ecosystem properties is a central topic in ecology [@hector_plant_1999;
@loreau_biodiversity_2001; @hooper_effects_2005; @dunne_network_2006;
@duffy_why_2009; @isbell_forest_quantifying_2018] and its documentation is thus
crucial to better anticipate the impacts of global changes. 

#### Species richness increases total biomass

Species richness promotes higher biomass production in a variety of ecosystems
and organisms. Indeed species richness generally increases primary productivity
and total biomass in experimental plant communities [@tilman_productivity_1996;
@grace_integrative_2016; @hector_plant_1999; @tilman_biodiversity_2014;
@grace_integrative_2016], but also in briophyte communities
[@mulder_physical_2001], stream feeders [@cardinale_species_2002] and aquatic
bacterial consumers [@pennekamp_biodiversity_2018]. Theoretical models also
predict this pattern in plant communities [@tilman_plant_1997;
@loreau_partitioning_2001] and food webs [@schneider_animal_2016]. Resource use
complementarity and selection effects have been proposed to elucidate the
positive effect of species richness on productivity. The complementarity in
resource use, rising through niche differentiation and interspecific
facilitation, increase the total amount of resource used
[@loreau_biodiversity_1998; @cardinale_species_2002; @loreau_partitioning_2001].
A positive selection effect arises when species richness leads to an higher dominance
of the most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
In contrast, both positive [@wu_relationship_2014; @li_relationship_2018],
negative or no effects [@szwagrzyk_above-ground_2007; @jacob_productivity_2010;
@seidel_relationship_2013] of species richness on total biomass have been found
in natural forest. Some authors suggest that the lack of resource
complementarity or environmental harshness might be responsible for an absence or a
negative effect of species richness [@loreau_partitioning_2001; @he_global_2013;
@wu_relationship_2014]. Overall, under what conditions and through what
mechanisms we should observe positive relationships between biomass and species
richness in natural settings is still an open question.

Many studies showed that species richness also increases temporal stability,
i.e. variation through time, often quantified using CV. Such positive
relationships between species richness and temporal stability have been reported
in experimental grasslands and aquatic bacterial systems
[@tilman_biodiversity_2006; @pennekamp_biodiversity_2018]. Theoretical works
have clarified which mechanisms generate this positive relationship between
species richness and temporal stability [@loreau_species_2008;
@thibaut_understanding_2013]. Two mechanisms may govern the temporal stability
of communities, (1) species synchrony and (2) species variability. Species
synchrony quantify to what extent the fluctuations of abundances or biomasses
through time are correlated among species. A low synchrony in species
fluctuations, i.e.  asynchrony, is synonymous of compensatory dynamic, where the
decrease in abundance of a species is compensated by the increase of an other.
Asynchrony is generally the main mechanism whereby species richness has a
stabilizing effect on temporal stability [@tilman_biodiversity_2006;
@olivier_independent_nodate].  ^[Colin asked for a word about $cv_{sp}$ and
stability but my opinion is that it is not necessary and that the depth of mecanisms are
currently fairly explained for the introduction]. Such positive relationships
between speciesrichness and temporal are also observed in natural settings, such
as stream fish communities [@franssen_annual_2011], bird and butterfly
communities [@olivier_independent_nodate].


#### Multitrophic communities
 
One has to notice that most of the empirical and experimental evidence of the
positive effect of richness on biomass production and stablity through time
comes from studies focusing on one trophic level, generally primary producers or
primary consumers. Natural ecosystems generally include
more than one or two trophic levels and it is not certain that what holds
on one trophic level hold also in multitrophic communities.
Theoretical studies showed that food web properties, such as interaction
distribution and strength, affect the distribution of biomass among adjacent
trophic levels, [@thebault_relationship_2006; @schneider_animal_2016;
@barbier_pyramids_2019]. A
large body of theoretical studies links the propagation of perturbations to the
foodweb structure [@may_will_1972; @angelis_stability_1975; @dunne_network_2006;
@neutel_reconciling_2007; @duffy_why_2009; @stouffer_compartmentalization_2011],
or trophic chain [@shanafelt_david_w._stability_nodate; @wang_biodiversity_2016;
@barbier_pyramids_2019]. To date, we have few evidence on the relationship
between network structure and total biomass and its temporal stability in
empirical multitrophic communities.

#### Problematic

Overall, the evidence suggests that both species richness and network structure
should modulate total biomass and stability of communities. The effects of
species richness and network structure are potentially conflicting or
synergistic in such a way that they need to be addressed jointly. Yet, there is
no direct empirical evidence to date for the combined effects of species
richness and network structure on total biomass and stability in natural
communities.

#### Environment can mitigate community structure and ecosystem properties 

When assessing the relationship between community structure and ecosystem
properties in natural communities, it is crucial 
to consider environmental factors [@loreau_biodiversity_2001;
@he_global_2013; @grace_integrative_2016]. Environment affects organism
performance directly, and thereby, species abundances, total biomass
[@grace_integrative_2016] and temporal stability [@de_boeck_patterns_2017;
@hansen_climate_2013; @bluthgen_land_2016; @oliver_heterogeneous_2010; @franssen_annual_2011;
@friedpetersen_drivers_2020]. For example, greater ecosystem size might increase
the number of available resources and thus total biomass [@post_ecosystem_2000;
@doi_resource_2009]. @li_relationship_2018 have notably shown that climate
moisture has a positive direct effect on total biomass, but also indirect
through a positive effect on species richness. Taking in consideration
environment also allow for an overall comparison of the strength of the
the effects of environment and community structure on total biomass and its
stability.


#### Stream fish communities is a good model to study effects of horizontal & vertical diversity

Stream fish community constitutes a good model to study the effects of
network structure on total biomass and its temporal stability. Despite that
fish trophic interactions are difficult to measure in nature, a consequent body
of literature supports that they can be inferred through body size and diet
informations [@gravel_inferring_2013; @jennings_weak_2001;
@brose_predator_2019]. Especially in stream communities, including fishes,
@brose_predator_2019 found that the prediction of predator prey trophic
interactions based on body size ratio was far better in stream ecosystems than
in other aquatic and te ecosystems. Furthermore, the biotic activity in stream
ecosystems determines for a large part the water quality
[@cummins_structure_1974] and thus are crucial to maintain stream ecosystem
properties. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems
while there is a evident need to test such relationships in a variety of
ecosystem types.

We used the ONEMA dataset consisting in standardized sampling of fish
communities in French streams [@edeline_ecological_2013]. 99 sites were sampled
for more than 10 years spanning on the 1995-2018 period. We inferred
1496 interaction networks, based on body size and food diet.  The network
structure was summarized by connectance and mean trophic level. Environment
was characterized by the stream size, altitude, slope, and the temperature, flow
and enrichment. Finally total biomass was measured as median total biomass over
the sampling period while its temporal stability was quantified as the inverse
of the CV.

We found a positive relationship between total biomass and species richness and
network structure  while total biomass and species richness had respectively a
negative and positive effect on temporal stability. We also showed a link
between species richness and network structure. We found that the environment had
a strong effect on total biomass and its temporal stability in particular by 
its effect on species richness and network structure. We then discuss the
possible mechanisms at play to explain those results and their implications on
our knowledge of the effect of network structure on ecosystem properties.


# Methods

```{r}
matmet_cap <- paste0(
  "(A) Conceptual model of the hypothesized relationships between environment,
  species richness, network metrics and total biomass / biomass stability. ",
  "Solid and dashed arrows represent respectively direct and indirect effects.
  ",
  "The blue, green and blue/green dashed arrows being respectively indirect
  effects going through species richness, network metrics and through both
  species richness and network metrics.",
  "(B) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. ", "Grey shades highlighted elevalation variation. ",
  "Inner borders draw the limits of the hydrographic basins. ",
  "(C) The metaweb. Each trophic species (N = 412) is represented by a node and
  each color represent a species (S = ). Resource nodes (7) were drawn in grey. ",
  "(D) Subset over network variation through time."
)
```

```{r matmet, fig.cap = matmet_cap}
myload(p_st,temporal_network, dir = mypath("manuscript/bef_stability/figs"))

# Network inference
net_method_path <- mypath("manuscript/bef_stability/figs",
  "hypothesis.pdf")
metaweb_path <- mypath("manuscript/bef_stability/figs",
  "metaweb.png")
library(magick)

p_net_method <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read_pdf(net_method_path))
p_metaweb <- cowplot::ggdraw() +
  cowplot::draw_image(magick::image_read(metaweb_path))

top <- plot_grid(p_net_method, p_st, ncol = 2, rel_widths = c(1, 1), labels =
  "AUTO")
bottom <- plot_grid(p_metaweb, temporal_network, ncol = 2,
  rel_widths = c(1, 1), labels = c("C", "D"))

p_method <- plot_grid(top, bottom, nrow = 2, rel_heights = c(1, 1),
  labels = c("", "C"))
save_plot(
  filename = mypath("manuscript/bef_stability/figs",
    "method_fig.pdf"),
  p_method, nrow = 2, ncol =2,
  base_width = 7/2.54,
  base_asp = 0.3
)
p_method
```


## Data collection

#### Protocol

Fish communities were monitored across stream sections in France on the period
1995-2018 by the French Office of Water and Aquatic Ecosystems
(ONEMA) using electric fishing. Two different standardized protocols were used
for little and big streams (detailed in Supplementary methods). For streams
shallower than (XX m), the sampling takes place over the whole width of the
streams and is done by foot whereas in streams deeper than (XX m), the sampling
was done over the bank by foot or by boat. The sampling season spans from 
late spring to Autumn. During sampling, all the fishes caught were
identified and counted. For each species, either the body size of all fish was
measured, or a representative sample when the number of fish was high (See
supplementary methods for details). The fishes were released at the end
of the sampling. Additionally, the physical characteristics of the river was
recorded during sampling as well as the sampling effort, quantified as the
surface sampled.


#### Data selection

We kept only the most frequent sampling protocol in each station and kept
stations that had been sampled ten years or more. The median sampling month was
mid-August while the median of the standard deviation of the sampled month
within station was $0.7$, i.e. there was low heterogeneity of the sampling month
within stations. As the concept of community variability referred to variability
around an equilibrium, which is rarely observed or difficult to characterize in
natural communities, only those stations with no temporal trends in total
biomass were selected (detailled in supplementary methods). However, the results
were robust to the relaxation of this hypothesis (Supplementary results). We
retained 99 stations distributed over seven hydrographic basins (Figure
\@ref(fig:matmet) B). 

## Data preparation 

#### Biomass  

The body size of the unmeasured individuals was inferred under the assumption
that species body size followed a normal distribution whose the mean and the
standard deviation was quantified from the measured individuals of the sampling
(See supplementary methods). The body mass of each individual was then estimated
using an allometric law ($B_i = 0.01 \times l_i^{3.03}$, $B$ being the body mass
in grams, $l$ the body size in millimeters and $i$ the individual), where the
coefficients $0.01$ and $3.03$ comes from meta-analysis
[@lleonart_removing_2000; @froese_cube_2006]. The species biomass
and total biomass at each sampling was then calculated by summing individual
body masses. To account for the sampling effort, species biomass and total
biomass have been related to the surface sampled, i.e. $gm^{-2}$.
In the further analysis, the total biomass of a station has been defined as the
median of the total biomass over time.

Temporal biomass stability was defined as the inverse of biomass variability.
Variability was computed as Coefficient of Variation (CV) of the biomass over
time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
respectively the standard deviation and the temporal average of the biomass of
the station $i$). Then, temporal stability was equal to $CV^{-1} = \mu
\sigma^{-1}$.

In order to describe the mechanisms driving temporal stability of biomass, we
decomposed the $CV$ of total biomass ($CV_{com}$) in synchrony ($\phi$) and
weighted average species $CV$ (\overline{CV_{sp}}) components according to
@thibaut_understanding_2013:

$$
CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
$$

with $CV_{com, i}$ being the Coefficient of Variation of the biomass in the
station $i$, $\overline{CV_{sp, i}}$ the average coefficient of variation of
species in the station $i$ weighted by the biomass of the species, $B_{k,i}$.
Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
total biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
population biomass over time ($\sigma_{x_k}$) [@loreau_species_2008]. $i$ being
the station $i$ and $k$ the species $k$.

$$
\overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
$$

$$
\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2}
$$

####  Species richness

Species richness was computed as the total number of species present over time
in a given station. As for biomass, we controlled species richness for sampling
effort by dividing the total number of species by the total surface sampled in
the given station. Species richness was then expressed in number of species by
square meter sampled.

### Network structure

#### Trophic network inference

```{r}
myload(metaweb_analysis, dir= mypath("data"))
myload(trophic_class, dir= mypath("data", "classes"))
meta <- metaweb_analysis
#metaweb_analysis$resource
#meta$metaweb[meta$resource, meta$resource]
```

Trophic interaction network was inferred from body size and ontogenic diet shift.
Body size is a reasonable approximation widely used to infer trophic
interactions [@gravel_inferring_2013; @brose_predator_2019;
@poisot_structure_2016]. The diet of stream fishes, as many organisms, shifts
over lifespan. For example, alvins feed on plankton while adults may feed on
algae or fishes. Accordingly, each fish species was divided in nine body size
classes, each of which is trophic species (Figure SXX). A high congruence
between inferred interactions and measured trophic interactions has been found
at trophic species scale but not at the species scale [@jennings_weak_2001].
Additionally to the fish trophic species, we added seven resource nodes present
in ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
macrophages, phytobenthos and zoobenthos (grey nodes in Figure \@ref(fig:matmet)
C & D). The ontogenic diet database was based on informations from fishbase and
literature. Each fish species had two or three life stages which are delimited by
body size (Table SXX, Figure SXX). 

The trophic interactions of fish trophic species was determining with the median
of its body size range, hereafter after midpoint. The midpoint of trophic
species fall into one of the species life stage and a trophic link was set
between the trophic species and the resources present in the life stage. If the
trophic species is in a piscivorous life stage, the fish-fish trophic links was
defined in two steps and based on the body size ratio between predators and
prey. First of all, we defined the range predation window from 3% to 45% of the
midpoint of the trophic species. Then, a trophic link was set between the
piscivorous trophic species and every trophic species whose midpoint was
included in the predation range (Figure SXX). Lastly, the trophic links between resources was
set according to the food diet data.

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between all trophic species and the resources (Figure
\@ref(fig:matmet) C), then (2) determine network of a given community by
subtracting the metaweb according to the trophic species present in a given
site and sampling event (Figure \@ref(fig:matmet) D).

For each trophic network, corresponding to a particular site and sampling, we
computed two of the most commonly used network metrics to characterize the food
web, namely the connectance and mean trophic level. Connectance describes 
the level of generalism in the network and is calculated as the number of actual
interaction divided by the maximum number of interaction if all species interact
together ($C = L / N^2$, L and N being resp. the number of
links and of trophic species plus resource nodes). The trophic level of the
nodes was computed of the nodes that the predator nodes consumes
to which is added one, obtained recursively by setting the trophic level of
basal nodes to 1. The mean trophic level $\overline{T}$ was computed as the mean trophic level
weighted by the biomass of each trophic species (excluding resource nodes for
which we had no biomass information), so
$\overline{T} = \sum_i^N{B_iT_i \times \sum_i^N{B_i}^{-1}}$, with $T_i$ and $B_i$
being resp. the trophic level and the biomass of the node $i$. 




```{r}
# Basin
st_basin <- get_basin_station(sf_obj = FALSE)

# Select fishing operation 
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

```

```{r, fig.show = "hide"}
myload(
  hab_analysis,
  temporal_station_desc,
  temporal_press_polluants,
  geo_station,
  dir = mypath("data")
)
habitat_press <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)

# Make PCA 
habitat_press %<>% na.omit()
mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
habitat_pressure <- 
  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
  as_tibble
ggplot(habitat_pressure, aes(x = RC2, y = temperature_med)) +
  geom_point()

ggplot(
  pivot_longer(habitat_pressure, cols = c("RC1", "RC2"),
    names_to = "variable", values_to = "value"
  )
  , aes(x = value)) +
geom_histogram() +
facet_grid(cols = vars(variable))

```

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))
tot_var_expl_pca <- sum(prop_var_expl_pca) 
```

```{r, message = FALSE, results = FALSE}
# Com
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes"
)
# Compute sem dataset
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )

```


## Environment

we characterised the sampled sites by their altitude, slope, distance from
source, stream width and depth and its strahler order, i.e. its position in the
stream network. From the naiades database
[http://www.naiades.eaufrance.fr/](http://www.naiades.eaufrance.fr/), we also
got data on water temperature and flow as they affect the type of fish that can
establish [@franssen_annual_2011; @rolls_scaling_2018; @tonkin_flow_2018;
@gutierrez-canovas_contrasting_2013] as well as BOD (Biological Oxygen Demand)
as a proxy for eutrophisation. As data from the naide database are not collected
on same site as our fish sampling sites, we performed an interpolation with
spatial stream networks [@isaak_applications_2014; @hoef_ssn:_2014]. The
interpolation procedure is detailed in supplementary methods.

We had one environmental variable value for each site and sampling event, except
for water temperature for which the record began in 2006. Then, we computed the average over
time and the CV over time for water temperature, flow, BOD, river width and
depth. As habitat and environmental variables are often collinear, a principal
component analysis (PCA)
was performed on the 14 scaled variables. We kept in the analysis the two first
principal components based on eigen values distribution (Fig. SXX).
The two first principal components explained `r tot_var_expl_pca`%
of the variance. A varimax axis rotation was performed to maximize the representation
of the variables by the principal components (Figure SXX).
The two first principal components were used in the analysis, representing respectively
the (1) river size (river width & depth), (2) altitude, slope and decreasing
average temperature. Further description of the variables are detailed in
supplementary information.

## Statistical analysis 

#### Summarise SEM statistical framework 

Structural Equation Modeling are able to assess multivariate relationships
between variables. It is one promising way to go beyond bivariate relationships
and to investigate complex relationships, direct and
indirect, between variables [@grace_structural_2008; @grace_causal_2014;
@lefcheck_piecewisesem_2016; @grace_integrative_2016]. We built the biomass
model (Figure \@ref(fig:matmet) A, \@ref(fig:sem-plot) B) by considering that environment
can directly affect species richness and network structure, as well as total
biomass. Species richness directly affects total biomass. Food web structure
was shown to be constrained by species richness @winemiller_must_1989;
@dunne_network_2006; @thebault_stability_2010. In turn,
the network structure affects total biomass (Figure
\@ref(fig:matmet) A, \@ref(fig:sem-plot) B). We used the same model structure for
temporal variability (Figure \@ref(fig:sem-plot) A). The structural equation
models used for total biomass and its temporal stability contains respectively 4
and 6 response variables, 35 and 26 direct paths.

Structural equation models were based on Gaussian linear models, some variables
were logged to fulfill model assumptions (see residual plots and data
transformation in supplementary informations, Table SXX). To account for the heterogeneity
between the seven hydrographic basins, we set it as random effect on the
intercept of the linear model. The absence of multicollinearity 
was checked with Variance Inflation Factor (VIF, Table SXX). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). In the main text,
only the slopes which had a $P$ value inferior to $0.05$ were reported (but see
Table SXX and SXX).  

The indirect effects of variables on total biomass and its temporal stability
was computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
r_{BC}$.  Only significant direct slopes were entered in the calculation of
indirect effects. Finally total effects were computed as the sum
of direct and indirect effects.

Environmental variables were interpolated with the `openStars` and `SSN`
packages. Linear models and SEMs were computed with respectively the `nlme` and
`piecewieseSEM` R packages. The code used for the analysis and the Rmarkdown
used to generate this document are accessible on github.

```{r get-data, cache = FALSE}
library(piecewiseSEM)
library(lme4)
library(nlme)

#ctrl <- lmeControl(opt='optim')
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

```{r}
# Compute SEMs
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

def_env_x_pos <- c(from = 0, to = 3)
asp <- 1.6

library(DiagrammeR)
meta_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "meta_stab_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE
)
p_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "stab_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2")
)

meta_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "meta_bm_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE
)
p_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "bm_sem"),
  format = "png",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2")
)
```


```{r get-sem-coeff}
coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

coef_bm_sem <- coef(bm_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

# Results

```{r}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for (A) biomass stability and
  (B) total biomass. ",
  "Results of the Structural Equation Models for (C) the
  determinants of biomass stability and (D) total biomass. Red and green
  represent respectively negative and positive path coefficients. The path
  coefficients are standardized coeffients. For convenience, only significant
  paths (i.e, *P < 0.05*) are shown."

)
```


```{r sem-plot, fig.height = 7, fig.cap = sem_caption}
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

plot_grid(
  meta_stab_sem_rich, meta_bm_sem_rich,
  p_stab_sem_rich, p_bm_sem_rich,
  labels = LETTERS[1:4], nrow = 2,
  rel_widths = c(1, 1)
)
```

```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
```

```{r get-bm-tot-effect-env}
bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# rich on bm 
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")

tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```
```{r}
caption_indir_stab_sem <- paste0(
  "Indirect and total effect of variables on biomass stability from the
  structural equation model. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable, here
  biomass stability. Indirect effects are considered as one step from the target
  variable. For exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is -0.61. To compute indirect
  effect, only the significant direct effects were taken into account. ",
  "Network structure being the indirect effect that went through both avg trophic
  level and connectance and Species richness_Network structure being the
  indirect effect that went through (i) species richness and from (ii) species
  richness to network structure."
)

caption_indir_bm_sem <- paste0(
  "Indirect and total effect of variables on total biomass from the
  structural equation model. See the table 1 for details about computation and
  meaning." 
)
```

```{r}
stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab
env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
  type = "std")
rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
com_on_stab <- get_com_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")

tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, com_on_stab),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```



```{r indir-bm}
kable(format_table(tmp_bm_indir_table),
  format = "latex",
  booktabs = T,
  label = paste0("indir-bm"),
  caption = caption_indir_bm_sem
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

```{r get-sem-single-effect}
stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
```

```{r get-sem-tot-effect-env}
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on stab via network 
env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
```

```{r indir-stab}
kable(format_table(tmp_stab_indir_table),
  format = "latex",
  booktabs = T,
  label = paste0("indir-stab"),
  caption = caption_indir_stab_sem 
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

Overall, the structural equation models explained a large part of the variation
of connectance, synchrony, $\overline{CV_{sp}}$ and total biomass (resp. $R^2 =
.45$, $.47$, $.49$ and $.38$) but not of mean trophic level ($R^2 =
.18$, Figure \@ref(fig:sem-plot) C and D).

## Total biomass

```{r get-sem-tot-effect-rich}
rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

Species richness and mean trophic level had a significant positive direct effect on total biomass
($r_\delta = `r rich_on_bm$direct`$ and $r_\delta = `r tlvl_on_bm`$ resp., Figure
\@ref(fig:sem-plot) D, Table \@ref(tab:indir-bm)), while connectance had no
direct nor indirect significant effect (Figure \@ref(fig:sem-plot) D) on total
biomass. The total effect of mean trophic level on total biomass was of the same
magnitude than the one of species richness (resp. $`r tlvl_on_bm`$ and $`r
rich_on_bm$total`$, Table \@ref(tab:indir-bm)). 

Species richness had a significant negative effect on mean trophic level
($r_\delta = `r rich_on_tlvl`$) and a strong negative effect on connectance
($r_\delta = `r rich_on_stab$total`$, Figure \@ref(fig:sem-plot) C and D). But,
in turn, connectance had no significant effect on total biomass.

The environmental variables had no significant direct effects on total biomass
(Table SXX), but indirect (Table \@ref(tab:indir-bm)). Average temperature and
altitude respectively increased and decreased total biomass ($r_\delta =
`r env_on_bm$direct["log_RC2"]`$, Table \@ref(tab:indir-bm)), mainly through
species richness ($r_\delta = `r env_on_bm$via_richness["log_RC2"]`$, Table
\@ref(tab:indir-bm)). Average stream size had a positive effect on total
biomass ($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-bm)),
equally through species richness and mean trophic level ($r_\delta = `r
env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_com["log_RC1"]`$
resp., Table \@ref(tab:indir-bm)). Average temperature and altitude effects on
total biomass were of the same magnitude than the effects on species richness
and mean trophic level.

## Temporal stability of biomass

By its effect on synchrony and $\overline{CV_{sp}}$, species richness had a
negative total effect on biomass stability ($r_\delta = `r rich_on_stab$total`$,
Table \@ref(tab:indir-stab)). On the one hand, species richness had a direct
negative effect on synchrony ($r_\delta = `r rich_on_sync$direct`$), thereby
increasing stability ($r_\delta = `r rich_on_stab$via_sync`$). On the other
hand, species richness had a
positive direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$),
thereby decreasing biomass stability ($r_\delta = `r rich_on_stab$via_cv_sp`$, Table
\@ref(tab:indir-stab)). Finally, it was surprising that the negative
effect of $\overline{CV_{sp}}$ on temporal stability was twice higher than the
negative effect of synchrony (resp. $r_\delta = `r cv_sp_on_stab`$ and $r_\delta
= `r sync_on_stab`$, Figure \@ref(fig:sem-plot) C).

The mean trophic level had a direct negative effect on
$\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$,
Figure \@ref(fig:sem-plot) C) and thereby had a total positive
effect on temporal stability ($r_\delta = `r com_on_stab$via_cv_sp["t_lvl"]`$,
Table \@ref(tab:indir-stab)). The mean trophic level had no significant
effect on synchrony and connectance had no significant direct, nor indirect
effect on temporal stability (Figure \@ref(fig:sem-plot) C, Table SXX).
The total effect of mean trophic level on temporal stability of biomass was of
the same magnitude than the one of species richness (resp.
$`r com_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-stab)). 

Average temperature and altitude had a negative and a positive effect on
temporal stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table \@ref(tab:indir-stab)) mainly
through a direct positive effect on $\overline{CV_{sp}}$
($r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$, Table \@ref(tab:indir-stab)).
Interestingly, average temperature (and opposite of altitude) had also a negative
effect on temporal stability through species richness but a positive one through
mean trophic level 
(resp. $r_\delta = `r env_on_stab$via_richness["log_RC2"]`$ and
$r_\delta = `r env_on_stab$via_com["log_RC2"]`$, Table \@ref(tab:indir-stab)).
This was also true for average river size but effects were weak. Finally, the
effect of average temperature on temporal stability was of higher magnitude than
the effects of species richness and mean trophic level (Table
\@ref(tab:indir-stab)).

# Discussion

---
# Chapeau
---

#### Hat

Our aim was to evaluate the effects of the network structure on the total
biomass and its temporal stability in natural communities, which have been
poorly documented. To do
this we quantified interactive effects of habitat properties, species richness,
and food web structure, on the biomass and stability of fish communities, from
the ONEMA fish dataset, containing over X million individual fish samples,
across 99 locations France spanning the period 1995 to 2018.
We infered trophic
interactions networks based on body size-dependency in food diet from the
literature and prey/predator body size ratio for piscivory^[ 
We inferred trophic networks at the scale of trophic species (i.e. nodes being
body size classes) to take in account ontogenic diet shifts and that fish-fish
trophic interaction depends on body size ratio between prey and predator. On the
other side, the community metrics were defined at the species level, (i.e.
species richness, average species CV and synchrony).
].
We used SEM to
disantangle direct and indirect effects of environmental drivers, horizontal and
vertical diversity on both total biomass and biomass stability. We found that
species richness and mean trophic level had a positive effect on total
biomass. In contrast, species richness had a negative effect on temporal
stability whereas mean trophic level covaried positively.  Futhermore, we
found that the effect of species richness and mean trophic level on total
biomass and its temporal stability were not independant as species richness had
a positive effect on mean trophic level.  Finally, we found that the
magnitude of the effects of average temperature and altitude was equal or
superior to the effects of species richness and mean trophic level. Overall,
our study is unique by its level of integration, from environmental effects to
total biomass and stability, going through species richness and network
structure, and the first direct assessment of a possible joint effect of
species richness and network structure.

## Species richness increased total biomass but decreased its temporal stability 

#### Species and total biomass

We found that species richness increased total biomass as found in salt marshes,
grasslands and
forests [@hector_plant_1999; @tilman_biodiversity_2014; @wu_relationship_2015;
@li_relationship_2018]. The positive effect of species richness on total biomass
might be due to resource use complementarity, which is held by niche
differentiation and interspecific facilitation [@loreau_biodiversity_1998;
@loreau_partitioning_2001; @cardinale_species_2002] or might be due to positive
select effect which takes place through the dominance of the
most productive species [@tilman_plant_1997; @loreau_partitioning_2001].
Previous research seems to indicate that resource complementarity might be the
main driver in fish communities [@carey_determining_2011].

Surprisingly found a negative relationship between temporal stability and
species richness. Overall, it contrasts with experimental studies in
grasslands [@tilman_biodiversity_2006]; mesocosms [@pennekamp_biodiversity_2018]
and even in natural communities [@olivier_independent_nodate] where positive
relationships are typically found between temporal stability and species
richness. In streams as well, @franssen_annual_2011 found that species richness
increased temporal stability. However other studies found a opposite relationship
in natural grassland [@yang_effects_2011] or a marginal one
[@declerck_species_2006] in natural forests. Further investigations are needed
to identify the mechanisms behind those contrasting patterns. A first step is to
look at the effects of species richness on synchrony and $\overline{CV_{sp}}$,
which constitute the two components of temporal stability quantified as CV
[@loreau_species_2008; @thibaut_understanding_2013].

The negative effect of species richness on synchrony, thereby increasing
stability, was expected. Whereas the positive effect of species richness on
$\overline{CV_{sp}}$, thereby decreasing stability, was more intriguing. Species
richness can reduce synchrony through decrease of population size, thus
raising the role of demographic stochasticity [@loreau_species_2008] but also in
the case where species have different responses to environmental variation
[@loreau_species_2008]. Two empirical studies found ... that mechanisms behind
synchrony was ...

However a negative effect of species richness on
both population ($\overline{CV_{sp}}$) and community stability can arise the
biomass distribution across population is strongly uneven and that the biomass
variance of population increases much faster than its mean
[@thibaut_understanding_2013].

In turn, we found that synchrony and $\overline{CV_{sp}}$ both decreased biomass
stability, as predicted by the formulation of stability based on the CV
[@thibaut_understanding_2013]. However, it was unexpected that the average
population $\overline{CV_{sp}}$ had a stronger negative effect on biomass
stability than synchrony [@bluthgen_land_2016; @olivier_independent_nodate]. We
can advance two hypothesis that can raise this effect. First, the opportunity
for diet differentiation can be low in streams compare to other organisms.
Secondly, in trophic communities, species directly affect each other through
feeding interactions, and so could raise synchrony between species
[@raimondo_interspecific_2004] more than in systems where interactions happen
more in the form of competitive exploitation.

- But @thebault_relationship_2006 with the same mecanisms on vertical and
  horizontal diversity

## Vertical diversity increased total biomass and its temporal stability

The mean trophic level was positively linked to total biomass. This result is
straightforward. As feeding interactions were partly determined by body size and
that body mass increase with body size, it is expected that the more the average
biomass is located at higher trophic level, the more the total biomass
increase. A mechanism, suggested by experimental and theoretical work, can
be that a higher trophic level is the result of a stronger top-down effect,
meaning higher predation rates and biomass fluxes to higher trophic levels
[@thebault_relationship_2006; @kratina_warming_2012], hence leading to an
increase in total biomass with vertical diversity. Furthermore,
@wang_biodiversity_2016 have shown that total nutrient uptake might increases
with the length of trophic chain and so results in higher total biomass. 
In contrast, connectance had no effect on total biomass. One might have expected
that an increase in connectance should translate in higher resource transfer
efficiency between prey and predators and so results in higher total biomass in
the fish compartment. A reason for such an absence of an effect might be the
little resolution that we have about interactions in non fish compartment (Fig.
\@ref(fig:methods) C, D). A consequence can be that our connectance measurement
contains few too informations.

mean trophic level had a positive effect on biomass stability by its negative
effect on CVsp (i.e. positive effect on average species stability). It means
that species at higher trophic level are more stable than the species at lower
trophic levels. @shanafelt_david_w._stability_nodate and @barbier_pyramids_2019
found the same pattern with pure trophic chain models. They have shown that
strong top-down control can generate this pattern but it is not
clear if this theoretical prediction holds when considering omnivorous species
(i.e not a pure food chain) [@wang_biodiversity_2016] and if other mechanisms
can generate the same pattern [@thibaut_understanding_2013].
Another explanation is that the fishes at higher trophic levels are not more
stable themselves, but rather allow for stronger top-down control and resource
complementarity and thus reduce biomass fluctuations [@rooney_structural_2006;
@neutel_reconciling_2007]. However, the ontogenic nature of the trophic
networks complicate the interpretation from the network to population
perspective. Over its life span, a given fish will change of diet and thus move
upward in the trophic chain. The dynamic of a given species composed
of several trophic species can thus be a mix of the dynamics of several trophic
levels, plus the oscillatory dynamics of the cohorts [@townsend_population_1989;
@medvinsky_modelling_2015]. Then, there is a clear need for a better
understanding of how the dynamics of pure food chain models would be affected by
inclusion of omnivory and ontogeny.

We found that connectance had no effect on temporal stability. This result
contradicts precedent theoretical studies on the relationship between stability
and network structure [@angelis_stability_1975; @may_will_1972;
@thebault_stability_2010], although they considered different stability concepts
and metrics [@arnoldi_resilience_2016]. Once again, it is possible that
that connectance from our networks contains too few information. Furthermore, a
crucial missing ingredient to go further is the interaction strength. Indeed,
@may_will_1972 has demonstrated theoretically the fundamental interplay between
connectance, species richness and average interaction strength
[@angelis_stability_1975; @dunne_network_2006].An alternative explanation can be
that connectance increases inhomogeneously in the food web, for instance a
higher connectance in lower trophic levels will not have the stabilising effects
conferred by higher predation and omnivory in higher trophic levels. Further
investigations on this effect is needed. 


## Horizontal and vertical diversity had common, opposite and dependent effects on total biomass and its temporal stability 

We found that species richness had a positive and a negative effect on
respectively total biomass and its temporal stability whereas average trophic
level had a positive effect on both. It confirms that more investigation is
needed to understand the mechanisms leading to common and opposite effects of
horizontal and vertical diversity. We found that connectance covaries
negatively with species richness [@winemiller_must_1989; @dunne_network_2006;
@thebault_stability_2010], connectance had itself no effects on both total
biomass and its temporal stability. On the other side, we found species richness
was negatively related to mean trophic level and mean trophic level
covariated positively with total biomass and its temporal stability. Hence,
horizontal diversity had a direct positive and negative effect respectively on
total biomass and its stability but a negative and positive effect through
vertical diversity.  Theoretical work have shown that species richness can be
linked to allocation of biomass toward higher trophic level
[@thebault_relationship_2006; @schneider_animal_2016; @wang_biodiversity_2016].
It indicates the importance to consider both horizontal, vertical diversity and
their dependence. Moreover, it calls for further investigations on how species
diversity variation translates in network structure.


@thibaut_understanding_2013 have theoretically shown that a highly positive
relationship between species variance and mean together with a positive
relationship between mean species abundance (i.e. dominance) and species
richness should drive to a negative temporal stability-species richness
relationship. @thebault_relationship_2006 have also shown in a bi-trophic
foodweb that a negative temporal stability-species richness appears in case of a
plant species is highly dominant through low consumption by consumers but in the
same time highly variable because of low competitive ability. Then, common
mechanisms might be at play for both horizontal and vertical diversity while
having same or opposite effects on total biomass and its temporal stability.
Overall our results confirm that more investigation is needed to understand the
mechanisms leading to common and opposite effects of horizontal and vertical
diversity.

## Environment had an high effect on total biomass and its temporal stability 

We find that environmental drivers overall affect total biomass indirectly,
through changes in vertical and horizontal diversity. This contrasts with
research in plant communities that showed that total biomass was primarily
driven by environmental factors [@grace_integrative_2016], and in particular by
warming, which has contrasted effects on biomass in aquatic communities
[@yvondurocher_warming_2011; @dossena_warming_2012]. Average temperature,
inverse altitude, and average stream size had indirect positive effects on total
biomass, through a positive direct effect on species richness. These effects are
well known in freshwater communities and are explained by a gain in species
along thermal gradients, from smaller and colder streams, which support small
food webs dominated by salmonids [@ogorman_chapter_2012; @emmrich_geographical_2014],
to wider and warmer sections of river networks, which contain larger food webs
dominated by mesotrophic preators such as percids [@allan_stream_2007;
@emmrich_geographical_2014]. Further in line with this pattern, we find that average stream
size had a positive effect on total biomass through
a positive effect on mean trophic level, consistent with the fact that food
webs in wider streams, with a greater amount of running waters, are also larger,
and hence support more species and biomass [@allan_stream_2007]. Greater ecosystem
size might be linked to a greater diversity of resources through habitat
heterogeneity, on so higher species richness and total biomass by surface unit,
through resource complementarity. Greater diversity of resources might also
allow to maintain higher biomass in high trophic level [@post_ecosystem_2000;
@doi_resource_2009]. Overall, our results indicate that environmental effects on
total biomass operate primarily through changes in community structure.
Furthermore, the positive effect of temperature on total biomass was of the
magnitude of effects of horizontal and vertical diversity, and thereby of
changes in community structure. This adds to the mounting body of work reporting
important effects of temperature on the structure and biomass of aquatic system
[e.g. @dossena_warming_2012; @edeline_ecological_2013;
@emmrich_geographical_2014; @hattab_forecasting_2016].

Interestingly, stream flow and size, inverse altitude, and temperature had
indirect effects on stability through two conflicting pathways, either
stabilising, involving vertical diversity, or destabilising, involving
horizontal diversity. The first pathway consists in a positive effect of
temperature and stream properties on mean trophic level, in line with the idea
that wider streams and warmer conditions are favourable to mesotrophic predators
[@allan_stream_2007; @emmrich_geographical_2014], which in turn stabilises
biomass fluctuations, possibly due to increased top-down regulation (as
discussed above). The second pathway consists in a positive effect of
temperature and stream properties (width, flow, inverse altitude) on species
richness, which itself has a destabilising effect (see discussion on horizontal
diversity). This result is interesting in that though both pathways had not been
evidenced to be at jointly play, as far as we know. Furthermore, it is unclear
as to which pathway is dominating, and under which circumstance, opening an
interesting avenue for further investigations. Overall our study highlights
that environmental factors should not be ignored in natural communities studies
and that its effects can be mainly indirect and in this case, path analysis
should more relevant than bivariate relationships
[@grace_causal_2014; @grace_integrative_2016].

# Conclusion and perspectives 

We aimed to assess the effect of horizontal & vertical diversity on empirical
trophic communities. While theoretical ecology has focused on the effects of
network structure on stability, empirical ecology has focused on species richness
and ignored network structure. Furthermore, both fields have largely used
different stability metrics. We showed that horizontal and vertical diversity
can have independent and sometimes opposite effects on total biomass and its
temporal stability. It opens a promising way for the understanding on how
species interactions, of different types, can affect both synchrony and CVsp in
different ecosystems. The reconstruction of ecological networks based on trait
can be a first approach to document such relationships, however it will not
compensate for close evaluation of measured interaction strength. We also
believe that SEM methods are particularly helpful to assess complex relationship
between environment, community structure and ecosystem properties in empirical
data which necessitate to move from simple bivariate relationships
[@grace_integrative_2016]. We believe that the integration of network structure
and species interaction will improve our understanding of the mechanisms driving
ecosystem properties.


```{r}
save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
```

# References
