---
title: Species richness and food-web structure jointly drive community biomass and its temporal stability in fish assemblages 
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault, Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    toc: false 
    fig_caption: true 
    keep_tex: true
  word_document:
fontsize: 12pt
header-includes:
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
csl: ecology-letters.csl
---

```{r, echo = FALSE, results = FALSE, message = FALSE}
mypath <- rprojroot::find_package_root_file
data_common <- mypath("data")
dest_dir <- mypath("data", "species")

knitr::opts_chunk$set(
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = FALSE 
)

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

theme_set(theme_alain())
```

```{r, results = FALSE}
knitr::opts_chunk$set(
  results = TRUE 
)
```

- Author affiliation:
  - Alain Danet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Maud Mouchet: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France
  - Willem Bonnaffé: Ecological and Evolutionary Dynamics Lab. Zoology Research
    and Administration Building, 11a Mansfield Rd, Oxford OX1 3SZ, United
    Kingdom.
  - Elisa Thébault: Sorbonne Université, CNRS, IRD, INRAE, Université Paris Est
    Créteil, Institute of Ecology and Environmental Sciences of Paris
    (iEES-Paris), Paris, France  
  - Colin Fontaine: Centre d’Ecologie et des Sciences de la Conservation, UMR 7204
    MNHN-CNRS-Sorbonne Université, Muséum national d’Histoire naturelle de
    Paris, 43 rue Buffon, 75005 Paris, France

- Author contributions: AD, CF, MM and ET designed the study. WB designed the
  network inference method and collected the food diet data. AD performed the
  data analysis and wrote the first draft of the manuscript. All authors
  contributed substantially to revisions.

- Data accessibility statement: Upon acceptance of the paper, we confirmed that
  the data supporting the results will be archived in an appropriate public
  repository and that the data DOI will be included at the
  end of the article. The code used for the analysis and to generate the
  manuscript is available on github: (alaindanet/fishcom.git). The raw fish
  database is public and available upon request to eddy.cosson@afbiodiversite.fr and
  thierry.point@afbiodiversite.fr. The raw data of water temperature, flow and
  Biological Oxygen Demand are available on http://www.naiades.eaufrance.fr/. 

- Article type: Letters

- Running title: food-web structure, biomass and stability

- Number of words:
  - Abstract: 149
  - Main text: 4930 

- Number of references: 92
- Number of figures: 3
- Number of tables: 1
- Number of text boxes: 0 

- Coresponding author:
  - Alain Danet
  - UMR 7204 CESCO, CP 135; 43, rue Buffon, 75005 Paris, France
  - alain.danet@mnhn.fr 
  - +33140798134

# Abstract

Biodiversity-ecosystem functioning (BEF) and food-web complexity-stability
relationships are central to ecology. However, they remain largely untested in
natural context. Here we quantify the links among environmental conditions,
richness, food-web structure, annual biomass and its temporal stability using a
standardized monitoring dataset of 99 stream fish communities spanning from 1995
to 2018. We first reveal that both richness and average trophic level are
positively related to annual biomass, with effects of similar strength. Second,
we show that mean trophic level decrease population variability thereby
increasing community stability, and contrary to expectation, a destabilizing
effect of species richness. Finally, we find that environmental conditions
affect both biomass and its stability via effects on richness and network
structure. Strikingly, the variation of stability are mediated by population
stability rather than synchrony, which contrasts with results from
single-trophic communities and might be characteristic of multi-trophic
communities.

# Introduction 

---
#### Biodiversity and ecosystem properties 
---

Current biodiversity losses and further global change have the potential to
affect ecosystems in complex ways [@loreau_biodiversity_2001;
@tilman_biodiversity_2014]. Biodiversity has indeed a major effect on
ecosystem functions and their stability in response to perturbations
[@hector_plant_1999; @loreau_biodiversity_2001; @hooper_effects_2005;
@dunne_network_2006; @duffy_why_2009]. Understanding the relationship
between biodiversity and ecosystem properties is thus crucial to better
anticipate the impacts of global change. 

---
#### Species richness increases total biomass
---


Species richness has been found to increase primary productivity, community
biomass and its temporal stability in a diversity of ecosystems and taxa both
empirically and experimentally [@tilman_productivity_1996;
@cardinale_species_2002; @tilman_biodiversity_2006; @franssen_annual_2011;
@grace_integrative_2016; @pennekamp_biodiversity_2018; @houlahan_negative_2018;
@olivier_urbanization_2020].  However, these studies mainly focused on
communities composed of a single trophic level, generally primary producers,
thereby ignoring potential effects of food-web structure [but see
@scherber_bottom-up_2010]. Conversely, theoretical works suggest that both
species richness and food-web structure affect ecosystem properties such as
productivity, total biomass and its stability. For example, the presence of
species at higher trophic levels may increase total primary production, through
the selection of primary producers which are larger and more complementary
[@wang_biodiversity_2018]. In communities including producers and consumers, the
connectance which measures the degree of consumer generalism is predicted to
modulate the diversity-productivity relationship [@thebault_food-web_2003;
@thebault_cascading_2007]. Similarly, theoretical studies generally show strong
links between food-web structure and stability [e.g.  @may_will_1972;
@dunne_network_2006; @neutel_reconciling_2007; @duffy_why_2009;
@stouffer_compartmentalization_2011].  Overall, the evidences from theoretical
model suggests that both species richness and food-web structure should affect
community biomass and stability, but empirical evidences of the effects of
network structure on community biomass and stability are lacking.

While community stability can be measured in many ways in theoretical studies,
most empirical studies measure community stability as the inverse of the
coefficient of variation of community productivity, biomass or abundance, also
called temporal stability [@kefi_advancing_2019]. This stability metric is also
well grounded in theory [e.g. @thebault_trophic_2005; @loreau_species_2008;
@thibaut_understanding_2013] and can be decomposed into two components:
population stability and synchrony [@thibaut_understanding_2013].  Studies
considering a single trophic level [@yachi_biodiversity_1999;
@tilman_biodiversity_2006; @loreau_species_2008; @olivier_urbanization_2020] as
well as theoretical prediction for multitrophic communities
[@thebault_trophic_2005] tend to highlight that asynchrony in population
dynamics as key for the stabilizing effects of species richness on community
biomass. Theory also predicts that higher food-web connectance can
counterbalance the positive effect of species richness on the temporal stability
of community biomass, because it may increase interaction strength and
thereby increases population variability, leading to a negative relationship
between species richness and the temporal stability of populations
[@thebault_trophic_2005]. Predators can also have cascading effects on both
population variability and synchrony at lower trophic levels
[@teng_dynamics_2004; @shanafelt_stability_2018]. Overall, these theoretical
studies show that the effects of species richness and food-web structure, such
as connectance and average trophic level, are potentially conflicting or
synergistic in such a way that they need to be addressed jointly.

The joint study of the effects of species richness and food-web structure on total
biomass and its stability is even more important in the context of environmental
changes. Recent studies comparing natural communities have shown that
environmental characteristics determine in part community biomass
[@grace_integrative_2016; @woods_testing_2020] and its temporal stability
[@franssen_annual_2011; @hansen_climate_2013; @bluthgen_land_2016;
@de_boeck_patterns_2017; @friedpetersen_drivers_2020]. The environment can
affect ecosystem function or stability directly. For example, larger freshwater ecosystems
tend to have more available resources and thus community biomass
[@post_ecosystem_2000; @doi_resource_2009] while agricultural intensification
destabilizes bird communities by decreasing population stability
[@olivier_urbanization_2020]. The effects of environment can also go through
effects on species richness and food-web structure, as larger ecosystems host
food-webs with higher diversity and trophic levels [@mchugh_dual_2010] whereas
temperature can affect food-web diversity and structure in contrasted ways
depending on the ecosystem studied [@ogorman_unexpected_2017;
@gauzens_biodiversity_2020]. Environmental characteristics have thus to be
accounted for if we are to tease apart the effects of species richness and
foodweb structure on community biomass and its temporal stability.


---
#### Stream fish communities is a good model to study effects of horizontal & vertical diversity
---

Stream fish communities constitute a good model to study the effects of network
structure on total biomass and its temporal stability because their trophic
interactions are well known,. A substantial body of literature supports that
trophic interactions can be inferred through body size and diet informations
[@jennings_weak_2001; @beckerman_foraging_2006; @gravel_inferring_2013;
@brose_predator_2019; @portalier_mechanics_2019]. Using long-term monitoring of
stream fish communities [@edeline_ecological_2013], we propose one of the first
attempts to test empirically the theoretical expectations on the
diversity-stability relationships according for community, trophic complexity
and environmental characteristics.


# Methods

```{r, fig.show = "hide"}
myload(
  hab_analysis,
  temporal_station_desc,
  temporal_press_polluants,
  geo_station,
  dir = mypath("data")
)
habitat_press <- build_habitat_pressure_dataset(
  .habitat_analysis = hab_analysis,
  .tmp_press = temporal_press_polluants,
  .tmp_st_desc = temporal_station_desc,
  .geo_st = geo_station 
)

# Make PCA 
habitat_press %<>% na.omit()
mask <- names(habitat_press) %in% names(get_pca_var_name_replacement())

pca_rotated <- compute_rotated_pca(
  .data = habitat_press[, mask],
  naxis = 2
)
habitat_pressure <- 
  cbind(habitat_press[, c("station", "temperature_med", "alt")], pca_rotated$rotated$score) %>%
  as_tibble

mysave(habitat_press, habitat_pressure, dir = mypath("data"), overwrite = TRUE)
```

```{r}
prop_var_expl_pca <- pca_rotated$rotated$Vaccounted["Proportion Var", ] %>%
  map_dbl(., ~round(.x * 100))
tot_var_expl_pca <- sum(prop_var_expl_pca) 
```



```{r}
# Basin
st_basin <- get_basin_station(sf_obj = FALSE)

# Select fishing operation 
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
range_surface <- map_dbl(c(min, max), ~.x(op_analysis_bbb$surface, na.rm =TRUE))
range_surface[1] <- ceiling(range_surface[1] / 10) * 10
range_surface[2] <- ceiling(range_surface[2] / 100) * 100
# quantile(op_analysis_bbb$surface, na.rm =TRUE)
```

## Data preparation and filtering

Fish communities were monitored across stream sections in France on the period
1995-2018 by the French Office of Water and Aquatic Ecosystems (ONEMA) using
electrofishing. Two different standardized protocols were used for small and
large streams (detailed in appendix B, part 1.1). In the case where a stream was
sampled alternatively with one of the two sampling protocols, we only included
data derived from the most frequently used sampling method. The sampling season
spanned from late spring to autumn.  There was low heterogeneity of the sampling
month within stations, with the median sampling month being mid-August where the
median standard deviation of the sampling month was $0.7$ month, i.e. three weeks.

We selected the stations that had been sampled ten years or more. As the concept
of community stability often refersred to the variability around an equilibrium
point [@donohue_navigating_2016], which is rarely observed or difficult to
characterize in natural communities. Then, we selected the stations that did not
show temporal trends in community biomass (detailed in appendix B, part 2).
However, the results were robust to the relaxation of this hypothesis (Fig. S7).
We selected the stations that had been sampled ten years or more. As the concept
of community stability referred to variability around an equilibrium, which is
rarely observed or difficult to characterize in natural communities, only those
stations that did not show temporal trends in community biomass were selected
(detailed in appendix B, part 2). However, the results were robust to the
relaxation of this hypothesis (Fig. S7). These selection steps resulted in 99
stations distributed over seven hydrographic basins (Fig. \@ref(fig:matmet)A).

## Community biomass and its temporal stability

### Biomass estimation

The body size of all fish individuals from a given species was not recorded when they were too
numerous (Fig. S1, appendix B, part 1.1). The body size of the unmeasured
individuals was inferred under the assumption that species body size followed a
normal distribution (Fig. S1, appendix B, part 1.2). The body mass of each
individual was then estimated following the results of two meta-analyses on
fishes [@lleonart_removing_2000; @froese_cube_2006], using an allometric law
$B_i = 0.01 \times l_i^{3.03}$, with $B$ the body mass in grams, $l$ the body
size in millimeters and $i$ the individual. Population biomass and community biomass at
each sampling event were then calculated by summing individual body masses. To
account for the variation in sampling effort among sites, population biomass and
community biomass were corrected by the surface sampled (range `r range_surface[1]` -
`r range_surface[2]` square metres), and expressed in grams per square meter
($gm^{-2}$). In the analysis, the community biomass of a site was defined as
the median of the community biomass across sampling years.


### Stability measures

Temporal biomass stability was defined as the inverse of biomass variability.
Variability was computed as Coefficient of Variation (CV) of the community biomass over
time ($CV_i = \sigma_i \mu_i^{-1}$, with $\sigma_i$ and $\mu_i$ being
respectively the standard deviation and the temporal average of the annual
community biomass of the station $i$). Then, temporal stability ($S_i$) was
equal to $CV_i^{-1} = \mu_i \sigma_i^{-1}$.

The variability of community biomass ($CV_{com, i}$) can be decomposed 
into a
synchrony ($\phi$) component and a weighted average population variability
($\overline{CV_{sp, i}}$) component according to @thibaut_understanding_2013:

\begin{equation} 
  CV_{com, i} = \overline{CV_{sp, i}} \times \sqrt{\phi_i}
  (\#eq:cvcom)
\end{equation}

To assess the mechanisms driving stability of community biomass, we thus in addition measure
the synchrony and the weighted average population variability $\overline{CV_{sp,
i}}$, the average CV at the species-level in the station $i$, weighted by the
relative biomass of the species, $B_{k,i}$.

Synchrony of the station $i$, $\phi_i$, is the ratio between the variance of
community biomass over time ($\sigma^2_{x_{T,i}}$) and the sum of the variance of
population biomass over time ($\sigma_{x_{k,i}}$), $i$ being the station $i$ and $k$
the species $k$ [@loreau_species_2008].

\begin{equation} 
\overline{CV_{sp, i}} = \sum_k{\frac{B_{k,i} {CV}_{k, i}}{\sum_k{B_{k,i}}}}
(\#eq:cvsp)
\end{equation} 

\begin{equation} 
\phi_i = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sqrt{\sigma^2_{x_{k,i}}}})^2} = \frac{\sigma^2_{x_{T,i}}}{(\sum_k{\sigma_{x_{k,i}}})^2}
(\#eq:phi)
\end{equation} 


## Species richness and food-web structure

### Species richness

Species richness in a given site was defined as the total number of species present across
all the sampling events. We controlled species richness for sampling effort by
dividing the total number of species by the total surface sampled in the given
station. Species richness was then expressed in number of species per square
meter sampled.

### Network inference 

```{r}
myload(metaweb_analysis, dir= mypath("data"))
myload(trophic_class, dir= mypath("data", "classes"))
meta <- metaweb_analysis
#metaweb_analysis$resource
#meta$metaweb[meta$resource, meta$resource]
```

We determined the network structure in two steps: (1) build a metaweb describing the
trophic interactions between fishes and the resources (Fig.
SXX), then (2) determine network of a given community by
extracting the metaweb according to the fishes present at a given
site and sampling event (Fig. \@ref(fig:matmet)C and D).

The trophic interaction network was inferred from body size and ontogenic diet
shift following previous studies [@edeline_ecological_2013;
@gravel_inferring_2013; @poisot_structure_2016; @brose_predator_2019]. The diet
of stream fishes, as for many organisms, shifts throughout an individual's life,
and thereby with body size. For example, larvae and small juveniles feed on
plankton while adults may feed on algae and fishes, with bigger individuals
eating bigger fishes. Each fish species was divided in nine body size
classes, each corresponding to a trophic species (appendix B, Fig. S2). A
trophic species constitutes a group of individuals from the same species and
size class, which are expected to share the same sets of prey and predators.
Additionally to the trophic species, we added seven resource nodes present in
the ontogenic food diet database: detritus, biofilm, phytoplankton, zooplankton,
macrophages, phytobenthos and zoobenthos (grey nodes in Fig. \@ref(fig:matmet)C
& D). The trophic species and the resources constituted the 412 nodes of the
metaweb, i.e. 45 fish species divided into nine body size classes plus seven
resource nodes. The inference of trophic interactions was shown to be more
accurate when considering body size classes, i.e. trophic species, than species
[@jennings_weak_2001].

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. The ontogenic fish diet
database was filled according to fishbase and literature (appendix A, Table S2). Each
fish species had two or three life stages which are delimited by its body size
range (appendix B, Fig. S2). The life stage of a fish trophic species was determined by 
the center of its body size range, hereafter midpoint (appendix B, Fig. S2).

For a piscivorous trophic species, the fish-fish trophic links were defined in
two steps and based on the body size ratio between predators and prey. First of
all, the predation window of a piscivorous trophic species was defined as 3% to
45% of its midpoint [@mittelbach_ontogeny_1998; @claessen_impact_2002;
@hart_handbook_2008]. Then, a trophic link was set between the piscivorous
trophic species and every trophic species whose midpoint in bodysize range was
included in the predation window (appendix B, Fig. S2). The fish-resource trophic links were
set between the trophic species and the resources nodes according the food items
of their size class.  Lastly, the trophic links among resource nodes were set
according to the literature [@allan_stream_2007; @hart_handbook_2008].

### Network structure

For each food-web, corresponding to a particular site and year, we computed the
connectance and mean trophic level. Connectance describes the level of
generalism in the network and is calculated as the actual number of interactions
divided by the number of interactions if all species interact ($C = L / N^2$, L
and N being resp. the number of links and of nodes).  The trophic level of the
nodes was computed as one added to the average trophic level of its food item.
The average trophic level $\overline{T}$ was computed as the average trophic
level of the trophic species weighted by their biomass (excluding resource nodes
for which we had no biomass information), so $\overline{T} = \sum_i^N{B_iT_i
\times (\sum_i^N{B_i})^{-1}}$, with $T_i$ and $B_i$ being respectively the
trophic level and the biomass of the node $i$. For each site, the median of
connectance and average trophic level over time was used in subsequent analysis
(Fig. \@ref(fig:matmet)C & D).


```{r, message = FALSE, results = FALSE}
# Com
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb,
 type_network_metrics = "classes"
)
# Compute sem dataset
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync_std"]],
  nmds = NULL,
  basin = st_basin
  )
mysave(sem_data, dir = mypath("data"), overwrite = TRUE)
```


## Environmental variables

We characterised the sites by their altitude, slope, distance from
source, stream width, depth and strahler order, i.e. its position in the
stream network hierarchy. We obtained data on water temperature, flow and Biological Oxygen
Demand (BOD) from the naiades
database
[(www.naiades.eaufrance.fr)](http://www.naiades.eaufrance.fr/). As data from naiades are
not collected on the same site as our fish sampling sites, we performed an
interpolation of the water temperature and flow based on the spatial stream
network models [@isaak_applications_2014; @hoef_ssn:_2014]. The interpolation procedure
is detailed in appendix B (part 1.4).

We had one environmental variable value for each sampling event, except
for water temperature for which the record began in 2006. Then, we computed the
average and temporal CV values of water temperature, flow, BOD, river width and
depth. As habitat and environmental variables are often collinear, a principal
component analysis (PCA) was performed on the 14 scaled variables. We kept in
the analysis the two first principal components based on the elbow method, on
the eigenvalues distribution (appendix B, Fig. SXX). The two first principal components
explained `r tot_var_expl_pca`% of the variance (Fig. \@ref(fig:matmet)B). A varimax axis rotation was
performed to maximize the representation of the environmental variables by the principal
components [@kaiser_varimax_1958; @revelle_psych_2019]. The first axis
represented a gradient from small to big streams, characterized by their width
and depth, but also a gradient from stream close to far from the source. We
reversed the values of the second axis, such as it represented a gradient of
increasing average water temperature, average BOD and decreasing altitude and slope.
Further description of the variables are provided in appendix B (part 1.4).

## Statistical analysis 

We analyzed the relationships among environment, species richness, food-web
structure, community biomass and its temporal stability with structural equation
models as they enable the assessment of potential indirect and direct causal
relationships among multiple variables [@grace_structural_2008;
@grace_causal_2014; @lefcheck_piecewisesem_2016; @grace_integrative_2016].  We
defined a structural equation model explaining the median annual community
biomass as a function of the two synthetic environmental variables, species
richness and food-web structure [@maureaud_biodiversityecosystem_2019;
@woods_testing_2020]. We assumed that both species richness and food-web
structure directly affect community biomass (Fig. \@ref(fig:sem-bm)A) and that
species richness affected food-web structure [@winemiller_must_1989;
@dunne_network_2006; @thebault_stability_2010].  

We used the same model structure to assess the drivers of temporal stability
of community biomass (Fig.  \@ref(fig:sem-stab)A). Instead of the
annual community biomass, we modelled the synchrony and $\overline{CV_{sp}}$ which
in turn determined the temporal stability of community biomass. We linearized
the mathematical relationship linking temporal stability to $\overline{CV_{sp,
i}}$ and $\phi$ by taking the log of
temporal stability such as 

\begin{equation} 
    \log S_i = - \log \overline{CV_{sp, i}} - \frac{1}{2} \log \phi_i
  (\#eq:stab)
\end{equation} 

The structural equation models were based on Gaussian linear mixed-effects models. All variables
except the connectance and average trophic level
were log-transformed to fulfill model assumptions (see residual plots and data
transformation in Fig. S5 and S6, Table S5, appendix B). We set the seven
hydrographic basins as a random effect on the intercept to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6, appendix B). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). Therefore, the
standardized coefficients expressed the variation of $x$ and $y$ in standard
deviation units. According to the equation (\@ref(eq:stab)), the unstandardized
coefficients of synchrony and $\overline{CV_{sp}}$ determining temporal
stability of biomass are respectively $-0.5$ and $1.0$. When standardized, a 
comparaison of those coefficients comes down to a comparaison of the standard
deviation of these two variables. The paths whose slope had a $P$ value inferior
or equal to $0.05$ were reported in the main text, all the path values are
presented in Table S7 and S8.

Indirect effects on community biomass and its temporal stability were computed
by multiplying slopes along the path. Only significant direct slopes were
included in the calculation of indirect effects. Total effects were computed as
the sum of direct and indirect effects.

Environmental variables were interpolated with the `openStars` and `SSN`
R packages [@kattwinkel_openstars_2018; @hoef_ssn:_2014]. Linear models and SEMs
were computed with respectively the `nlme` and `piecewieseSEM` R packages
[@pinheiro_nlme_2020; @lefcheck_piecewisesem_2016]. The code used for the
analysis and to generate the manuscript are accessible on github
(alaindanet/fishcom). The analyses were performed with R version 3.6.3
[@r_core_team_r_2020].

```{r get-data}
library(piecewiseSEM)
library(lme4)
library(nlme)

#ctrl <- lmeControl(opt='optim' relative)
ctrl_lmer <- lmerControl(optCtrl = list(method = 'optimx'))
```

```{r}
# Compute SEMs
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

def_env_x_pos <- c(from = 0, to = 3)
asp <- 1.6

library(DiagrammeR)
meta_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability","figs", "meta_stab_sem"),
  format = "pdf",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE,
  inverse_y_node_pose = TRUE
)
p_stab_sem_rich <- export_diagram(
  fit = stab_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "figs", "stab_sem"),
  format = "pdf",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  inverse_y_node_pose = TRUE
)

meta_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "figs", "meta_bm_sem"),
  format = "pdf",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  metamodel = TRUE,
  inverse_y_node_pose = TRUE
)
p_bm_sem_rich <- export_diagram(
  fit = bm_sem_rich,
  file_path = mypath("manuscript", "bef_stability", "figs", "bm_sem"),
  format = "pdf",
  width = 700*2,
  height = 700*2 * asp,
  arrows = "ortho",
  val_thd = 0.05,
  env_x_pos_range = def_env_x_pos,
  env_y_pos = 0,
  env_y_sep = 1.5,
  order_env_node = c("log_RC1", "log_RC2"),
  inverse_y_node_pose = TRUE
)
```


```{r get-sem-coeff}
coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value <= 0.05)

coef_bm_sem <- coef(bm_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value <= 0.05)
```


```{r, cache = FALSE}
sem_caption <- paste0(
  "Metamodel of the Structural Equation Models for the (A) median of annual
  community biomass (in grams by square meter) and (C) its temporal stability.",
  "Results of the Structural Equation Models for
  (B) the median of annual community biomass and (D) its temporal stability. Red and black
  arrows represent respectively negative and positive path coefficients. The
  path coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA performed on environmental variables (see methods)."
)
```



```{r get-bm-sem-single-effect}
bm_sem_coef <- filter(coef_bm_sem, P.Value <= 0.05)

rich_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_rich_tot_std")
rich_on_tlvl <- get_clean_sem_coef(sem = bm_sem_coef, resp = "t_lvl", pred = "log_rich_tot_std")
rich_on_ct <- get_clean_sem_coef(sem = bm_sem_coef, resp = "ct", pred = "log_rich_tot_std")
tlvl_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "t_lvl")
ct_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "ct")
RC1_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC1")
RC2_on_bm <- get_clean_sem_coef(sem = bm_sem_coef, resp = "log_bm_std", pred = "log_RC2")
```

```{r get-bm-tot-effect-env}
bm_all_params <- get_coefficient_piecewisesem(sem = bm_sem_rich, p_val_thl = NULL)

# effect of env on bm 
env_on_bm <- get_env_on_bm(fit = bm_all_params, p_val_thl = 0.05,
  type = "std")
# rich on bm 
rich_on_bm <- get_rich_on_bm(fit = bm_all_params,
  p_val_thl = 0.05, type = "std")
# direct
ct_on_bm_trick <- list(direct = c(ct = ct_on_bm), total = c(ct = ct_on_bm))
tlvl_on_bm_trick <- list(direct = c(t_lvl = tlvl_on_bm), total = c(t_lvl = tlvl_on_bm))


tmp_bm_indir_table <- map(list(env_on_bm, rich_on_bm, ct_on_bm_trick,
    tlvl_on_bm_trick),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```

```{r}
stab_all_params <- get_coefficient_piecewisesem(sem = stab_sem_rich, p_val_thl = NULL)
# effect of env on stab
env_on_stab <- get_env_on_stab(fit = stab_all_params, p_val_thl = 0.05,
  type = "std")
rich_on_stab <- get_rich_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
ct_on_stab <- get_ct_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
tlvl_on_stab <- get_tlvl_on_stab(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")

tmp_stab_indir_table <- map(list(env_on_stab, rich_on_stab, ct_on_stab, tlvl_on_stab),
  ~as_tibble(c(.x, list(variable = names(.x[[1]]))))
  ) %>%
bind_rows()
```
```{r get-sem-single-effect}
stab_sem_coef <- filter(coef_stab_sem, P.Value < 0.05)

sync_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_sync")
cv_sp_on_stab <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_stab_std", pred = "log_cv_sp")
RC1_on_sync <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_sync", pred = "log_RC1")
tlvl_on_cv_sp <- get_clean_sem_coef(sem = stab_sem_coef, resp = "log_cv_sp", pred = "t_lvl")
```

```{r get-sem-tot-effect-env}
# effect of env on sync and cv_sp
env_on_sync <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
env_on_cv_sp <- get_env_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
# env on stab via network 
env_on_t_lvl <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "t_lvl", type = "std")
env_on_ct <- get_env_on_com(fit = stab_all_params,
  p_val_thl = 0.05,
  com = "ct", type = "std")
env_on_richness <- get_env_on_rich(fit = stab_all_params,
  p_val_thl = 0.05, type = "std")
```


# Results

The structural equation models explained a large part of the variation
of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
trophic level ($R^2 = .11$, Fig. \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A). We found a
negative relationship between species richness and mean trophic level ($r_\delta
= `r rich_on_tlvl`$, $r_\delta$ meaning standardized slope) and connectance
($r_\delta = `r rich_on_ct`$, Fig.  \@ref(fig:sem-bm)A and \@ref(fig:sem-stab)A), meaning that a
part of the effects of species richness on community biomass and its temporal
stability went through food-web structure.

## Species richness and average trophic level are positively correlated with community biomass

```{r get-sem-tot-effect-rich}
rich_on_sync <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_sync", type = "std")
rich_on_cv_sp <- get_rich_on_stab_comp(fit = stab_all_params,
  p_val_thl = 0.05,
  stab_comp = "log_cv_sp", type = "std")
```

Species richness and mean trophic level had a significant positive direct effect
on community biomass ($r_\delta = `r rich_on_bm$direct`$ and 
$r_\delta = `r tlvl_on_bm`$ resp., Fig. \@ref(fig:sem-bm)A, B, C, Table
\@ref(tab:indir-sem)), while connectance had no direct effect.

The two PCA axes synthesising environmental variables had no significant direct
effects on community biomass, but indirect (Table \@ref(tab:indir-sem)). The first
axis, related to the stream size, was positively linked to community biomass
($r_\delta = `r env_on_bm$total["log_RC1"]`$, Table \@ref(tab:indir-sem)),
through both species richness and mean trophic level ($r_\delta = 
`r env_on_bm$via_richness["log_RC1"]`$ and $`r env_on_bm$via_tlvl["log_RC1"]`$
resp., Fig. \@ref(fig:sem-bm) F, G, Table \@ref(tab:indir-sem)). The second axis, related to the average
annual temperature was positively related
to community biomass ($r_\delta = `r env_on_bm$total["log_RC2"]`$, Table
\@ref(tab:indir-sem)), mainly through species richness ($r_\delta = 
`r env_on_bm$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-bm) G, Table \@ref(tab:indir-sem)). Streams
with higher temperature and BOD contained more species, indirectly increasing
community biomass. The total effect of PCA1, PCA2 and species richness on
community biomass were of the same magnitude.


## Temporal stability of annual community biomass

By its effects on synchrony and population variability ($\overline{CV_{sp}}$),
species richness had a negative total effect on biomass stability ($r_\delta =
`r rich_on_stab$total`$, Table \@ref(tab:indir-sem)). This effect resulted from
two opposite effects. On the one hand, species richness had a direct negative
effect on synchrony ($r_\delta = `r rich_on_sync$direct`$, Fig.
\@ref(fig:sem-stab) A, B), thereby increasing stability ($r_\delta = 
`r rich_on_stab$via_sync`$). On the other hand, species richness had a positive
direct effect on $\overline{CV_{sp}}$ ($r_\delta = `r rich_on_cv_sp$direct`$,
Fig. \@ref(fig:sem-stab) A, C), thereby decreasing biomass stability ($r_\delta
= `r rich_on_stab$via_cv_sp`$, Table \@ref(tab:indir-sem)), which outweighted
the decreasing effect of species richness on synchrony. The negative effect of
$\overline{CV_{sp}}$ on temporal stability was twice higher than the negative
effect of synchrony (resp.  $r_\delta = `r cv_sp_on_stab`$ and $r_\delta = 
`r sync_on_stab`$, Fig.  \@ref(fig:sem-stab)A). Population variability and
synchrony constitute a mathematical decompositon of the stability, contributing
respectively to 1 and 0.5 respectively (Eq. \@ref{eq:stab}), meaning that their
$r_\delta$ difference to temporal stability is due to their standard deviation,
and so that the standard deviation of $\overline{CV_{sp}}$ is of the same
magnitude than the one of synchrony.

The total effect of mean trophic level and species richness on temporal
stability of biomass were of the same magnitude (resp.  
$`r tlvl_on_stab$total["t_lvl"]`$ and $`r rich_on_stab$total`$, Table
\@ref(tab:indir-sem)).  The mean trophic level had only a direct negative effect
on $\overline{CV_{sp}}$ ($r_\delta = `r tlvl_on_cv_sp`$, Fig.
\@ref(fig:sem-stab)A, F) and thereby had a total positive effect on temporal
stability ($r_\delta = `r tlvl_on_stab$via_cv_sp["t_lvl"]`$, Table
\@ref(tab:indir-sem)). Food webs in which community biomass is located on
average at higher trophic levels thus tend to have higher population and
community stability. Connectance had no significant direct effect on either
$\overline{CV_{sp}}$ nor synchrony and thus no effect on temporal stability
(Fig. \@ref(fig:sem-stab)A, Table \@ref(tab:indir-sem)).
 
The total effect of PCA2, related to average annual temperature and BOD, on
temporal stability was of higher magnitude than the effects of species richness
and mean trophic level (Table \@ref(tab:indir-sem)).  The PCA2 had a total
negative effect on temporal stability, meaning that higher temperature and BOD
results in lower stability ($r_\delta = `r env_on_stab$total["log_RC2"]`$, Table
\@ref(tab:indir-sem)).  PCA2 had an indirect positive effect on temporal
stability through a direct positive effect on mean trophic level ($r_\delta = 
`r env_on_stab$via_tlvl["log_RC2"]`$, Fig. \@ref(fig:sem-stab) I, Table
\@ref(tab:indir-sem)). However, PCA2 had a negative effect on temporal stability
through a direct positive effect on $\overline{CV_{sp}}$ and species richness
(resp.  $r_\delta = `r env_on_cv_sp$direct["log_RC2"]`$ and $r_\delta = 
`r env_on_stab$via_richness["log_RC2"]`$, Fig. \@ref(fig:sem-stab)G, Fig.
\@ref(fig:sem-bm)G, Table \@ref(tab:indir-sem)). This was
also true for the PCA1, related to stream size, with a resulting very slight
positive effect of PCA1 on temporal stability ($r_\delta = 
`r env_on_stab$total["log_RC1"]`$, Table \@ref(tab:indir-sem)).  Warmer and
larger streams thus tend to have more species and more variability in population
biomass, then have a lower stability of community biomass.

```{r, cache = FALSE}
cap_sem <- paste0(
  "Direct, indirect and total effects of environment, species richness,
  connectance and mean trophic level on community biomass
  and its temporal stability. Indirect effects are computed by multiplying the
  path coefficients from the variable predictor to the response variable.
  Indirect effects are considered as one step from the target variable. For
  exemple, the indirect effect of species richness on
  biomass stability via its effect on CVsp is $-0.62$. Only the
  significant direct effects were retained for the computation of indirect
  effects. ", "As an example, the indirect effect via species richness takes
  into account the direct effect of species richness as well as the effect of
  species richness through connectance and average trophic level. ",
 "NA values indicate that the corresponding paths do not exist in the
 specified Structural Equation Model (SEM). ", "NS: statistically non-significant."
)
```

```{r indir-stab, cache = FALSE}

full_table <- bind_rows(
  tmp_bm_indir_table,
  tmp_stab_indir_table
) %>%
mutate(`SEM type` = c(rep("Total annual biomass", 5), rep("Temporal Stability of annual biomass", 5))) %>%
select(`SEM type`, variable, direct, via_richness, via_ct, via_tlvl, via_cv_sp, via_sync, total) %>%
format_table() %>%
select(`SEM type`, everything())

full_table %<>%
  mutate(Direct = ifelse(Direct == 0, "NS", Direct)) %>%
  mutate_if(is.numeric, format, digits = 2, nsmall = 2)

library(kableExtra)
mytable <- kable(full_table,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = cap_sem
  ) %>%
kable_styling(latex_options =c("scale_down")) %>%
add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
column_spec(1:2, width = "3cm") %>%
collapse_rows(columns = 1, valign = "top")
#write(mytable, file = mypath("manuscript", "bef_stability", "table.tex"))
```


# Discussion

---
#This study is unique by its level of integration, from environmental
#effects to total biomass and its stability, going through species richness and
#food-web structure. It is the first direct assessment of a possible joint effect
#of species richness and network structure on both total biomass and its temporal
#stability. We found that species richness and mean trophic level had a positive
#effect on total biomass. In contrast, species richness had a negative effect on
#temporal stability whereas mean trophic level covaried positively. We also found
#that the effect of species richness and mean trophic level on total biomass and
#its temporal stability were not independent as species richness had a negative
#effect on mean trophic level. Furthermore, we found that connectance had no
#significant effect on both total biomass and its temporal stability. The results
#shows that temporal stability was mediated by changes in species variability 
#rather than synchrony. Finally, we found that the magnitude of the effects of
#average temperature and altitude was equal or superior to the effects of species
#richness and mean trophic level. 
---

## Species richness increased community biomass but decreased its temporal stability 

We found that species richness increased community biomass in line with the
results on plants and tree communities [@hector_plant_1999;
@tilman_biodiversity_2014; @wu_relationship_2015; @li_relationship_2018] as well
as those found for fish communities [@maureaud_biodiversityecosystem_2019;
@woods_testing_2020] and for theoretical food-web models
[@schneider_animal_2016]. Theory suggests that the positive effect of species
richness on community biomass might be held by resource use complementarity
[@carey_determining_2011], which is driven by niche differentiation
[@loreau_biodiversity_1998; @loreau_partitioning_2001] or by positive selection
effect, which is driven by the dominance of the most productive species
[@loreau_biodiversity_2001]. Recent findings suggest that dominance, a positive
selection effect [@loreau_partitioning_2001], is the main driver of the observed
positive relationship between biomass and species richnes in fish communities
[@maureaud_biodiversityecosystem_2019; @woods_testing_2020].

We found that species richness decreases synchrony, threby increasing stability.
This is in accordance with most studies on experimental grasslands
[@isbell_biodiversity_2009; @roscher_identifying_2011] and natural communities
of birds, grasslands, bats and butterflies [@bluthgen_land_2016;
@olivier_urbanization_2020]. It is thought that it is the main effect by which
species richness increases stability [but see @declerck_species_2006;
@valencia_synchrony_2020].  Our result thus extend that species richness
decreases synchrony also in multi-trophic communities.  However, theory does not
clearly state what would be the effect of food-web structure on the relationship
between species richness and synchrony [@raimondo_interspecific_2004;
@korpimaki_predatorinduced_2005; @mccann_more_2009].   

The positive effect of species richness on population variability, thereby
decreasing stability, is more intriguing. A previous meta-analysis has indeed
reported that species richness had often a negative effect on population
variability in multi-trophic communities while a positive effect is often found
in single-trophic communities [@jiang_different_2009]. In food-webs, theoretical
models predict that the relationship between the temporal stability of populations
and species richness depends on interaction strength and its distribution
[@mccann_reevaluating_1997; @thebault_trophic_2005; @downing_temporal_2020],
with stronger interactions promoting a negative relationship between species
richness and stability. Therefore, it is possible that our results are due to
strong trophic interactions, leading to more fluctuations in population biomass,
but this hypothese was not testable with the available dataset. Alternatively,
other authors suggest that this effect might be due to an increase of
demographic stochasticity with an increase of species richness [@loreau_species_2008].

A major finding of the study is that we found a negative relationship between
species richess and temporal stability, contrast with most experimental and
empirical studies to date [@franssen_annual_2011; @tilman_biodiversity_2006;
@valencia_synchrony_2020; @pennekamp_biodiversity_2018;
@olivier_urbanization_2020], but coincide with a few empirical ones
[@declerck_species_2006]. This finding means that the destabilising effect of
species richness through population variability was superior its stabilising
effect through synchrony. It can happen either because of the relative strength
of the effect species richness on both population variability and synchrony or
because of the overall variability of synchrony and population variability in
the our study system.

We found indeed that the population variability had a standardized effect
on the stability of community biomass twice stronger than synchrony, meaning that the
variability of synchrony was equivalent the one of population variability, in
contrast with a previous study which found that the variability of synchrony was
twice higher than the variability of population variability
[@olivier_urbanization_2020]. Therefore, the low variability of synchrony in our
system might be a cause for the observed negative effect of species richness on
temporal stability of community biomass despite the strong negative effect of species
richness on synchrony. Could the lower variability of synchrony be a
characteristic of multitrophic communities? Theoretical models suggest that
generalist predator can either synchronise or desynchronize the dynamics its
prey, depending on the distribution of interaction strength and competition
between preys [@raimondo_interspecific_2004; @korpimaki_predatorinduced_2005;
@mccann_more_2009]. Alternatively, it is possible that, in aquatic food-webs,
the occurrence of large oscillatory dynamics typical of predator-prey dynamics
leads to a larger variability of population variability than the one of synchrony
[@mccann_reevaluating_1997]. Another hypothese is that food-webs are
characterized by highly uneveness biomass distribution, which can decrease the
variability of synchrony, i.e. decrease the strength of the porfolio effect
[@doak_statistical_1998; @thibaut_understanding_2013].

All together, the destabilising effect of species richness on temporal stability
raises more questions than it solves and then highlight the need for more
investigations about the difference between single and multitrophic
communities in natural communities.

---
#@thibaut_understanding_2013 proposed that a
#strongly uneven biomass distribution across populations and that the biomass
#variance of population increases much faster than its mean can generate a
#positive effect of species richness on population ($\overline{CV_{sp}}$)
#stability.
---


## Average trophic level increased community biomass and its temporal stability while connectance had no effect

Our analysis further indicates that network structure, and in particular average
trophic level was strongly related to community biomass, as higher total
biomass was found in communities with an higher average trophic level. These results are
in accordance with the predictions of theoretical models [@schneider_animal_2016;
@wang_biodiversity_2018]. @wang_biodiversity_2018 proposed that this effect is driven
by predators selecting primary producers with higher resource use efficiency and predators
enhancing complementarity between primary producers, a mechanism which
drive the positive effect of horizontal diversity on productivity
[@loreau_biodiversity_2001].

In addition, our results show that communities with an higher average trophic
level had a lower population variability, and thereby were more stable. This
result is in accordance with theoretical models [@shanafelt_stability_2018;
@barbier_pyramids_2019; @mccann_diversitystability_2000] and might result from a
higher stability of populations of higher trophic levels
[@shanafelt_stability_2018; @barbier_pyramids_2019] or a damping effect of
higher trophic levels on the variability of lower trophic level populations
[@mccann_diversitystability_2000].

In contrast, we found that connectance was not related to community biomass,
which contradicts theoretical models which suggest that a greater connectance should
decrease complementarity in resource use between species, which is expected to
lower community biomass [@thebault_food-web_2003; @poisot_trophic_2013].
However, the effect of connectance on productivity has been poorly investigated.

One of the most surprising result is that we found no relationship between
connectance and stability. It contrasts with the central role that connectance
plays in the studies of the food-web complexity-stability relationship [e.g.,
@angelis_stability_1975; @may_will_1972; @thebault_stability_2010; but see
@neutel_reconciling_2007], although theoretical ecology generally considers
different stability concepts and metrics [@arnoldi_resilience_2016]. The lack of
effect of connectance on the temporal stability of community biomass might be
related to the fact that our measure of connectance does not take into account
the distribution of interaction strengths in the food-webs. Indeed, food-web
connectance is expected to have different consequences on the temporal stability
of community biomass depending on the strength of trophic interactions
[@thebault_trophic_2005], which we could not test due to the scarcity of
information on the lower compartments of the community, i.e. primary producers,
decomposers and the benthic species.

## Environment had an strong effect on community biomass and its temporal stability 

We found that the larger, warmer and more enriched streams had higher total biomass
through higher average trophic level and species richness, in line with mounting
body of work reporting important effects of temperature on the structure and
biomass of aquatic systems [@allan_stream_2007; @edeline_ecological_2013;
@emmrich_geographical_2014; @hattab_forecasting_2016; @woods_testing_2020].
Larger ecosystem in freshwater systems might provide a higher diversity
of resources through habitat heterogeneity and then result in higher species
richness and community biomass by surface unit, through complementarity in
resource use. Our result suggest that warming and enrichment might result in
higher total biomass but previous studies find contradictory results
[@yvondurocher_warming_2011; @dossena_warming_2012;
@maureaud_biodiversityecosystem_2019; @tabi_warming_2019]. One of the reason
might be that temperature has non monotonic effects on biological processes and
that temperature and enrichment can have antagonistic effects 
[@oconnor_warming_2009; @uszko_effects_2017; @tabi_warming_2019].

Our analysis revealed that stream size had only a weak effect on the temporal
stability of community biomass, while warmer and enriched streams had an higher
average population variability, thereby a lower temporal stability. Our results
are in line with previous experiments showing that warming decreases temporal
stability, however enrichment is predicted to counter the destabilising effect
of warming [@binzer_dynamics_2012; @tabi_warming_2019].  However, enrichment alone 
is predicted to increase population variability while warmer 
temperature is predicted to decrease stability through starvation resulting from high
metabolic activity [@tabi_warming_2019] but again it depends on the species thermal
niche and of the shape of the response of biological processes to warming
[@uszko_effects_2017].

---
#Interestingly, the two PCA axes related to environmental conditions had indirect
#effects on stability through two conflicting pathways, either stabilising, via
#network structure, or destabilising, via species richness. The first pathway
#consists in a positive effect of temperature and stream size on mean
#trophic level, in line with the idea that wider streams and warmer conditions
#are favourable to mesotrophic predators [@allan_stream_2007;
#@emmrich_geographical_2014], which in turn stabilises biomass fluctuations,
#possibly due to increased top-down regulation. The second pathway consists in a
#positive effect of temperature and stream size on species richness, which itself
#has a destabilising effect. This result is interesting in that both
#pathways had not been evidenced to jointly play, to the best of our knowledge.
#Furthermore, it is unclear which pathway is dominating, and under which circumstances,
#opening an interesting avenue for further investigations.
---

---
## Final thoughts about empirical food-webs

#It was unexpected that the average population $\overline{CV_{sp}}$
#had a stronger negative effect on biomass stability than synchrony
#[@bluthgen_land_2016; @olivier_urbanization_2020], and explain why we observe a
#negative effect of species on temporal stability of biomass. The lower effect of
#synchrony can be explained by the  presence of generalist predators in stream
#communities, which can raise synchrony between prey species which shares the
#same predator [@raimondo_interspecific_2004]. Uneven population biomass within
#communities also raise synchrony between species [@thibaut_understanding_2013].

#As found in other studies, we found that species richness was negatively related
#to mean trophic level and connectance [@winemiller_must_1989;
#@dunne_network_2006; @thebault_stability_2010]. Species richness had thus a
#consistent destabilising effect on temporal stability of biomass directly and
#through average trophic level, but it has a direct positive effect on total annual
#biomass directly but a negative one through the decrease of average trophic
#level. It highlights the importance to consider several aspects of
#network structure to order to improve our understanding of the drivers of
#community structure and stability.
---

## Network reconstruction: limits and perspectives 

The lack of experimental or empirical studies considering the effects of both
species richness and food-web structure on ecosystem functions can be explained
by the challenges associated with manipulating both species richness and
food-web structure  experimentally [e.g. @sander_ecological_2017] and by the
fact that describing trophic interactions between species is highly labour
intensive. These challenges are even more acute when studying the temporal
stability of ecosystem properties, which requires time series. In this context,
recent developments to predict trophic interactions among species
[@beckerman_foraging_2006; @gravel_inferring_2013; @portalier_mechanics_2019],
combined with observational long-term monitoring of ecological communities,
offer an promising opportunity. They thus offer a way to maximise the  amount of
information that we can extract from already collected empirical data, but at
the cost of their precision. Build on the ratio of body-size between predator
and prey [@gravel_inferring_2013], those methods are however in general blind to
the modulation of species interactions according to the realized niche of
species such as temperature and prey preferences. Although, the development of
more mechanistic methods incorporating predator behaviour
[@portalier_mechanics_2019] or more statistically flexible framework such as
machine learning [@pichler_machine_2020] will certainly increase the accuracy of
species interaction predictions. With the increasing availability of long-term
empirical data, we believe that methods of food-web reconstruction have a great
potential to increase our understanding of the role of network structure on
ecosystem functioning in natural settings.
 

# Conclusion

Our work contributes to bridging the gap between theoretical, experimental and
empirical findings on the functioning and stability of communities. Our study
extends the assessment of the effect of species richness on community biomass
and its temporal stability to the case of food-webs in natural settings,
providing the evidence that species richness decreases synchrony also in
multi-trophic communities. Our results highlight population variability as key
in transmitting effects of species richness, network structure and environmental
gradients on community stability. This contrast with previous results found in
single trophic communities, mostly plants, that mainly focus on synchrony and,
although further confirmation are needed, might be characteristic of animal
and/or multi-trophic communities. Further, we found that the effects of
environmental gradient related to temperature, enrichment and ecosystem size are
largely mediated by their impact on richness and average trophic level. Finally,
our study open stimulating questions about how the food-web structure and
species richness drives synchrony and population variability. 



```{r}
save.image(file = mypath("manuscript", "bef_stability", "result", "workspace.rda"))
```

# References {-}

<div id="refs"></div>

\clearpage

# Figures and Table {-}


```{=latex}
\input{table.tex}
```

\clearpage

```{r, cache = FALSE}
pca_caption <- paste0(
  "(B) Rotated axis of PCA on environmental variables. The five components
  explained, ", tot_var_expl_pca, "% of the variance (",
  paste0(names(prop_var_expl_pca), ":", prop_var_expl_pca, "%"), ").",
  " Axis 1 was positively related to the stream size, axis 2 was related to
  the stream slope and altitude and negatively related to average water temperature and
  BOD. For simplicity, we reversed the second axis of the PCA in the structural equation
  models, so that the second axis covaries with average water temperature and
  BOD."
  )

matmet_cap <- paste0( 
  "(A) Observation sites (black dots) were located across France and monitored
  on the period 1995-2018. The red dots show the location of (C) and (D) sites.
  ", " Inner borders draw the limits of the hydrographic basins. ", pca_caption,
  " (C) and (D) The temporal dynamic of population biomass with three networks
  of years 1997, 1999 and 2002. Each trophic species is represented
  by a node and each color represents a species. The node size are proportional to
  the biomass of the trophic species. The seven resource nodes are drawn in grey. ",
  "The species names corresponding to the three digit codes are found in Table
  S1.")

```

```{r matmet, cache = FALSE, fig.cap = matmet_cap, results = "fig.show", out.height="80%"}
library(knitr)
include_graphics(path = mypath("manuscript", "bef_stability", "figs", "fig1_modif.pdf"))
```

\clearpage

```{r, cache = FALSE}
sem_caption <- paste0(
  "Structural Equation Models for the median of annual
  community biomass (in grams by square meter) and (C) its temporal stability.",
  " Results of the Structural Equation Models for
  (B) the median of annual community biomass and (D) its temporal stability. Red and black
  arrows represent respectively negative and positive path coefficients. The
  path coefficients are standardized. For convenience, only significant
  paths (i.e. $P < 0.05$) are shown. Rsq: Adjusted $R^2$; Avg:
  Average, CVsp: weighted temporal CV of the population; PCA1 and PCA2: respectively the first and
  second axis of the PCA performed on environmental variables (see methods)."
)
```

```{r}

sem_bm_caption <- paste0( "Species richness and average trophic level are
  positively linked to community biomass. (A) Structural Equation Model for the
  median of annual community biomass (in grams by square meter). Dotted and
  solid arrows represent respectively negative and positive path coefficients.
  Non significant paths are shown in grey. The path coefficients are
  standardized. The $R^2$ are the adjusted $R^2$; Avg: Average, CVsp: weighted
  temporal CV of the population biomass; PCA1 and PCA2: respectively the first
  and second axis of the PCA performed on environmental variables (see methods).
  (B) to (G): significant bivariate relationships between variables of the
  structural equation model. The solid lines show the predictions of the
  statiscal model.")

```


```{r sem-bm, out.width="\\maxwidth", fig.cap = sem_bm_caption, results = "fig.show", cache = FALSE}
#out.height="120%",
#https://tex.stackexchange.com/questions/20496/drawing-different-tikz-shapes-parameterized-by-data-from-a-file?rq=1
#https://tex.stackexchange.com/questions/83888/how-to-plot-data-from-a-csv-file-using-tikz-and-csvsimple

#plot_grid(
  #meta_bm_sem_rich, p_bm_sem_rich,
  #meta_stab_sem_rich, p_stab_sem_rich,
  #labels = LETTERS[1:4], nrow = 2,
  #rel_widths = c(1, 1)
#)
# Put the panel of Colin
arrow_dir <- mypath("manuscript", "bef_stability","fleches", "figure_sem2")
filename <- list.files(arrow_dir, full.names = TRUE)
mask <- str_match(filename, "\\.svg")[, 1] %>% is.na %>% !.
#filename[mask]
type <- c("bm", "meta_bm", "meta_stab", "stab")
sem_list <- map(filename[mask], function (x) {
  w <- 2400
  img <- magick::image_read_svg(
    path = x, width = w, height=w*1.618)#, density = 600
  p_sem <- cowplot::ggdraw() +
    cowplot::draw_image(img)#, scale = 1.0
  return(p_sem)
})
sem_list %<>% map(., ~.x + theme(plot.margin = unit(x = rep(0, 4), units = "pt")))
names(sem_list) <- type
sem_plot <- plot_grid(
  plotlist = sem_list[c("meta_bm", "bm", "meta_stab", "stab")],
  labels = "AUTO" 
  )
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs",
    "sem_colin.pdf"),
  plot = sem_plot, ncol = 2, nrow = 2,
  base_width = 2.71, base_asp = 1.2 
)
#sem_plot
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "fig2.pdf"))
```

\clearpage

```{r}

sem_stab_caption <- paste0("Relationships among environment, species richness,
  food-web structure, stability decomposition and the temporal stability of community biomass. (A)
    Structural Equation Model for the temporal stability of community biomass.
  Dotted and solid arrows represent respectively
  negative and positive path coefficients. Non significant paths are shown in
  grey. The path coefficients are standardized. The $R^2$ are the adjusted
  $R^2$; Avg: Average, CVsp: weighted temporal CV of the population biomass;
  PCA1 and PCA2: respectively the first and second axis of the PCA performed on
  environmental variables (see methods). (B) to (I): significant bivariate
  relationships between variables of the structural equation model. The solid
  lines show the predictions of the statistical model.")
```

```{r sem-stab, out.width="\\maxwidth", fig.cap = sem_stab_caption, results = "fig.show", cache = FALSE}
knitr::include_graphics(mypath("manuscript", "bef_stability", "figs", "fig3.pdf"))
```


